## Day 7 follow-up data quality checks\n\n

```{r}
write("Export Day 7 follow-up data and run corresponding quality checks", stderr())
```

```{r format-RCT-LS-ODK-fu-day7-data}
db_name <- "Day 7 follow-up"
out <- timci::format_day7_data(raw_day7fu_data)
raw_allday7fu_data <- out[[3]]
n_raw_allday7fu_data_records <- nrow(raw_allday7fu_data)
raw_successday7fu_data <- out[[1]]
raw_allday7fu_is_not_empty <- timci::is_not_empty(raw_allday7fu_data)
```

There are **`r n_raw_allday7fu_data_records`** records in the raw `r db_name` database.

### Inconsistent dates

#### Inconsistent finalisation and submission dates [compliance check `r qc_nontimely_day7_submission_id`]\n\n

```{r}
write(" o Inconsistent finalisation and submission", stderr())
```

```{r, eval=raw_allday7fu_is_not_empty, results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- raw_allday7fu_data
col_date1 <- "end"
col_date2 <- "submission_date"
cleaning <- "none"
qc_text <- "the submission was not transferred on the same day it was finalised"
qc_idx <- qc_nontimely_day7_submission_id
qc_export_label <- "nontimely_day7_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Number of days between submission finalisation and transfer" ,
     ylab="Occurences",
     main="")
```

#### Non-timely completion [compliance check `r qc_nontimely_day7_completion_id`]\n\n

```{r}
write(" o Non-timely completion", stderr())
```

```{r, eval=raw_allday7fu_is_not_empty, results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- raw_allday7fu_data
col_date1 <- "start"
col_date2 <- "end"
cleaning <- "none"
qc_text <- "the submission was not finalised on the same day it was started"
qc_idx <- qc_nontimely_day7_completion_id
qc_export_label <- "nontimely_day7_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Number of days between submission start and finalisation" ,
     ylab="Occurences",
     main="")
```

### Follow-ups corresponding to participants enrolled outside the lock date range [context check `r qc_pids_out_lock_range_day7fu`]\n\n

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(raw_allday7fu_data), results='asis'}
qc_description <- paste0("Day 7 follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- raw_allday7fu_data
idcol1 <- "child_id"
refdf <- facility_data_after_lock %>%
  filter( !is.na(child_id) )
idcol2 <- "child_id"
col_date <- "date_call"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_day7fu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up correspond to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_day7fu_records <- n_detected
allday7fu_data <- cleaned_df
```

### Non-valid participant IDs [compliance check `r qc_nonvalid_day7fu`]\n\n

```{r}
write(" o Non-valid participant IDs", stderr())
```

```{r, eval=!is.null(allday7fu_data), results='asis'}
qc_description <- "Day 7 follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_type <- "nonvalid_ids"
df <- allday7fu_data
idcol1 <- "child_id"
refdf <- day0_data
idcol2 <- "child_id"
qc_text <- "non-valid participant IDs"
qc_idx <- qc_nonvalid_day7fu
qc_export_label <- "nonvalid_pids_day7fu"
qc_export_description <- "the child ID does not correspond to any ID found the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_nonvalid_pids_day7fu_records <- n_detected
allday7fu_data <- cleaned_df
```

### Data cleaning summary\n\n

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
n_cleaned_allday7fu_records <- nrow(allday7fu_data)
```

```{r}
timci::create_day7fu_qc_flowchart(n_raw_allday7fu_data_records,
                                  n_afterlock_pids_day7fu_records,
                                  n_nonvalid_pids_day7fu_records,
                                  n_cleaned_allday7fu_records)
```

### Data export\n\n

```{r}
write(" o Data export", stderr())
```

```{r, results = 'asis'}
timci::dataset_export(raw_allday7fu_data,
                      "04a",
                      "timci_followup_day7_data",
                      rctls_dir,
                      "Raw Day 7 follow-up data")
```

```{r, results = 'asis'}
timci::dataset_export(allday7fu_data,
                      "04a",
                      "timci_followup_day7_data",
                      locked_db_dir,
                      "Cleaned Day 7 follow-up data")
```
