```{r}
write("Export withdrawal data and run corresponding quality checks", stderr())
```

## Withdrawal quality checks\n\n

**Rule:** withdrawals with documented child IDs are kept in the locked Day 0 database, then removed in all the databases where entries are posterior to the date of withdrawal. If withdrawn IDs cannot be found in the locked Day 0 database, it is assumed that the caregiver withdrew during data collection. More information will be collected about this in the withdrawal form.

```{r, results='asis'}
if (nrow(day0_data) > 0) {
  if (!is.null(raw_withdrawal_data)) {
    if (nrow(raw_withdrawal_data) > 0) { 
      raw_withdrawal_data$child_id <- ifelse(!is.na(raw_withdrawal_data$'page-a1_a_4'), raw_withdrawal_data$'page-a1_a_4', raw_withdrawal_data$'page-a1_a_4a')
      withdrawal_data2 <- raw_withdrawal_data[!is.na(raw_withdrawal_data$child_id), ]
      withdrawal_data2$child_id <- gsub("O", "0", withdrawal_data2$child_id)
    }
  }
}
```

```{r, results='asis'}
if (nrow(day0_data) > 0) {
  if (!is.null(raw_withdrawal_data)) {
    if (nrow(raw_withdrawal_data) > 0) { 
      cat(paste0("**", nrow(raw_withdrawal_data), "** withdrawal(s) reported (among which **", nrow(withdrawal_data2),"** withdrawals with documented child IDs)."))
    } else {
      cat("No withdrawal reported.")
    }
  }
} else {
  cat("N/A")
}
```

```{r}
day0_data_id_withdrawal <- NULL
non_reconciled_withdrawn_ids <- NULL
`%!in%` <- Negate(`%in%`)

if (nrow(day0_data) > 0) {
  if (!is.null(raw_withdrawal_data)) {
    if (nrow(raw_withdrawal_data) > 0) {
      
      # Non reconciled withdrawn IDs
      non_reconciled_withdrawn_ids <- withdrawal_data2[withdrawal_data2$child_id %!in% day0_data$child_id, ]
      
      # Reconciled withdrawn IDs
      day0_data_id_withdrawal <- day0_data[day0_data$child_id %in% withdrawal_data2$child_id, ]
      day0_data_id_withdrawal <- day0_data_id_withdrawal %>%
        merge(withdrawal_data2, by = 'child_id', all.x = TRUE)
      
    }
  }
}
```

```{r, results='asis'}
if (nrow(day0_data) > 0) {
  if (!is.null(day0_data_id_withdrawal)) {
    cat(paste0("**", nrow(day0_data_id_withdrawal), "** participant(s) who withdrew found in the locked Day 0 database."))
  }
}
```

```{r, results='asis'}
if (nrow(day0_data) > 0) {
  if (!is.null(non_reconciled_withdrawn_ids)) {
    non_reconciled_withdrawn_ids %>%
      dplyr::select(c("child_id", "date", "page-withdrawal_reason")) %>%
      knitr::kable(col.names = c("Child ID",
                                 "Withdrawal date",
                                 "Documented reason"),
                   caption = "List of withdrawals which could not be reconciled with any child ID in the Day 0 locked database")
  }
}
```

```{r, results = 'asis'}
timci::quality_check_export(non_reconciled_withdrawn_ids,
                            qc_nonreconciled_withdrawals_id,
                            "non_reconciled_withdrawn_ids",
                            qc_dir,
                            "withdrawals were not reconciled")
```

### Data export\n\n

```{r}
write(" o Export withdrawal data", stderr())
```

```{r, results = 'asis'}
timci::dataset_export(raw_withdrawal_data,
                      "99",
                      "withdrawal_data",
                      params$rctls_dir,
                      "Raw withdrawal data")
```

```{r, results = 'asis'}
timci::dataset_export(day0_data_id_withdrawal,
                      "99",
                      "withdrawal_data",
                      locked_db_dir,
                      "Cleaned withdrawal data") 
```
