---
title: "TIMCI Data Export Report"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King George s Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
params:
  rctls_dir: !r tempdir()
  participant_zip: "."
  spa_dir: !r tempdir()
  qual1_dir: !r tempdir()
  facility_data: NULL
  raw_day7fu_data: NULL
  raw_hospit_data: NULL
  raw_day28fu_data: NULL
  raw_withdrawal_data: NULL
  spa_cgei_data: NULL
  spa_fa_data: NULL
  spa_hcpi_data: NULL
  spa_sco_data: NULL
  tf_data: NULL
  cgidi_invitation_data: NULL
  cgidi_encryption_data: NULL
  cgidi_interview_data: NULL
output:
  html_document: default
  word_document:
    reference_docx: word_styles1.docx
    fig_width: 7.5
---

```{r setup-rmd, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

```

```{r setup-variables, echo = FALSE}

deidentification_on <- 0

spa_pid <- Sys.getenv("TIMCI_SPA_PID")
qpid <- Sys.getenv("TIMCI_QUAL_PID")
cgidi3_fid <- Sys.getenv("TIMCI_QUAL_CGIDI3_FID")

qual1_dir <- params$qual1_dir

if (!is.null(params$facility_data)) {
  
  facility_data <- params$facility_data
  raw_day7fu_data <- params$raw_day7fu_data
  raw_hospit_data <- params$raw_hospit_data
  raw_day28fu_data <- params$raw_day28fu_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  spa_cgei_data <- params$spa_cgei_data
  spa_fa_data <- params$spa_fa_data
  spa_hcpi_data <- params$spa_hcpi_data
  spa_sco_data <- params$spa_sco_data
  tf_data <- params$tf_data
  cgidi_invitation_data <- params$cgidi_invitation_data
  cgidi_encryption_data <- params$cgidi_encryption_data
  cgidi_interview_data <- params$cgidi_interview_data
  
} else {
  
  rctls_pid <- Sys.getenv("TIMCI_RCTLS_PID")
  rctls_pp <- Sys.getenv("TIMCI_RCTLS_PP")
  
  ################
  # Set up ruODK #
  ################

  ruODK::ru_setup(
    svc = Sys.getenv("ODKC_SVC"),
    un = Sys.getenv("ODKC_UN"),
    pw = Sys.getenv("ODKC_PW"),
    tz = Sys.getenv("TZ"),
    verbose = TRUE # Can be switched to TRUE for demo or debugging
  )

  # List of projects visible with the credentials `ODKC_UN` and `ODKC_PW`
  odkc_project_list <- ruODK::project_list()$id

  wd_fid <- Sys.getenv("TIMCI_WD_FID")

  # RCT / LS environment variables
  crf_facility_fid <- Sys.getenv("TIMCI_CRF_FACILITY_FID")
  crf_day7_fid <- Sys.getenv("TIMCI_CRF_DAY7_FID")
  crf_hospit_fid <- Sys.getenv("TIMCI_CRF_HOSPIT_FID")
  if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
    crf_day28_fid <- Sys.getenv("TIMCI_CRF_DAY28_FID")
  }
  crf_wfa_fid <- Sys.getenv("TIMCI_WEEKLY_FA_FID")

  # SPA environment variables
  cgei_fid <- Sys.getenv("TIMCI_SPA_CGEI_FID")
  fa_fid <- Sys.getenv("TIMCI_SPA_FA_FID")
  sco_fid <- Sys.getenv("TIMCI_SPA_SCO_FID")
  hcpi_fid <- Sys.getenv("TIMCI_SPA_HCPI_FID")
  tf_fid <- Sys.getenv("TIMCI_TF_FID")

  # Qualitative environment variables
  cgidi1_fid <- Sys.getenv("TIMCI_QUAL_CGIDI1_FID")
  cgidi2_fid <- Sys.getenv("TIMCI_QUAL_CGIDI2_FID")
  cgidi3_fid <- Sys.getenv("TIMCI_QUAL_CGIDI3_FID")

  #######################
  # Load TIMCI ODK data #
  #######################

  # List of forms visible in the RCT / LS project
  rct_ls_form_list <- ruODK::form_list(pid = rctls_pid)$fid

  # List of forms visible in the SPA project
  spa_form_list <- NULL
  if (spa_pid %in% odkc_project_list) {
    spa_form_list <- ruODK::form_list(pid = spa_pid)$fid
  }

  # List of forms visible in the qualitative project
  qual_form_list <- NULL
  if (qpid %in% odkc_project_list) {
    qual_form_list <- ruODK::form_list(pid = qpid)$fid
  }

  # Load facility data
  print("Load facility data")

  raw_facility_zip <- ruODK::submission_export(local_dir = tempdir(),
                                               pid = rctls_pid,
                                               fid = crf_facility_fid,
                                               pp = rctls_pp)
  raw_facility_data <- timci::extract_data_from_odk_zip(raw_facility_zip, paste0(crf_facility_fid,".csv"))
  facility_data <- timci::process_facility_data(raw_facility_data)
  pii <- timci::extract_enrolled_participants(facility_data)[[2]]

  #To do copy audit trail in folder
  # local_dir = file.path(mdb_dir, "facility_crf_media")

  # Load day 7 follow-up data
  print("Load day 7 follow-up data")
  raw_day7fu_data <- NULL
  if (crf_day7_fid %in% rct_ls_form_list) {
    raw_day7fu_zip <- ruODK::submission_export(local_dir = tempdir(),
                                               pid = rctls_pid,
                                               fid = crf_day7_fid,
                                               pp = rctls_pp,
                                               media = FALSE)
    raw_day7fu_data <- timci::extract_data_from_odk_zip(raw_day7fu_zip, paste0(crf_day7_fid,".csv"))
  }

  # Load hospital visit follow-up data
  print("Load hospital visit data")
  raw_hospit_data <- NULL
  if (crf_hospit_fid %in% rct_ls_form_list) {
    raw_hospit_zip <- ruODK::submission_export(local_dir = tempdir(),
                                               pid = rctls_pid,
                                               fid = crf_hospit_fid,
                                               pp = rctls_pp,
                                               media = FALSE)
    raw_hospit_data <- timci::extract_data_from_odk_zip(raw_hospit_zip, paste0(crf_hospit_fid,".csv"))
  }

  # Load day 28 follow-up data
  raw_day28fu_data <- NULL
  if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
    print("Load day 28 follow-up data")
    if (crf_day28_fid %in% rct_ls_form_list) {
      raw_day28fu_zip <- ruODK::submission_export(local_dir = tempdir(),
                                                  pid = rctls_pid,
                                                  fid = crf_day28_fid,
                                                  pp = rctls_pp,
                                                  media = FALSE)
      raw_day28fu_data <- timci::extract_data_from_odk_zip(raw_day28fu_zip, paste0(crf_day28_fid,".csv"))
    }
  }

  # Load widthdrawal data
  print("Load withdrawal data")
  raw_withdrawal_data <- NULL
  if (wd_fid %in% rct_ls_form_list) {
    raw_withdrawal_zip <- ruODK::submission_export(local_dir = tempdir(),
                                                   pid = rctls_pid,
                                                   fid = wd_fid,
                                                   pp = rctls_pp,
                                                   media = FALSE)
    raw_withdrawal_data <- timci::extract_data_from_odk_zip(raw_withdrawal_zip, paste0(wd_fid,".csv"))
  }

  # Load weekly facility assessment data
  print("Load weekly facility assessment data")
  wfa_data <- NULL
  if (crf_wfa_fid %in% rct_ls_form_list) {
    raw_wfa_zip <- ruODK::submission_export(local_dir = tempdir(),
                                            pid = rctls_pid,
                                            fid = crf_wfa_fid,
                                            pp = rctls_pp,
                                            media = FALSE)
    raw_wfa_data <- timci::extract_data_from_odk_zip(raw_wfa_zip, paste0(crf_wfa_fid,".csv"))
    wfa_data <- timci::process_weekly_fa_data(raw_wfa_data)
  }

  # Load SPA data
  spa_cgei_data <- NULL
  spa_fa_data <- NULL
  spa_hcpi_data <- NULL
  spa_sco_data <- NULL
  tf_data <- NULL

  if (spa_pid %in% odkc_project_list) {

    # Load SPA caregiver exit interview data
    print("Load SPA caregiver exit interview data")
    if (cgei_fid %in% spa_form_list) {
      raw_spa_cgei_data <- ruODK::odata_submission_get(pid = spa_pid,
                                                       fid = cgei_fid,
                                                       download = FALSE)
      spa_cgei_data <- timci::format_odk_metadata(raw_spa_cgei_data)
    }

    # Load SPA facility assessment data
    print("Load SPA facility assessment data")
    if (fa_fid %in% spa_form_list) {
      raw_spa_fa_data <- ruODK::odata_submission_get(pid = spa_pid,
                                                     fid = fa_fid,
                                                     download = FALSE)
      spa_fa_data <- timci::format_odk_metadata(raw_spa_fa_data)
    }

    # Load SPA healthcare provider interview data
    print("Load SPA healthcare provider interview data")
    if (hcpi_fid %in% spa_form_list) {
      raw_spa_hcpi_data <- ruODK::odata_submission_get(pid = spa_pid,
                                                       fid = hcpi_fid,
                                                       download = FALSE)
      spa_hcpi_data <- timci::format_odk_metadata(raw_spa_hcpi_data)
    }

    # Load SPA sick child observation protocol data
    print("Load SPA sick child observation protocol data")
    if (sco_fid %in% spa_form_list) {
      raw_spa_sco_data <- ruODK::odata_submission_get(pid = spa_pid,
                                                      fid = sco_fid,
                                                      download = FALSE)
      spa_sco_data <- timci::format_odk_metadata(raw_spa_sco_data)
    }

    # Load time-flow data
    print("Load time-flow data")
    if (tf_fid %in% spa_form_list) {
      raw_tf_data <- ruODK::odata_submission_get(pid = spa_pid,
                                                 fid = tf_fid,
                                                 download = FALSE)
      tf_data <- timci::format_odk_metadata(raw_tf_data)
    }

  }

  # Load qualitative data
  cgidi_invitation_data <- NULL
  cgidi_encryption_data <- NULL
  cgidi_interview_data <- NULL

  if (qpid %in% odkc_project_list) {

    # Load caregiver IDI invitation data
    print("Load caregiver IDI invitation data")
    if (cgidi1_fid %in% qual_form_list) {
      raw_cgidi_invitation_data <- ruODK::odata_submission_get(pid = qpid,
                                                               fid = cgidi1_fid,
                                                               download = FALSE)
      cgidi_invitation_data <- timci::format_odk_metadata(raw_cgidi_invitation_data)
    }

    # Load caregiver IDI encryption list
    print("Load caregiver IDI encryption list")
    if (cgidi2_fid %in% qual_form_list) {
      raw_cgidi_encryption_data <- ruODK::odata_submission_get(pid = qpid,
                                                               fid = cgidi2_fid,
                                                               download = FALSE)
      cgidi_encryption_data <- timci::format_odk_metadata(raw_cgidi_encryption_data)
    }

    # Load caregiver IDI interview data
    print("Load caregiver IDI interview data")
    if (cgidi3_fid %in% qual_form_list) {
      raw_cgidi_interview_zip <- ruODK::submission_export(local_dir = tempdir(),
                                                          pid = qpid,
                                                          fid = cgidi3_fid)
      cgidi_interview_data <- timci::extract_data_from_odk_zip(raw_cgidi_interview_zip, paste0(cgidi3_fid,".csv"))
    }

  }
  
}
```

```{r load-RCT-LS-ODK-facility-data}
start_date <- NULL
end_date <- NULL
if (!is.null(facility_data)) { 
  if (nrow(facility_data) > 0) {
    start_date <- min(facility_data$date_visit)
    end_date <- max(facility_data$date_visit)
  }
}
```

This report covers the period from **`r start_date`** to **`r end_date`**.

# 1. `r if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India"){'Pragmatic cluster RCT'} else{'Longitudinal Observational Study'}`

## 1.1. Facility data

### Load data

```{r export-screening-data}
if (!is.null(facility_data)) { 
  screening_data <- timci::extract_screening_data(facility_data)
  fn <- timci::export_df2xlsx(screening_data, params$rctls_dir,
                              "01_timci_screening_data")
  fn <- timci::export_df2csv(screening_data, params$rctls_dir,
                             "01_timci_screening_data")
}
```

```{r split-pii-from-research-data}
if (!is.null(facility_data)) {
  res <- timci::extract_enrolled_participants(facility_data)
  
  day0_data <- res[[1]]
  n_enrolled <- nrow(day0_data)
  
  if (deidentification_on == 1) {
    deidentified_day0_data <- timci::deidentify_data(day0_data)
    fn <- timci::export_df2xlsx(deidentified_day0_data, params$rctls_dir,
                                "02_timci_day0_data")
    fn <- timci::export_df2csv(deidentified_day0_data, params$rctls_dir,
                               "02_timci_day0_data")
  } else {
    fn <- timci::export_df2xlsx(day0_data, params$rctls_dir,
                                "02_timci_day0_data")
    fn <- timci::export_df2csv(day0_data, params$rctls_dir,
                               "02_timci_day0_data")
  }
  
  pii <- res[[2]]
  xlsx_fname <- timci::export_df2xlsx(pii, tempdir(),
                                      "timci_contact_data")
  pii_pwd <- Sys.getenv("TIMCI_PII_PW")
  zip(params$participant_zip, 
      files = xlsx_fname, 
      flags = paste("-r9Xj --password", pii_pwd))
}
```

```{r export-visit-data}
if (!is.null(facility_data)) {
  study_data <- timci::extract_all_visits(facility_data)
  
  if (deidentification_on == 1) {
    deidentified_facility_data <- timci::deidentify_data(study_data)
    fn <- timci::export_df2xlsx(deidentified_facility_data, params$rctls_dir, "03_timci_facility_visits_data")
    fn <- timci::export_df2csv(deidentified_facility_data, params$rctls_dir, "03_timci_facility_visits_data")
  } else {
    fn <- timci::export_df2xlsx(study_data, params$rctls_dir, "03_timci_facility_visits_data")
    fn <- timci::export_df2csv(study_data, params$rctls_dir, "03_timci_facility_visits_data")
  }

}
```

### Quality checks

#### Duplicates

```{r check-RCT-LS-ODK-facility-data-001, results='asis'}
day0_qc <- NULL
if (!is.null(facility_data)) {
  if (nrow(day0_data) > 0) {
    day0_qc <- timci::detect_id_duplicates(day0_data)
    duplicates <- day0_qc[day0_qc$id_fq > 1,]
    if (nrow(duplicates) > 0) { 
      knitr::kable(duplicates, caption = "ID duplicates", row.names = FALSE)
    } else {
      cat("No ID duplicates detected")
    }
  } else {
    cat("N/A")
  }
}
```

```{r check-RCT-LS-ODK-facility-data-002, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(pii) > 0) {
    day0_qc1 <- timci::detect_name_duplicates(pii)
    day0_qc <- merge(day0_qc, day0_qc1, by = 'child_id')
    duplicates <- day0_qc[(day0_qc$ex_name_fq > 1) | (day0_qc$sw_name_fq > 1),]
    if (nrow(duplicates) > 0) { 
      knitr::kable(duplicates, caption = "Possible name duplicates")
    } else {
      cat("No name duplicates detected")
    }
  } else {
    cat("N/A")
  }
}

# Approximate String Matching (Fuzzy Matching)
df <- dplyr::mutate(pii, full_name = tolower(paste(fs_name, ls_name, sep = ' ')))
df3 <- df[c("child_id", "full_name")]
qc3 <- lapply(list(df3$full_name), agrep, x = list(df3$full_name), value = TRUE)
print(qc3)
```
```{r export-duplicates}
if (!is.null(day0_qc)) {
  fn <- timci::export_df2xlsx(day0_qc, params$rctls_dir,
                              "07_data_quality_checks")
}
```

## 1.2. Day 7 follow-up

### Load data

```{r load-RCT-LS-ODK-fu-day7-data}
day7fu_data <- NULL
if (!is.null(raw_day7fu_data)) {
  if (nrow(raw_day7fu_data) > 0) {
    res <- timci::format_day7_data(raw_day7fu_data)
    day7fu_data <- res[[1]]
  }
}
```

### Quality checks

```{r check-RCT-LS-ODK-fu-day7-data, results='asis'}
if (!is.null(day7fu_data)) {
  day7fu_qc <- timci::detect_id_duplicates(day7fu_data)
  day7fu_duplicates <- day7fu_qc[day7fu_qc$id_fq > 1,]
  if (length(day7fu_duplicates) > 0) { 
       knitr::kable(day7fu_duplicates,
                    caption = "ID duplicates",
                    row.names = FALSE)
  } else {
    cat("No ID duplicates detected")
  }
}
```

### Export data

```{r export-RCT-LS-ODK-fu-day7-data}
if (!is.null(day7fu_data)) {
  fn <- timci::export_df2xlsx(day7fu_data, params$rctls_dir, "04_timci_followup_day7_data")
  fn <- timci::export_df2csv(day7fu_data, params$rctls_dir, "04_timci_followup_day7_data")
}
```

## 1.3. Hospitalisation follow-up

### Load data

```{r load-RCT-LS-ODK-fu-hospit-data}
hospit_data <- NULL
if (!is.null(raw_hospit_data)) {
  hospit_data <- process_hospital_data(raw_hospit_data)
}
```

### Quality checks

```{r check-RCT-LS-ODK-fu-hospit-data, results='asis'}
if (!is.null(hospit_data)) {
  hospit_data_duplicates <- detect_id_duplicates(hospit_data)
  if (length(hospit_data_duplicates) > 0) { 
       knitr::kable(hospit_data_duplicates, caption = "ID duplicates")
  } else {
    cat("No ID duplicates detected")
  }
}
```

### Export data

```{r export-RCT-LS-ODK-fu-hospit-data}
if (!is.null(hospit_data)) {
  fn <- timci::export_df2xlsx(hospit_data, params$rctls_dir,
                              "05_timci_followup_hospit_data")
  fn <- timci::export_df2csv(hospit_data, params$rctls_dir,
                             "05_timci_followup_hospit_data")
}
```

## 1.3. Day 28 follow-up

```{r load-RCT-LS-ODK-fu-day28-data}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  if (!is.null(raw_day28fu_data)) {
    fn <- timci::export_df2xlsx(raw_day28fu_data, params$rctls_dir,
                                "06_timci_followup_day28_data")
    fn <- timci::export_df2csv(raw_day28fu_data, params$rctls_dir,
                               "06_timci_followup_day28_data")
  }
}
```

## 1.4. Withdrawal data

```{r load-RCT-LS-ODK-withdrawal}
if (!is.null(raw_withdrawal_data)) {
  withdrawal_data <- raw_withdrawal_data
}
```

# 2. Service Provision Assessment (SPA)

## 2.1. Caregiver exit interview

```{r cg-exit-interview-export}
if (!is.null(spa_cgei_data)) {
  fn <- timci::export_df2xlsx(spa_cgei_data, params$spa_dir,
                              "03_timci_spa_exit_interview_data")
  fn <- timci::export_df2csv(spa_cgei_data, params$spa_dir,
                             "03_timci_spa_exit_interview_data")
}
```

## 2.2. Facility assessment

```{r facility-assessment-export}
if (!is.null(spa_fa_data)) {
  fn <- timci::export_df2xlsx(spa_fa_data, params$spa_dir,
                              "01_timci_spa_facility_assessment_data")
  fn <- timci::export_df2csv(spa_fa_data, params$spa_dir,
                             "01_timci_spa_facility_assessment_data")
}
```

## 2.3. Healthcare provider interview

```{r hcp-interview-export}
if (!is.null(spa_hcpi_data)) {
  fn <- timci::export_df2xlsx(spa_hcpi_data, params$spa_dir,
                              "02_timci_spa_provider_interview_data")
  fn <- timci::export_df2csv(spa_hcpi_data, params$spa_dir,
                             "02_timci_spa_provider_interview_data")
}
```

## 2.4. Sick child observation protocol

```{r sick-child-observation-export}
if (!is.null(spa_sco_data)) {
  if (deidentification_on == 1) {
    deidentified_spa_sco_data <- timci::deidentify_spa_data(spa_sco_data)
    fn <- timci::export_df2xlsx(deidentified_spa_sco_data, params$spa_dir,
                                "04_timci_spa_consultation_obs_data")
    fn <- timci::export_df2csv(deidentified_spa_sco_data, params$spa_dir,
                               "04_timci_spa_consultation_obs_data")
  } else {
    fn <- timci::export_df2xlsx(spa_sco_data, params$spa_dir,
                                "04_timci_spa_consultation_obs_data")
    fn <- timci::export_df2csv(spa_sco_data, params$spa_dir,
                               "04_timci_spa_consultation_obs_data")
  }
  
}
```

## 2.5. Time-flow

```{r time-flow-export}
if (!is.null(tf_data[[1]])) {
  fn <- timci::export_df2xlsx(tf_data[[1]], params$spa_dir,
                              "05a_timci_timeflow_data")
  fn <- timci::export_df2csv(tf_data[[1]], params$spa_dir,
                             "05a_timci_timeflow_data")
  fn <- timci::export_df2xlsx(tf_data[[2]], params$spa_dir,
                              "05b_timci_timeflow_audit")
  fn <- timci::export_df2csv(tf_data[[2]], params$spa_dir,
                             "05b_timci_timeflow_audit")
  fn <- timci::export_df2xlsx(tf_data[[3]], params$spa_dir,
                              "05c_timci_timeflow_steps")
  fn <- timci::export_df2csv(tf_data[[3]], params$spa_dir,
                             "05c_timci_timeflow_steps")
}
```

# 3. Qualitative studies

## 3.1. Caregiver in-depth interview

```{r cg-idi-potential-participants}
if (!is.null(day0_data) && !is.null(day7fu_data)) {
  cg_qual_export_data <- generate_cg_log(day0_data, day7fu_data)
  fn <- timci::export_df2xlsx(cg_qual_export_data, qual1_dir,
                              "cg_idi_participants")
  fn <- timci::export_df2csv(cg_qual_export_data, qual1_dir,
                             "cg_idi_participants")
}
```

```{r cg-idi-invitation-export}
if (!is.null(cgidi_invitation_data)) {
  fn <- timci::export_df2xlsx(cgidi_invitation_data, qual1_dir,
                              "01_timci_cg_invitation_data")
}
```

```{r cg-idi-encryption-export}
if (!is.null(cgidi_encryption_data)) {
  fn <- timci::export_df2xlsx(cgidi_encryption_data, qual1_dir,
                              "02_timci_cg_encryption_data")
}
```

```{r cg-idi-interview-export}
if (!is.null(cgidi_interview_data)) {
  fn <- timci::export_df2xlsx(cgidi_interview_data, qual1_dir,
                              "03_timci_cg_interview_data")

  sl <- ruODK::submission_list(pid = qpid,
                               fid = cgidi3_fid)
  
  # Loop on all rows
  for (i in 1:nrow(sl)) {
    crow <- cgidi_interview_data[i,]
    uuid <- crow$'meta-instanceID'
    cpath <- file.path(qual1_dir, crow$'identification-idiidm')
    print(paste0("Participant: ", crow$'identification-idiidm'))
    dir.create(cpath, showWarnings = FALSE)
    # Create a new dataframe using the transpose of crow
    tcrow <- as.data.frame(t(as.matrix(crow)))
    names(tcrow)[names(tcrow) == "V1"] <- "values"
    fname <- file.path(cpath, paste("data", "_", Sys.Date(), ".xlsx", sep = ""))
    openxlsx::write.xlsx(tcrow, fname, row.names = TRUE)
    
    # Download attachments
    al <- ruODK::get_one_submission_attachment_list(pid = qpid,
                                                    fid = cgidi3_fid,
                                                    uuid)
    for (j in 1:nrow(al)) {
      aid <- al$name[[j]]
      print(paste0("Attachment: ", aid))
      ruODK::attachment_get(pid = qpid,
                            fid = cgidi3_fid,
                            uuid, 
                            aid,
                            local_dir = cpath)
    }
  }
}
```
