\newpage

## Day 28 data quality checks\n\n

```{r}
write("Export Day 28 data and run corresponding quality checks", stderr())
```

```{r}
db_name <- "Day 28 follow-up"
out <- timci::format_day28_data(raw_day28fu_data)
raw_allday28fu_data <- out[[3]]
n_raw_allday28fu_data_records <- nrow(raw_allday28fu_data)
raw_successday28fu_data <- out[[1]]

raw_allday28fu_is_not_empty <- timci::is_not_empty(raw_allday28fu_data)
raw_day28_fu_is_not_empty <- timci::is_not_empty(raw_day28fu_data)
```

There are **`r n_raw_allday28fu_data_records`** records in the raw `r db_name` database.

### Non-consistent finalisation and submission dates [Context check `r qc_nontimely_submission_day28fu`]

```{r}
write(" o Inconsistent finalisation and submission", stderr())
```

```{r}
fig_caption <- "Submissions not transferred on the same day they were finalised"
facility_col <- "hf_id"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"
```

### Non-timely completion [Context check `r qc_nontimely_completion_day7fu`]

```{r}
write(" o Non-timely completion", stderr())
```

```{r}
fig_caption <- "Number of submissions not finalised on the same day they were started"
facility_col <- "hf_id"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"
```

### Follow-ups corresponding to participants enrolled outside the lock date range [context check `r qc_pids_out_lock_range_day28fu`]\n\n

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(raw_allday28fu_data), results='asis'}
qc_description <- paste0("Day 28 follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- raw_allday28fu_data
idcol1 <- "child_id"
refdf <- facility_data_after_lock %>%
  dplyr::filter( !is.na(child_id) )
idcol2 <- "child_id"
col_date <- "date_call"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_day28fu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up correspond to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_day28fu_records <- n_detected
allday28fu_data <- cleaned_df
```

### Non-valid participant IDs [compliance check `r qc_nonvalid_day28fu`]\n\n

```{r}
write(" o Non-valid participant IDs", stderr())
```

```{r, eval=!is.null(allday28fu_data), results='asis'}
qc_description <- "Day 28 follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_type <- "nonvalid_ids"
df <- allday28fu_data
idcol1 <- "child_id"
refdf <- day0_data
idcol2 <- "child_id"
qc_text <- "non-valid participant IDs"
qc_idx <- qc_nonvalid_day28fu
qc_export_label <- "nonvalid_pids_day28fu"
qc_export_description <- "the child ID does not correspond to any ID found the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_nonvalid_pids_day28fu_records <- n_detected
allday28fu_data <- cleaned_df
```

### Non-consistent participant names [Context check `r qc_nonconsistent_name_day28fu`]

```{r}
write(" o Non-consistent participant names", stderr())
```

```{r, eval=is_tanzania}
raw_day0_with_names <- day0_data %>% 
  merge(raw_pii %>%
          dplyr::select(fs_name,
                        ms_name,
                        ls_name,
                        uuid),
        by = "uuid")
```

```{r, eval=!is_tanzania}
raw_day0_with_names <- day0_data %>%
  merge(raw_pii %>%
          dplyr::select(fs_name,
                        ls_name,
                        uuid),
        by = "uuid")
```

### Data cleaning summary\n\n

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
n_cleaned_allday28fu_records <- nrow(allday28fu_data)
```

```{r}
timci::create_day28fu_qc_flowchart(n_raw_allday28fu_data_records,
                                   n_afterlock_pids_day28fu_records,
                                   n_nonvalid_pids_day28fu_records,
                                   n_cleaned_allday28fu_records)
```

### Data export\n\n

```{r}
write(" o Data export", stderr())
```

```{r, results = 'asis'}
timci::dataset_export(raw_allday28fu_data,
                      "06a",
                      "timci_followup_day28_data",
                      rctls_dir,
                      "Raw Day 28 follow-up data")
```

```{r, results = 'asis'}
timci::dataset_export(allday28fu_data,
                      "06a",
                      "timci_followup_day28_data",
                      locked_db_dir,
                      "Cleaned Day 28 follow-up data")
```
