---
title: "TIMCI Data Quality Report"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King Georges Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M GMT%z')`"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 3
  word_document:
    toc: true
    reference_docx: word_styles1.docx
    fig_width: 7.5
params:
  locked_day0_data: NULL
  locked_allday7fu_data: NULL
  locked_allday28fu_data: NULL
  locked_hospit_data: NULL
  locked_spa_sco_data: NULL
  locked_spa_hcpi_data: NULL
  spa_cgei_data: NULL
  spa_fa_data: NULL
---

```{r setup-rmd, include=FALSE}
library(dplyr)
library(magrittr)
library(skimr)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
options(knitr.table.format = "pipe")
```

```{r}
locked_day0_data <- params$locked_day0_data
locked_allday7fu_data <- params$locked_allday7fu_data
locked_allday28fu_data <- params$locked_allday28fu_data
locked_hospit_data <- params$locked_hospit_data
locked_spa_sco_data <- params$locked_spa_sco_data
spa_cgei_data <- params$spa_cgei_data
locked_spa_hcpi_data <- params$locked_spa_hcpi_data
spa_fa_data <- params$spa_fa_data
```

```{r translations-subsection, child = 'translations.Rmd'}
```

\newpage

`r intro_str`

```{r data-explore-verbose}
write(formats2h2("Explore Day 0 data"), stderr())
```

# `r if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India"){'Pragmatic cluster Randomised Controlled Trial (RCT)'} else{'Longitudinal Observational Study (LS)'}`

## Day 0 data

```{r, results='asis'}
skimr::skim(locked_day0_data)
```

## Day 7 follow-up data

```{r, results='asis'}
skimr::skim(locked_allday7fu_data)
```

## Day 28 follow-up data

```{r, results='asis'}
skimr::skim(locked_allday28fu_data)
```

## Hospital visit follow-up data

```{r, results='asis'}
skimr::skim(locked_hospit_data)
```

# Service Provision Assessment (SPA)

## Sick child observation data

```{r, results='asis'}
skimr::skim(locked_spa_sco_data)
```

## Caregiver exit interview data

```{r, results='asis', eval=(!is.null(spa_cgei_data))}
skimr::skim(spa_cgei_data)
```

## Healthcare provider interview data

```{r, results='asis', eval=(!is.null(locked_spa_hcpi_data))}
skimr::skim(locked_spa_hcpi_data)
```

## Facility Assessment

```{r, results='asis', eval=(!is.null(spa_fa_data))}
skimr::skim(spa_fa_data)
```
