## Hospitalisation data quality checks\n\n

```{r}
write("Export hospital/hospitalisation data and run corresponding quality checks", stderr())
```

```{r format-RCT-LS-ODK-fu-hospit-data}
hospit_data <- timci::format_hospital_data(raw_hospit_data)
db_name <- "hospitalisation follow-up"
```

There are **`r if ( !is.null(hospit_data) ) { nrow(hospit_data) } else { 'NA' }`** record(s) in the raw `r db_name` database.

```{r}
hospit_data_uids <- NULL
locked_hospit_data <- NULL
hospit_fu <- NULL
```

### Follow-ups corresponding to participants enrolled outside the lock date range [context check `r qc_pids_out_lock_range_hospitfu`]\n\n

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- paste0("Hospitalisation follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- hospit_data
idcol1 <- "child_id"
refdf <- facility_data_after_lock %>%
  filter( !is.na(child_id) )
idcol2 <- "child_id"
col_date <- "date"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_hospitfu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up correspond to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_hospitfu_records <- n_detected
hospit_data <- cleaned_df
```

### Non-valid participant IDs [compliance check `r qc_nonvalid_hospitfu`]\n\n

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- "Hospitalisation follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of participant who are found in the locked Day 0 database."
qc_type <- "nonvalid_ids"
df <- hospit_data
idcol1 <- "child_id"
refdf <- day0_data
idcol2 <- "child_id"
qc_text <- "non-valid participant IDs"
qc_idx <- qc_nonvalid_hospitfu
qc_export_label <- "nonvalid_pids_hospitfu"
qc_export_description <- "the child ID does not correspond to any ID found the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_pids_hospitfu <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
locked_hospit_data <- cleaned_df
```

### Duplicate management [compliance check `r qc_duplicated_hospitfu`]\n\n

```{r, eval=!is.null(locked_hospit_data), results='asis'}
qc_description <- "It is possible to have more than one successful follow-up records available for the same participant."
qc_rule <- action_alert_no_modification
qc_type <- "duplicates"
df <- locked_hospit_data %>% 
  filter(found == 1)
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicated_hospitfu
qc_export_label <- "duplicated_hospitfu"
qc_export_description <- "hospitalisation follow-ups are duplicated"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_duplicates_hospitfu <- n_detected
```

### Invalid date of hospitalisation [context check `r qc_hospit_before_enrolment`]\n\n

```{r, eval=!is.null(locked_hospit_data), results='asis'}
qc_description <- "The reported hospital visit should have happened between enrolment at Day 0 and the Day 7 follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- locked_hospit_data %>%
  filter(found == 1) %>% 
  merge(day0_data,
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_visit_rhf"
col_date2 <- "date_visit"
qc_text <- "a date of hospitalisation before the enrolment date"
qc_idx <- qc_hospit_before_enrolment
qc_export_label <- "hospit_before_enrolment"
qc_export_description <- "the reported date of hospitalisation was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Data cleaning summary\n\n

```{r}
timci::create_hospit_qc_flowchart(nrow(hospit_data),
                                  n_afterlock_pids_hospitfu_records,
                                  n_nonvalid_pids_hospitfu,
                                  n_duplicates_hospitfu,
                                  nrow(locked_hospit_data))
```

### Data export\n\n

```{r export-RCT-LS-ODK-fu-hospit-data, results = 'asis'}
timci::dataset_export(hospit_data,
                      "05a",
                      "timci_followup_hospit_data",
                      rctls_dir,
                      "Raw hospitalisation data")
```

```{r, results = 'asis'}
timci::dataset_export(locked_hospit_data,
                      "05a",
                      "timci_followup_hospit_data",
                      locked_db_dir,
                      "Cleaned hospitalisation data")
```

```{r, eval=!is.null(raw_pii)}
hospit_fu <- timci::generate_hospital_log(pii = raw_pii,
                                          fu7df = raw_day7fu_data,
                                          day0df = day0_data,
                                          hospitdf = raw_hospit_data,
                                          deidentify = TRUE)
```

```{r, results = 'asis'}
timci::dataset_export(hospit_fu,
                      "05c",
                      "timci_deidentified_hospit_fu_log_all",
                      rctls_dir,
                      "Hospitalisation log data")
```

### Data summary statistics\n\n

```{r, results='asis'}
skimr::skim(locked_hospit_data)
```
