\newpage

```{r}
write("Export Day 0 data and run corresponding quality checks", stderr())
```

```{r}
###########################
# Day 0 quality check IDs #
###########################
qc_true_duplicates <- "DQC_00_2ED_05"
qc_duplicate_id <- "DQC_00_2ED_06"
qc_ambiguous_enrolment_date1 <- "DQC_00_2ED_07"
qc_ambiguous_enrolment_date2 <- "DQC_00_2ED_08"
qc_multiple_enrolment_id <- "DQC_00_2ED_09"
qc_multiple_enrolment_sex_discrepancy_id <- "DQC_00_2ED_10"
qc_missing_cp_id <- "DQC_00_2ED_11"
qc_missing_diagnosis_id <- "DQC_00_2ED_12"
qc_missing_referral_id <- "DQC_00_2ED_13"
qc_missing_treatment_id <- "DQC_00_2ED_14"
qc_negative_nb_days_id <- "DQC_00_2ED_15"
qc_free_text_rx_id <- "DQC_00_2ED_16"
qc_pox_ <- "DQC_00_2ED_17"
qc_summary_id <- "DQC_00_2ED_18"
```

```{r}
n_dropped_true_duplicate_records <- 0
n_duplicate_edits <- 0
n_dropped_duplicate_records <- 0
n_nonvalid_fid_records <- 0
n_incorrect_enroldate_records <- 0
n_missing_cp <- 0
n_missing_diagnosis <- 0
```

## Day 0 data quality checks and cleaning

```{r}
db_name <- "Day 0"
day0_data <- facility_data %>%
    dplyr::filter(enrolled == 1)
n_raw_day0_records <- nrow(day0_data)
day0_is_not_null <- !is.null(day0_data)
day0_is_not_empty <- timci::is_not_empty(day0_data)
print_clean_drug_data_title <- ""
drug_edits_is_not_empty <- FALSE
```

Among the **`r n_cleaned_screening_records`** cleaned screening record(s), there are **`r n_raw_day0_records`** record(s) corresponding to new Day 0 enrolment(s).

### Participant identification

#### True duplicated records of same enrolment [Compliance check `r qc_true_duplicates`]

```{r}
write(" o Management of true duplicates (same ID, same day, same name)", stderr())
```

`r if ( is_tanzania & !is_pilot ) { paste0('::: {custom-style="redparagraph"}\n\nInitial check ', qc_true_duplicates, 'a\n\n:::')}`

```{r, eval=day0_is_not_null, results='asis'}
qc_description <- "Participants who have been entered twice as new enrolments with the same ID on the same day, which creates duplicates in the database."
qc_rule <- "True duplicates are detected and corrected where possible."
qc_type <- "true_duplicates"
df <- day0_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- paste0(qc_true_duplicates, "a")
qc_export_label <- "timci_true_duplicates"
qc_export_description <- "the data was entered in two different records on the same day"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=((is_tanzania|is_senegal)&!is_pilot), results='asis'}
mc_description <- ""
to_correct_df <- day0_data
correction_type <- "delete_day0_records"

# Parameters for the quality check following manual corrections
qc_idx <- paste0(qc_true_duplicates, "b")
qc_rule <- "Remaining duplicated child IDs are deleted from the database."
cleaning <- "none"

cat(knitr::knit_child('database_export_sub_corrections.Rmd',
                      envir = environment(),
                      quiet = TRUE))

day0_data <- corrected_df
n_dropped_true_duplicate_records <- n_mc
```

#### Duplicated child IDs [Compliance check `r qc_duplicate_id` ]

```{r}
write(" o Management of duplicated child IDs", stderr())
```

`r if ( !is_pilot ) { paste0('::: {custom-style="redparagraph"}\n\nInitial check ', qc_duplicate_id, 'a\n\n:::')}`

```{r, eval=day0_is_not_null, results='asis'}
qc_description <- "All participants should have a distinct ID. Duplicated IDs may generate errors for the conduct of follow-ups in the field and results in ambiguous outcomes for duplicated participants once the database is deidentified."
qc_rule <- "Duplicated child IDs are detected and corrected proactively where possible."
qc_type <- "day0_duplicates"
df <- day0_data
ref_df <- raw_successday7fu_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- paste0(qc_duplicate_id, 'a')
qc_export_label <- "timci_day0_data_id_duplicates"
qc_export_description <- "the submission was allocated the same ID that has been used for another participant in the databse"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
fig_caption <- "Duplicated IDs"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- ""
comparison <- "type"
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>% 
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(date_2), "week", week_start = getOption("lubridate.week.start", 1)))) %>%
  dplyr::mutate(fid = substr(id, 3, 7))

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
initial_duplicates_df <- qc_df %>%
  dplyr::select(id) %>% 
  dplyr::mutate(is_duplicate = 1)
```

```{r, eval=!is_pilot, results='asis'}
mc_description <- ""
to_correct_df <- day0_data
correction_type <- "edit_day0_child_ids_to_correct_duplicates"

# Parameters for the quality check following manual corrections
qc_idx <- paste0(qc_duplicate_id, "b")
qc_rule <- "Remaining duplicated child IDs are deleted from the database."
cleaning <- "drop_all"

cat(knitr::knit_child('database_export_sub_corrections.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_duplicate_edits <- n_mc
```

```{r, eval=!is.null(cleaned_df)}
day0_data <- cleaned_df
n_dropped_duplicate_records <- n_detected
```

### Dates and times

#### Ambiguities about the enrolment date [Context check `r qc_ambiguous_enrolment_date1`]

```{r}
write(" o Ambiguities about the enrolment date", stderr())
```

```{r}
qc_df <- NULL
```

```{r, eval=day0_is_not_null&(is_tanzania|is_senegal), results='asis'}
qc_description <- "The enrolment date is defined as the creation (start) date of the form. However if research assistants reuse a form that already exist on their device to enrol a new participant, it is possible that the date on which the name of the participant is entered in the form is not on the same day it was started. As a consequence the enrolment date may be shifted and follow-up may not be triggered at the right time."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day0_data
col_date1 <- "start"
col_date2 <- "contact_start"
cleaning <- "replace_by_end_date"
qc_text <- "an incorrect date of enrolment"
qc_idx <- qc_ambiguous_enrolment_date1
qc_export_label <- "ambiguous_enrolment_date"
qc_export_description <- "the enrolment date is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_incorrect_enroldate_records <- n_detected
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = ifelse(diff <= 1,
                                    "1 day", ifelse(diff < 3,
                                                       "2-3 days",
                                                       "Above 3 days")))

fig_caption <- "Number of days between submission start and entry of participant contact details"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Difference"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=day0_is_not_null&(is_kenya), results='asis'}
qc_description <- "The enrolment date is defined as the creation (start) date of the form. However if research assistants reuse a form that already exist on their device to enrol a new participant, it is possible that the date on which the name of the participant is entered in the form is not on the same day it was started. As a consequence the enrolment date may be shifted and follow-up may not be triggered at the right time."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day0_data
col_date1 <- "sd_start"
col_date2 <- "start"
cleaning <- "replace_by_end_date"
qc_text <- "an incorrect date of enrolment"
qc_idx <- qc_ambiguous_enrolment_date1
qc_export_label <- "ambiguous_enrolment_date1"
qc_export_description <- "the enrolment date is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_incorrect_enroldate_records <- n_detected
```

```{r, eval=day0_is_not_null&(is_kenya), results='asis'}
qc_description <- "The enrolment date is defined as the creation (start) date of the form. However if research assistants reuse a form that already exist on their device to enrol a new participant, it is possible that the date on which the name of the participant is entered in the form is not on the same day it was started. As a consequence the enrolment date may be shifted and follow-up may not be triggered at the right time."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day0_data
col_date1 <- "start"
col_date2 <- "sd_start"
cleaning <- "replace_by_end_date"
qc_text <- "an incorrect date of enrolment"
qc_idx <- qc_ambiguous_enrolment_date2
qc_export_label <- "ambiguous_enrolment_date2"
qc_export_description <- "the enrolment date is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_incorrect_enroldate_records <- n_detected
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = ifelse(diff <= 1,
                                    "1 day", ifelse(diff < 3,
                                                       "2-3 days",
                                                       "Above 3 days")))

fig_caption <- "Number of days between submission start and entry of participant contact details"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Difference"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Clinical presentation

#### Missing clinical presentation [Mandatory check `r qc_missing_cp_id`]

```{r}
write(" o Missing clinical presentation", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
qc_description <- "All participants should have complete information about their clinical presentation, i.e. a participant cannot have simultaneously:

* No convulsions (*sx_convulsions* $\\neq$ 1)
* No lethargy (*sx_lethargy* $\\neq$ 1)
* No vomiting (*sx_vomit* = 0 or *sx_vomit* = 98)
* No feeding less than usual (*sx_less_feed* = 0 or *sx_less_feed* = 98)
* No cough (*sx_cough* = 0 or *sx_cough* = 98)
* No difficulty breathing (*sx_difficulty_breath* = 0 or *sx_difficulty_breath* = 98)
* No diarrhoea (*sx_diarrhoea* = 0 or *sx_diarrhoea* = 98)
* No fever (*sx_fever* = 0 or *sx_fever* = 98)
* No other complaint (*sx_var* = 96)"
qc_rule <- action_alert_no_modification
qc_type <- "missing_clinical_presentation"
df <- day0_data
qc_text <- "missing clinical presentation"
qc_idx <- qc_missing_cp_id
qc_export_label <- "missing_clinical_presentation"
qc_export_description <- "the clinical presentation is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_cp <- n_detected
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(date_visit),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))  %>%
  dplyr::mutate(Antibiotics = ifelse(antibio_has_been_prescribed == 1 | antibio_has_been_recorded, "Yes", "No"))

fig_caption <- "Missing clinical presentation"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Antibiotics"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Negative illness onset [Consistency check `r qc_negative_nb_days_id`]

```{r}
write(" o Negative illness onset", stderr())
```

```{r, results='asis', eval=timci::is_not_empty(day0_data)}
qc_description <- "Check for spurious values/outliers in illness onset: illness onset should be positive values (number of days) only."
qc_rule <- action_alert_no_modification
qc_type <- "negative_value"
df <- day0_data
col_value <- "sick_duration"
qc_text <- "negative illness onset"
qc_idx <- qc_negative_nb_days_id
qc_export_label <- "negative_illness_onset"
qc_export_description <- "illness onset is negative"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_negative_illness_onset <- n_detected
```

#### Convulsion reporting over time

```{r, eval=timci::is_not_empty(day0_data), results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate(Convulsions = dplyr::case_when(
    sx_convulsions == 1  ~ "a) Yes",
    sx_convulsions == 0  ~ "b) No",
    sx_convulsions == 98 ~ "c) Not sure")) %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1))))

fig_caption <- "Convulsion reporting at clinical presentation over time"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Convulsions"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Lethargy reporting over time

```{r, eval=timci::is_not_empty(day0_data), results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate(Lethargy = dplyr::case_when(
    sx_lethargy == 1  ~ "a) Yes",
    sx_lethargy == 0  ~ "b) No",
    sx_lethargy == 98 ~ "c) Not sure")) %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1))))

fig_caption <- "Lethargy reporting at clinical presentation over time"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Lethargy"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Vomit everything reporting over time

```{r, eval=timci::is_not_empty(day0_data), results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate("Vomit everything" = dplyr::case_when(
    sx_vomit_evthing == 1                            ~ "a) Yes",
    is.na(sx_vomit_evthing) | sx_vomit_evthing == 0  ~ "b) No",
    sx_vomit_evthing == 98                           ~ "c) Not sure")) %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1))))

fig_caption <- "Vomit everything reporting at clinical presentation over time"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Vomit everything"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Unable to feed reporting over time

```{r, eval=timci::is_not_empty(day0_data), results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate("Unable to feed" = dplyr::case_when(
    sx_unable_feed == 1                          ~ "a) Yes",
    is.na(sx_unable_feed) | sx_unable_feed == 0  ~ "b) No",
    sx_unable_feed == 98                         ~ "c) Not sure")) %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1))))

fig_caption <- "Unable to feed reporting at clinical presentation over time"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Unable to feed"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Diagnoses

#### Missing diagnosis [Mandatory check `r qc_missing_diagnosis_id`]\n\n

```{r}
write(" o Missing diagnosis", stderr())
```

```{r, results='asis', eval=day0_is_not_null&!is_india}
qc_description <- "All participants should have complete information about their diagnosis for their Day 0 visit, i.e. a participant cannot have simultaneously:

* No danger signs (*dx_severe* = 0)
* No pneumonia (*dx_pneumonia* = 0)
* No diarrhoea (*dx_diarrhoea* = 0)
* No dehydration (*dx_dehydration* = 0)
* No malaria (*dx_malaria* = 0)
* No ear infection (*dx_ear_infection* = 0)
* No malnutrition (*dx_malnutrition* = 0)
* No anaemia (*dx_anaemia == 0*)
* No other diagnoses (*sx_var* = 96 and *dx_oth_yn* = 1)"
qc_rule <- action_alert_no_modification
qc_type <- "missing_diagnosis"
df <- day0_data
qc_text <- "missing diagnosis information"
qc_idx <- qc_missing_diagnosis_id
qc_export_label <- "missing_diagnosis"
qc_export_description <- "the diagnosis is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_diagnosis <- n_detected
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(date_visit),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Missing diagnosis"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- ""
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
write("   o Free text entries", stderr())
```

```{r, eval=day0_is_not_null, results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate("Free text available" = dplyr::case_when(
    !is.na(dx_oth) ~ "a) Yes",
    .default       = "b) No")) %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(date_visit),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Diagnosis free text entries"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Free text available"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Referrals

#### Missing referral information [Mandatory check `r qc_missing_referral_id`]

```{r}
write(" o Missing referral", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
qc_description <- "All participants should have complete information about the management at the facility for their Day 0 visit. This information is collected from 2 soures: the caregiver at the exit of the consultation and the facility registries/consultation notes. However, caregivers may be lost at the exit of the consultation, so that the referral information from this source would be missing (*referral_cg* = 'NA')."
qc_rule <- action_alert_no_modification
qc_type <- "missing_referral"
df <- day0_data
qc_text <- "missing referral information (source: caregiver at the exit of the consultation)"
qc_idx <- qc_missing_referral_id
qc_export_label <- "missing_referral_cg"
qc_export_description <- "the referral information that should have been obtained from the caregiver at the exit of the consultation is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_referral_cg <- n_detected
```

```{r, eval=timci::is_not_empty(day0_data), results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Referral = dplyr::case_when(
    referral_cg == 1 ~ "a) Referred",
    referral_cg == 0 ~ "b) Not referred",
    referral_cg == 98 ~ "c) Not sure",
    referral_cg == 97 ~ "d) Declined",
    is.na(referral_cg) ~ "e) Missing"))

fig_caption <- "Spatiotemporal pattern of referrals reported by the caregiver"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "type"
fill_col <- "Referral"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
fig_caption <- "Spatiotemporal pattern of referrals recorded in the facility registries/notes"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "type"
fill_col <- "Referral"
```

```{r, eval=timci::is_not_empty(day0_data), results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Referral = dplyr::case_when(
    referral_hf == 1 ~ "Referred",
    referral_hf == 0 ~ "Not referred"))

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Treatments

```{r}
write(" o Treatments", stderr())
```

#### Free text entries

```{r}
write("   o Free text entries", stderr())
```

```{r, eval=day0_is_not_null&is_ls, results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate("Free text available" = dplyr::case_when(
    !is.na(rx_misc_oth) | !is.na(rx_misc_oth_hf) ~ "a) Yes",
    .default                                     = "b) No")) %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(date_visit),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Treatment free text entries"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Free text available"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Structured entries

##### Missing structured treatment [Mandatory check `r qc_missing_treatment_id`]

```{r}
write("   o Missing structured treatment - check 1", stderr())
```

```{r, results='asis', eval=day0_is_not_null&!is_rct}
qc_description <- "All participants should have complete information about the treatment at the facility for their Day 0 visit."
qc_rule <- action_alert_no_modification
qc_type <- "missing_treatment"
df <- day0_data
qc_text <- "missing treatment information (source: caregiver at the exit of the consultation)"
qc_idx <- qc_missing_treatment_id
qc_export_label <- "missing_treatment"
qc_export_description <- "the treatment information is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_treatment <- n_detected
```

```{r, eval=timci::is_not_empty(day0_data)&!is_rct, results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate("Structured treatment entry" = dplyr::case_when(
    ( !is.na(rx_amoxicillin) & !is.na(rx_misc) & rx_misc != "996" ) | ( is.na(rx_amoxicillin_hf) & ( is.na(rx_misc_hf) | rx_misc_hf == "996" ) ) ~ "a) Yes",
    .default                                                                                                                                     = "b) No"))

fig_caption <- "Spatiotemporal pattern of treatments"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "type"
fill_col <- "Structured treatment entry"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=is_ls}
print_clean_drug_data_title <- "##### Update with reentered drug data"
```

`r print_clean_drug_data_title`

```{r}
edited_records_status_update <- ""
```

```{r, eval=is_ls}
out <- timci::correct_day0_drug_data(day0_data, drug_data)
day0_data <- out[[1]]
drug_edits <- out[[2]]
drug_edits_is_not_empty <- timci::is_not_empty(drug_edits)
```

```{r, eval=drug_edits_is_not_empty}
edited_records_status_update <- paste0('**', nrow(drug_edits), '** record(s) manually corrected in the ', db_name, ' database.')
```

`r edited_records_status_update`

```{r, eval=drug_edits_is_not_empty, results='asis'}
drug_edits %>%
  select(start,
         uuid,
         child_id,
         free_text1,
         free_text2) %>%
  head(10) %>%
  knitr::kable()
```

```{r, eval=drug_edits_is_not_empty, results='asis'}
cat("...")
```

```{r, eval=drug_edits_is_not_empty, results='asis'}
drug_edits %>%
  select(start,
         uuid,
         child_id,
         free_text1,
         free_text2) %>%
  tail(10) %>%
  knitr::kable()
```

##### Missing structured treatments after manual entries [Mandatory check `r qc_missing_treatment_id`]

```{r}
write("   o Missing structured treatment - check 2", stderr())
```

```{r, eval=timci::is_not_empty(day0_data)&is_ls, results='asis'}
fig_df <- day0_data %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate("Structured treatment entry" = dplyr::case_when(
    ( !is.na(rx_amoxicillin) & !is.na(rx_misc) & rx_misc != "996" ) | ( is.na(rx_amoxicillin_hf) & ( is.na(rx_misc_hf) | rx_misc_hf == "996" ) ) ~ "a) Yes",
    .default                                                                                                                                     = "b) No"))

fig_caption <- "Spatiotemporal pattern of treatments"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "type"
fill_col <- "Structured treatment entry"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=day0_is_not_null}
qc_description <- "All participants should have their antimicrobials entered in a structured way and not in free text to facilitate the statistical analysis."
qc_rule <- action_alert_no_modification
qc_type <- "free_text_missing_structured_entry"
df <- day0_data
qc_text <- "free text drug"
qc_idx <- qc_free_text_rx_id
qc_export_label <- "free_text_drug"
qc_export_description <- "the treatments should have been entered in a structured manner"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_free_text_rx_cg <- n_detected
```

##### Discrepancies between drug re-entry and initial entries

To be added only for Kenya and Senegal

### Clinical measurements

```{r}
write(" o Clinical measurements", stderr())
```

```{r}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(spo2_meas1,
                         rr_meas),
                       as.numeric))
```

```{r, eval=!is_india}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(temp_meas),
                       as.numeric))
```

```{r, eval=is_india}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(temp_meas_farenheit),
                       as.numeric))
```

#### Temperature [Reasonability checks]

```{r}
write("   o Temperature", stderr())
```

```{r, results='asis', eval=day0_is_not_null&!is_india}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = temp_meas)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 0.2) +
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666") +
  ggplot2::geom_vline(aes(xintercept = 37.5),
                      color="blue",
                      linetype="dashed",
                      size=1) +
  ggplot2::coord_cartesian(xlim = c(30, 43), ylim = c(0, 1))
```

```{r, results='asis', eval=day0_is_not_null&!is_india}
dataMaid::identifyOutliers(day0_data$temp_meas,
                           nMax = 50)
```

```{r, results='asis', eval=day0_is_not_null&is_india}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = temp_meas_farenheit)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 0.2) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666") +
  ggplot2::geom_vline(aes(xintercept = 99.5),
                      color="blue",
                      linetype="dashed",
                      size=1) +
  ggplot2::coord_cartesian(xlim = c(86, 110), ylim = c(0, 1))
```

```{r, results='asis', eval=day0_is_not_null&is_india}
dataMaid::identifyOutliers(day0_data$temp_meas_farenheit,
                           nMax = 50)
```

```{r}
fig_df <- day0_data %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(end),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))
```

```{r}
fig_caption <- "Spatiotemporal pattern of temperature values"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
y_is_time <- FALSE
comparison <- "type"
```

```{r, eval=!is_india}
y_col <- "temp_meas"
y_lbl <- "Temperature (in °C)"
y_min <- 25
y_max <- 45
```

```{r, eval=is_india}
y_col <- "temp_meas_farenheit"
y_lbl <- "Temperature (in °F)"
y_min <- 90
y_max <- NA
```

```{r, results='asis', eval=timci::is_not_empty(day0_data)}
cat(knitr::knit_child('database_export_sub_facet_scatter_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Pulse oximetry [Reasonability checks]

```{r}
write("   o Pulse oximetry", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = spo2_meas1)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 1) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666") +
  ggplot2::coord_cartesian(xlim = c(75, 100), ylim = c(0, 0.6))
```

spo2_meas

```{r, results='asis', eval=day0_is_not_null}
dataMaid::identifyOutliers(day0_data$spo2_meas1,
                           nMax = 100)
```

```{r}
fig_df <- day0_data %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(end),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))
```

```{r}
fig_caption <- "Spatiotemporal pattern of oxygen saturation values"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
y_col <- "spo2_meas1"
y_lbl <- "Oxygen saturation (in %)"
y_is_time <- FALSE
y_min <- 0
y_max <- 100
comparison <- "type"
```

```{r, results='asis', eval=timci::is_not_empty(facility_data)}
cat(knitr::knit_child('database_export_sub_facet_scatter_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Respiratory rate [Reasonability checks]

```{r}
write("   o Respiratory rate", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = rr_meas)) +
  ggplot2::geom_histogram(ggplot2::aes(y = ..density..),
                          colour = "black",
                          fill = "white",
                          binwidth = 1) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill = "#FF6666") +
  ggplot2::coord_cartesian(xlim = c(0, 150), ylim = c(0, 0.12))
```

```{r, results='asis', eval=day0_is_not_null}
dataMaid::identifyOutliers(day0_data$rr_meas,
                           nMax = 150)
```

```{r}
fig_df <- day0_data %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(end),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))
```

```{r}
fig_caption <- "Spatiotemporal pattern of respiratory rate values"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
y_col <- "rr_meas"
y_lbl <- "Respiratory rate (in breaths/min)"
y_is_time <- FALSE
y_min <- 0
y_max <- 150
comparison <- "type"
```

```{r, results='asis', eval=timci::is_not_empty(facility_data)}
cat(knitr::knit_child('database_export_sub_facet_scatter_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

<!-- Multiple enrolments -->

```{r child_duplicate-subsection, child = 'database_export_sub_QC_child_multiple_enrolments.Rmd'}
```

### Pseudonymisation

```{r}
write(" o Pseudonymisation", stderr())
```

```{r}
allday0_data <- day0_data
out <- timci::extract_pii(day0_data,
                          is_pilot)
day0_data <- out[[1]]
```

Pseudonymisation is performed using a cryptographic hash function (md5) that takes strings as input and produces a random-like fixed-length output.

```{r}
day0_data <- day0_data %>%
  dplyr::rowwise() %>%
  dplyr::mutate(uuid = digest(uuid, algo = crypto_algo),
                child_id = digest(child_id, algo = crypto_algo),
                device_id = digest(device_id, algo = crypto_algo)) %>%
  dplyr::ungroup()
```

```{r}
n_cleaned_day0_records <- nrow(day0_data)
```

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
timci::create_day0_qc_flowchart(n_raw_day0_records,
                                n_nonvalid_fid_records,
                                n_incorrect_enroldate_records,
                                n_dropped_true_duplicate_records,
                                n_dropped_duplicate_records,
                                n_duplicate_edits,
                                n_missing_cp,
                                n_missing_diagnosis,
                                n_missing_referral_cg,
                                n_cleaned_day0_records)
```

### Data export

```{r}
write(" o Data export", stderr())
```

```{r, eval=!deidentification_on, results = 'asis'}
timci::dataset_export(raw_day0_data,
                      "02",
                      "timci_day0_data",
                      rctls_dir,
                      "Raw Day 0 data")
```

```{r, results = 'asis'}
timci::dataset_export(day0_data,
                      "02",
                      "timci_day0_data",
                      locked_db_dir,
                      "Cleaned Day 0 data")
```

```{r split-pii-from-research-data, eval=!is.null(facility_data)}
ts <- timci::export_df2xlsx(raw_pii,
                            tempdir(),
                            "timci_contact_data")
pii_pwd <- Sys.getenv("TIMCI_PII_PW")
zip(params$participant_zip, 
    files = file.path(tempdir(), "timci_contact_data.xlsx"), 
    flags = paste("-r9Xj --password", pii_pwd))
```

### Data summary statistics

```{r}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(form_version,
                         fid,
                         who_age_ctg,
                         district,
                         facility,
                         dob_knwn,
                         age_mo_knwn,
                         enrolled,
                         mother_education),
                       factor)) %>%
  dplyr::mutate(across(c(date_visit), ~format(as.Date(.), "%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start,
                         end), ~format(as.Date(.), "%Y-%m-%d %H:%M:%S")))
```

```{r, eval = (is_tanzania | is_kenya | is_senegal)}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(living_with_cg),
                       factor))
```

```{r, eval = (is_tanzania)}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(district_ra,
                         location_lvl1,
                         location_lvl2,
                         location_lvl3,
                         location_lvl4),
                       factor))
```

```{r, results='asis'}
skimr::skim(day0_data)
```

```{r, results='hide'}
rm(raw_day0_data)
gc()
```
