```{r}
write("Export screening data and run corresponding quality checks", stderr())
```

```{r}
###############################
# Screening quality check IDs #
###############################
qc_screening_w_nonvalid_deviceid <- "DQC_00_0SG_01"
qc_incorrect_date_setup <- "DQC_00_0SG_02"
qc_nontimely_submission_id <- "DQC_00_0SG_03"
qc_nontimely_completion_id <- "DQC_00_0SG_04"
qc_screening_before_startdate <- "DQC_00_0SG_05"
qc_screening_after_lockdate <- "DQC_00_0SG_06"
qc_screening_other_fids <- "DQC_00_0SG_07"
qc_inconsistent_age_info <- "DQC_00_0SG_08"
qc_underaged_cg_id <- "DQC_00_0SG_09"
qc_dup_repeats_id <- "DQC_00_0SG_10"
```

## Screening data quality checks and cleaning

```{r}
db_name <- "screening"

# Screening data
raw_screening_data <- timci::extract_screening_data(facility_data, is_pilot)

n_raw_screening_records <- nrow(raw_screening_data)

# Split into PII and deidentified raw data
out <- timci::extract_enrolled_participants(facility_data, is_pilot)
raw_day0_data <- out[[1]]
raw_pii <- out[[2]]
raw_repeat_data <- facility_data %>%
  dplyr::filter(repeat_consult == 1)
```

Initially, there are **`r n_raw_screening_records`** record(s) in the raw `r db_name` database from the start of the study on **`r start_date`**.

```{r}
n_inconsistent_age_info <- 0
```

### Format raw data

```{r}
dictionary <- timci::import_country_specific_xls_dict("main_dict.xlsx", Sys.getenv('TIMCI_COUNTRY'))
screening_dictionary <- subset(dictionary, screening == 1)
n_screening_dictionary_vars <- nrow(screening_dictionary)
```

There are **`r n_screening_dictionary_vars`** variables exported from the raw `r db_name` database.

```{r, results='asis'}
screening_dictionary %>%
  dplyr::select(new,
                old) %>%
  knitr::kable(col.names = c("Database reference",
                             "ODK reference"))
```

### Facilities

```{r}
write(" o Facility checks", stderr())
```

#### Non-valid device IDs [Context check `r qc_screening_w_nonvalid_deviceid`]

```{r}
write("\to Non-valid device IDs", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Devices different from the ones whose IDs are listed in Section 2.3 of this report are considered as *non-valid* and may have been used for instance for training purposes. Records submitted by non-valid devices should not be considered as part of the main database."
qc_rule <- "Records submitted by devices different from the ones listed in Section 2.3 of this report are deleted."
qc_type <- "nonvalid_deviceids"
df <- facility_data
qc_text <- "non-valid device IDs"
qc_idx <- qc_screening_w_nonvalid_deviceid
qc_export_label <- "nonvalid_deviceids"
qc_export_description <- "the device ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_deviceid_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

#### Facility IDs from other TIMCI studies [Context check `r qc_screening_other_fids`]

```{r}
write("\to Facility IDs from other facilities (India only)", stderr())
```

```{r}
qc_df <- NULL
n_other_fid_records <- 0
cleaned_df <- NULL
```

`r if ( !is_india ) { paste0('This check is only implemented for the India dataset.') }`

```{r, eval=facility_data_is_not_null&is_india, results='asis'}
qc_description <- "Records submitted by facilities which are part of a different TIMCI study and stored in the same ODK Central project should not be considered as part of the main database."
qc_rule <- "Records submitted by non-study facilities listed in Section 2.3 of this report are deleted."
qc_type <- "other_study_fids"
df <- facility_data
qc_text <- "facility IDs corresponding to another TIMCI study"
qc_idx <- qc_screening_other_fids
qc_export_label <- "screening_other_fids"
qc_export_description <- "the facility ID correspond to another TIMCI study"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_other_fid_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

#### Data from two different facilities collected on the same device on the same day

```{r}
write("\to Data from two different facilities collected on the same device on the same day (Tanzania only)", stderr())
```

Add correction from the field (to be implemented asap)

### Dates and times

```{r}
write(" o Date and time checks", stderr())
```

#### Incorrect date and time setup on the device [Context check `r qc_incorrect_date_setup`]

```{r}
write(" o Incorrect data and time setup on the device", stderr())
```

```{r, results='asis'}
qc_description <- "The enrolment date is defined as the creation (start) date of the form. However if for any reason the date is not setup correctly on the tablet, the enrolment date is not correct and follow-up is not triggered on the right date."
qc_rule <- "If the server submission date is anterior to the creation date (start of the form on the tablet) in the database, the creation date is considered incorrect and is replaced by the server submission date."
qc_type <- "date_discrepancy"
df <- facility_data
col_date1 <- "submission_date"
col_date2 <- "start"
cleaning <- "replace_by_start_date"
qc_text <- "an incorrect date setup on the tablet"
qc_idx <- qc_incorrect_date_setup
qc_export_label <- "incorrect_date_setup"
qc_export_description <- "the date setup is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_incorrect_date_setup_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>% 
  dplyr::mutate(week = lubridate::floor_date(as.Date(start),
                                             "week", 
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Incorrect date and time setup on the device"
facility_col <- "fid_from_device"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- ""

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Late submissions [Compliance check `r qc_nontimely_submission_id`]

```{r}
write(" o Non-timely submission", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day). A delay superior to 12 days mean that the participant has never appeared in the Day 7 follow-up log on the tablet."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- facility_data
col_date1 <- "end"
col_date2 <- "submission_date"
cleaning <- "none"
qc_text <- "an actual transfer date later than the finalisation date"
qc_idx <- qc_nontimely_submission_id
qc_export_label <- "nontimely_day0_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_late_submissions <- n_detected
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>% 
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(end), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = dplyr::case_when(
    diff < 3 ~ "a) Less than 3 days",
    diff >= 3 & diff < 7 ~ "b) 3-6 days",
    diff >= 7 ~ "c) 7 days and above"))

fig_caption <- "Submissions not transferred on the same day they were finalised"
facility_col <- "fid_from_device"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Late completions [Compliance check `r qc_nontimely_completion_id`]

```{r}
write(" o Non-timely completion", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- facility_data
col_date1 <- "start"
col_date2 <- "end"
cleaning <- "none"
qc_text <- "an actual finalisation date later than the start date"
qc_idx <- qc_nontimely_completion_id
qc_export_label <- "nontimely_day0_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_late_completions <- n_detected
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = dplyr::case_when(
    diff <= 1 ~ "a) 1 day",
    diff > 1 & diff < 3 ~ "b) 1-2 days",
    diff >= 3 ~ "c) 3 days and above"))

fig_caption <- "Number of submissions not finalised on the same day they were started"
facility_col <- "fid_from_device"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "type"
fill_col <- "Difference"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Study start date [Context check `r qc_screening_before_startdate`]

```{r}
write(" o Study start date context", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Screening data are considered valid only from the study start date. Data may have been entered before this date for training purposes."
qc_rule <- paste0("Records entered before the study start date on ", start_date, " are deleted")
qc_type <- "anterior_to_startdate"
df <- facility_data
qc_text <- paste0("an entry date anterior to the study start date on **", start_date, "**")
qc_idx <- qc_screening_before_startdate
qc_export_label <- "anterior_to_startdate"
qc_export_description <- "the entry date is anterior to the study start date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
facility_data_before_start <- qc_df %>%
  dplyr::select(date_visit, child_id)
n_before_startdate_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

#### Study lock date [Context check `r qc_screening_after_lockdate`]

```{r}
write(" o Study lock date context", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Screening data are considered valid only until the date for the lock. Note that follow-up data will be managed differently, since they are considered valid after the lock data as soon as they correspond to a participant enrolled before the date of the lock."
qc_rule <- paste0("Records entered after the lock date on ", lock_date, " are deleted")
qc_type <- "posterior_to_lockdate"
df <- facility_data
qc_text <- paste0("an entry date posterior to the lock date on **", lock_date, "**")
qc_idx <- qc_screening_after_lockdate
qc_export_label <- "posterior_to_lockdate"
qc_export_description <- "the entry date ID is posterior to the lock date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
facility_data_after_lock <- qc_df %>%
  dplyr::select(date_visit, child_id)
n_after_lockdate_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

#### Entry times [Context check `r qc_screening_after_lockdate`]

```{r}
write(" o Data entry times", stderr())
```

```{r, results='asis', eval=timci::is_not_empty(facility_data)}
fig_df <- facility_data %>%
  dplyr::mutate(start_time1 = as.POSIXct(paste0("2021-01-01 ", start_time),
                                         tz = Sys.getenv("TZ"))) %>% 
  dplyr::mutate(week = lubridate::floor_date(as.Date(end),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Spatiotemporal pattern of data entry times"
facility_col <- "fid_from_device"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
y_col <- "start_time1"
y_lbl <- "Start time of record entry"
y_is_time <- TRUE
time_break_str <- "4 hours"
time_format <- "%H:%M"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_scatter_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Participant eligibility

#### Caregiver eligibility [Compliance check `r qc_underaged_cg_id`]

```{r}
write(" o Caregiver eligibility", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Caregivers must be above 18 years old to be able provide consent for the child to be part in the study."
qc_rule <- "Children with a caregiver below 18 years old are kept in the screening database but excluded from the study."
qc_type <- "underaged_cg"
df <- facility_data
qc_text <- "a consenting caregiver below 18 years old"
qc_idx <- qc_underaged_cg_id
qc_export_label <- "underaged_cg"
qc_export_description <- "the consenting caregiver is below 18 years old"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_ineligible_cg_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

#### Repeat visits incorrectly recorded as new enrolments [Compliance check `r paste0(qc_dup_repeats_id, "a")`]

```{r}
write(" o Repeat visits incorrectly recorded as new enrolments", stderr())
```

`r if ( is_tanzania | is_ls ) { paste0('* Initial check ', qc_dup_repeats_id, 'a') }`

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Participants who came back to the facility between 1 and 28 days after their enrolment should be recorded as repeat visits. If they are recorded as new enrolments with the same participant ID they were initially given, this artificially creates duplicates in the database."
qc_rule <- "Repeat visits incorrectly recorded as new enrolments are detected and corrected proactively were possible."
qc_type <- "duplicates_check_pii"
df <- facility_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- paste0(qc_dup_repeats_id, "a")
qc_export_label <- "timci_repeat_visit_duplicates"
qc_export_description <- "the repeat visit was allocated the same ID that has been used for another participant in the database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>% 
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(date_2), "week", week_start = getOption("lubridate.week.start", 1)))) %>%
  dplyr::mutate(fid = substr(id, 3, 7))

fig_caption <- "Repeat visits incorrectly recorded as new enrolments"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"

cat(knitr::knit_child('database_export_sub_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if ( is_tanzania | is_ls ) { '* Manual correction of repeat visits recorded as duplicated IDs' }`

```{r}
n_repeat_edit_records <- 0
```

```{r, eval = (is_tanzania | is_ls), results='asis'}
# Parameters for manual corrections
mc_description <- paste0('Confirmed repeat records are manually edited in the ', db_name, ' database as described below: variable *repeat_consult* set to *1* variable *consent* set to *NA* variable *enrolled* set to *NA*')
to_mc_df <- facility_data
correction_type <- "convert_screening_from_day0_to_repeat"

# Parameters for the quality check following manual corrections
qc_description <- "Remaining repeat visits incorrectly recorded as new enrolments are deleted from the database."
qc_idx <- paste0(qc_dup_repeats_id, "b")

cat(knitr::knit_child('database_export_sub_corrections.Rmd',
                      envir = environment(),
                      quiet = TRUE))
facility_data <- mc_df
n_repeat_edit_records <- n_mc
```

### Misc

#### Missing young infant child age category [Mandatory check `r qc_inconsistent_age_info`]

```{r}
write(" o Discrepancy in child age and categories", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Age group consistent with young infants flag and categories as specified in the codebook."
qc_rule <- action_alert_no_modification
qc_type <- "blank_value"
df <- facility_data %>%
  dplyr::filter(yg_infant == 1)
col_value <- "who_age_ctg"
qc_text <- "missing young infant age category"
qc_idx <- qc_inconsistent_age_info
qc_export_label <- "inconsistent_age_info"
qc_export_description <- "age information is inconsistent"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_inconsistent_age_info <- n_detected
```

```{r, results='asis'}
ggplot2::ggplot(facility_data,
                ggplot2::aes(x = who_age_ctg,
                             fill = yg_infant)) +
    ggplot2::geom_bar(position = "stack") +
    ggplot2::theme(text = element_text(size = tsize),
                   panel.grid.major.x = element_blank(),
                   panel.grid.minor.x = element_blank())
```

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
screening_data <- timci::extract_screening_data(facility_data,
                                                is_pilot)
n_cleaned_screening_records <- nrow(screening_data)
```

```{r, fig.asp=1}
timci::create_screening_qc_flowchart(n_raw_screening_records,
                                     n_nonvalid_deviceid_records,
                                     n_other_fid_records,
                                     n_before_startdate_records,
                                     n_after_lockdate_records,
                                     n_ineligible_cg_records,
                                     n_repeat_edit_records,
                                     n_incorrect_date_setup_records,
                                     n_late_submissions,
                                     n_late_completions,
                                     n_inconsistent_age_info,
                                     n_cleaned_screening_records)
```

### Data overview

```{r}
write(" o Data overview", stderr())
```

```{r, results='asis', eval=timci::is_not_empty(screening_data), results='asis'}
fig_df <- screening_data %>%
  dplyr::mutate(Status = dplyr::case_when(
    repeat_consult == 1 ~ "Repeat visit",
    consent == 1        ~ "Newly enrolled",
    .default            = "Not enrolled")) %>% 
  dplyr::mutate(week = lubridate::floor_date(as.Date(start),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Screening data overview over time by facility"
facility_col <- "fid_from_device"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Status"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
screening_data <- screening_data %>%
  dplyr::mutate(across(c(device_id,
                         sys_submit_id,
                         form_version,
                         fid,
                         fid_from_device,
                         who_age_ctg,
                         district,
                         facility,
                         dob_knwn,
                         age_mo_knwn,
                         consult_reason,
                         main_cg,
                         main_cg_lbl,
                         repeat_consult,
                         consent,
                         enrolled),
                       factor)) %>%
  dplyr::mutate(across(c(age_yr,
                         age_mo),
                       as.integer)) %>% 
  dplyr::mutate(across(c(date_visit),
                       ~format(as.POSIXct(.),"%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start,
                         end,
                         submission_date),
                       as.POSIXct))
```

```{r, results='asis'}
skimr::skim(screening_data)
```

### Data export

```{r}
write(" o Data export", stderr())
```

```{r, eval = TRUE, results = 'asis'}
timci::dataset_export(facility_data,
                      "01",
                      "timci_facility_data",
                      rctls_dir,
                      "Raw screening data")
```

```{r export-screening-data, results = 'asis'}
timci::dataset_export(raw_screening_data,
                      "01",
                      "timci_screening_data",
                      rctls_dir,
                      "Raw screening data")
```

```{r export-locked-screening-data, results = 'asis'}
timci::dataset_export(screening_data,
                      "01",
                      "timci_screening_data",
                      locked_db_dir,
                      "Cleaned screening data")
```

```{r export-facility-audit, results = 'asis'}
timci::dataset_export(facility_data_audit,
                      "00",
                      "timci_facility_audit_data",
                      rctls_dir,
                      "Screening audit data")
```

```{r}
rm(raw_screening_data,
   screening_data,
   facility_data_audit)
gc()
```
