#### Detection of brand names for Amoxicillin in free text entries [`r qc_missing_structured_entry_amox`]

```{r}
qc_description <- "All participants should have where possible a structured entry of their treatment at the facility for their Day 0 visit."
qc_rule <- action_alert_no_modification
qc_type <- "missing_structured_entry_for_specific_drug"
df <- day0_data
```

```{r}
write(" o Detection of brand names for Amoxicillin in free text entries", stderr())
```

Clamoxyl, Bactox, Alfamox, Teramox and Hiconcil in Senegal

```{r, results='asis', eval=timci::is_not_empty(day0_data)}
drug_val_col <- "rx_amoxicillin"
drug_text_col <- "rx_misc_oth"
drug_vec <- c("alfamox", "bactox", "clamoxyl", "teramox", "hiconcil")
qc_text <- "missing structured entry for Amoxicillin"
qc_idx <- qc_missing_structured_entry_amox
qc_export_label <- "missing_str_entry_amox"
qc_export_description <- "the structured entry for Amoxicillin is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Detection of brand names for amoxicillin + clavulanic acid in free text entries

```{r}
write(" o Detection of brand names for amoxicillin + clavulanic acid in free text entries", stderr())
```

Fleming, Amoxiclav, Soclav, Augmentin in Senegal

#### Detection of brand names for cotrimoxazole in free text entries [`r qc_missing_structured_entry_ctx`]

```{r}
write(" o Detection of brand names for cotrimoxazole in free text entries", stderr())
```

Phartrim and Bactrim in Senegal

```{r, results='asis', eval=timci::is_not_empty(day0_data)}
drug_val_col <- "rx_cotrimoxazole"
drug_text_col <- "rx_misc_oth"
drug_vec <- c("phartrim", "bactrim")
qc_text <- "missing structured entry for Cotrimoxazole"
qc_idx <- qc_missing_structured_entry_ctx
qc_export_label <- "missing_str_entry_ctx"
qc_export_description <- "the structured entry for Cotrimoxazole is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Detection of brand names for metronidazole in free text entries

```{r}
write(" o Detection of brand names for metronidazole in free text entries", stderr())
```

Flagyl

#### Detection of brand names for ampicillin in free text entries

```{r}
write(" o Detection of brand names for ampicillin in free text entries", stderr())
```

Totapen in Senegal
