## Screening data quality checks\n\n

```{r}
write("Export screening data and run corresponding quality checks", stderr())
```

```{r}
db_name <- "screening"

facility_data_is_not_null <- !is.null(facility_data)

raw_screening_data <- timci::extract_screening_data(facility_data)
n_raw_screening_records <- nrow(raw_screening_data)

out <- timci::extract_enrolled_participants(facility_data)
raw_day0_data <- out[[1]]
raw_pii <- out[[2]]
```

Initially, there are **`r n_raw_screening_records`** record(s) in the raw `r db_name` database from the start of the study on **`r start_date`**.

### Non-valid device IDs [context check `r qc_screening_w_nonvalid_deviceid`]\n\n

```{r}
write(" o Non-valid device IDs", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Devices different from the ones whose IDs are listed in Section 2.3 of this report are considered as *non-valid* and may have been used for instance for training purposes. Records submitted by non-valid devices should not be considered as part of the main database."
qc_rule <- "Records submitted by devices different from the ones listed in Section 2.3 of this report are deleted."
qc_type <- "nonvalid_deviceids"
df <- facility_data
qc_text <- "non-valid device IDs"
qc_idx <- qc_screening_w_nonvalid_deviceid
qc_export_label <- "nonvalid_deviceids"
qc_export_description <- "the device ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_deviceid_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Caregiver eligibility [compliance check `r qc_underaged_cg_id`]\n\n

```{r}
write(" o Caregiver eligibility", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Caregivers must be above 18 years old to be able provide consent for the child to be part in the study."
qc_rule <- "Children with a caregiver below 18 years old are deleted from the database."
qc_type <- "underaged_cg"
df <- facility_data
qc_text <- "a consenting caregiver below 18 years old"
qc_idx <- qc_underaged_cg_id
qc_export_label <- "underaged_cg"
qc_export_description <- "the consenting caregiver is below 18 years old"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_ineligible_cg_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Repeat visits incorrectly recorded as new enrolments [compliance checks]

```{r}
write(" o Repeat visits incorrectly recorded as new enrolments", stderr())
```

`r if ( is_tanzania ) { paste0('#### Initial check [compliance check ', qc_dup_repeats_id1, ']\n\n') }`

```{r, eval=facility_data_is_not_null&(is_tanzania), results='asis'}
qc_description <- "Participants who come back within 28 days after their enrolment should be recorded as repeat visits. If they are recorded as new enrolments with their participant ID, this creates duplicates in the database."
qc_rule <- "Repeat visits incorrectly recorded as new enrolments are detected and corrected proactively were possible."
qc_type <- "duplicates_check_pii"
df <- facility_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_dup_repeats_id1
qc_export_label <- "timci_repeat_visit_duplicates"
qc_export_description <- "the repeat visit was allocated the same ID that has been used for another participant in the databse"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if ( is_tanzania ) { '#### Manual correction of repeat visits recorded as duplicated IDs\n\n' }`

`r if ( is_tanzania ) { paste0('Confirmed repeat records are manually edited in the ', db_name, ' database as described below:\n\n* variable *repeat_consult* set to 1\n\n* variable *consent* set to NA\n\n* variable *enrolled* set to NA') }`

```{r}
repeat_visit_edits_is_not_empty <- FALSE
edited_records_status_update <- ""
n_repeat_edit_records <- 0
```

```{r, eval=is_tanzania}
out <- timci::edit_day0_to_repeat(facility_data)
facility_data <- out[[1]]
repeat_visit_edits <- out[[2]]
repeat_visit_edits_is_not_empty <- timci::is_not_empty(repeat_visit_edits)
n_repeat_edit_records <- nrow(repeat_visit_edits)
```

```{r, eval=repeat_visit_edits_is_not_empty}
edited_records_status_update <- paste0('**', n_repeat_edit_records, '** record(s) manually corrected in the ', db_name, ' database.')
```

`r edited_records_status_update`

```{r, eval=repeat_visit_edits_is_not_empty, results='asis'}
repeat_visit_edits %>%
  select(old_child_id, uuid) %>%
  knitr::kable()
```

`r if ( is_tanzania ) { paste0('#### Final check after manual edits [compliance check ', qc_dup_repeats_id2, ']\n\n') }`

```{r, eval=facility_data_is_not_null&is_tanzania, results='asis'}
qc_description <- "Remaining repeat visits incorrectly recorded as new enrolments are deleted from the database." 
qc_rule <- action_alert_no_modification
qc_type <- "duplicates_check_pii"
df <- facility_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_dup_repeats_id2
qc_export_label <- "timci_repeat_visit_duplicates"
qc_export_description <- "the repeat visit was allocated the same ID that has been used for another participant in the databse"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Lock date [context check `r qc_screening_after_lockdate`]\n\n

```{r}
write(" o Lock date context", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Screening data are considered valid only until the date for the lock. Note that follow-up data will be managed differently, since they are considered valid after the lock data as soon as they correspond to a participant enrolled before the date of the lock."
qc_rule <- paste0("Records entered after the lock date on ", lock_date, " are removed in the locked database.")
qc_type <- "posterior_to_lockdate"
df <- facility_data
qc_text <- paste0("an entry date posterior to the lock date on **", lock_date, "**")
qc_idx <- qc_screening_after_lockdate
qc_export_label <- "posterior_to_lockdate"
qc_export_description <- "the device ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
facility_data_after_lock <- qc_df
n_after_lockdate_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Data cleaning summary\n\n

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
screening_data <- timci::extract_screening_data(facility_data)
n_cleaned_screening_records <- nrow(screening_data)
```

```{r}
timci::create_screening_qc_flowchart(n_raw_screening_records,
                                     n_nonvalid_deviceid_records,
                                     n_after_lockdate_records,
                                     n_ineligible_cg_records,
                                     n_repeat_edit_records,
                                     n_cleaned_screening_records)
```

### Data export\n\n

```{r}
write(" o Data export", stderr())
```

```{r export-screening-data, results = 'asis'}
timci::dataset_export(raw_screening_data,
                      "01",
                      "timci_screening_data",
                      rctls_dir,
                      "Raw screening data")
```

```{r export-locked-screening-data, results = 'asis'}
timci::dataset_export(screening_data,
                      "01",
                      "timci_screening_data",
                      locked_db_dir,
                      "Cleaned screening data")
```

```{r export-facility-audit, results = 'asis'}
timci::dataset_export(facility_data_audit,
                      "00",
                      "timci_facility_audit_data",
                      rctls_dir,
                      "Screening audit data")
```
