```{r}
write("Export Day 0 data and run corresponding quality checks", stderr())
```

## Day 0 quality checks\n\n

```{r}
out <- timci::extract_enrolled_participants(locked_facility_data)
day0_data <- out[[1]]
pii <- out[[2]]
```

```{r}
day0_is_not_null <- !is.null(day0_data)
day0_is_not_empty <- timci::is_not_empty(day0_data)
```

```{r}
n_raw_day0 <- nrow(day0_data)
```

Among the **`r n_locked_screening`** cleaned screening record(s), there are **`r n_raw_day0`** record(s) corresponding to new Day 0 enrolment(s) in the `r db_name` database.

```{r}
db_name <- "Day 0"
locked_day0_data <- day0_data
```

### Non-valid enrolling facility IDs [compliance checks]\n\n

`r if (is_kenya) { paste0('#### Initial check [compliance check', qc_nonvalid_fid1, ']\n\n') }`

```{r, eval=(day0_is_not_null&is_kenya), results='asis'}
qc_description <- "The facility ID (Fxxxx) is extracted from the participant enrolment ID (X-Fxxxx-Pxxxx). It should correspond to the ID of one of the research facility listed in Section 2.2 of this report."
qc_rule <- "Records corresponding to facility IDs not listed in Section 2.2 of this report are detected and manually corrected before Day 7 follow-up is conducted where possible."
qc_type <- "nonvalid_ids_no_cleaning"
df <- lock_day0_data
idcol1 <- "fid"
refdf <- research_facilities
idcol2 <- "facility_id"
qc_text <- "facility ID not valid"
qc_idx <- qc_nonvalid_fid1
qc_export_label <- "nonvalid_fids"
qc_export_description <- "the facility ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if (is_kenya) {'#### Facility ID manual edits\n\n'}`

```{r, results='asis', eval=is_kenya}
out <- timci::correct_day0_non_valid_facilities(day0_data)
locked_day0_data <- out[[1]]
facility_edits <- out[[2]]
if (!is.null(facility_edits)) {
  facility_edits %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

`r if (is_kenya) { paste0('#### Second check after manual edits [compliance check', qc_nonvalid_fid2, ']\n\n') }`

```{r, eval=!is.null(locked_day0_data), results='asis'}
qc_description <- ""
qc_rule <- "Records corresponding to facility IDs not listed in Section 2.2 of this report are removed."
qc_type <- "nonvalid_ids"
df <- locked_day0_data
idcol1 <- "fid"
refdf <- research_facilities
idcol2 <- "facility_id"
qc_text <- "facility ID not valid"
qc_idx <- qc_nonvalid_fid2
qc_export_label <- "nonvalid_fids"
qc_export_description <- "the facility ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
locked_day0_data <- cleaned_df
n_nonvalid_fids <- nrow(qc_df)
```

`r if (is_india) {'### Inconsistent facility information [Context check]\n\n'}`

`r if (is_india) {'**Rule**: records with inconsistent facility information are kept in the locked database, but will need to be checked more carefully (e.g: GPS data).\n\n'}`

```{r}
qc_inconsistent_facility <- NULL
if (Sys.getenv('TIMCI_COUNTRY') == 'India') {
  if (!is.null(locked_day0_data)) {
    if (nrow(locked_day0_data) > 0) {
      qc_inconsistent_facility <- locked_day0_data[locked_day0_data$fid != locked_day0_data$fid_ra, ]
      qc_inconsistent_facility <- qc_inconsistent_facility[c("child_id", "fid", "fid_ra", "uuid")]
    }
  }
}
```

```{r, results='asis'}
if (!is.null(qc_inconsistent_facility)) {
  if (nrow(qc_inconsistent_facility) > 0) {
    cat(paste0("**", nrow(qc_inconsistent_facility), "** record(s) with inconsistent facility information detected."))
  }
}
```

```{r, results='asis'}
if (!is.null(qc_inconsistent_facility)) {
  if (nrow(qc_inconsistent_facility) > 0) {
    qc_inconsistent_facility %>%
      knitr::kable(row.names = FALSE)
  }
}
```

### Caregiver eligibility [compliance check `r qc_underaged_cg_id`]\n\n

```{r, eval=!is.null(locked_day0_data), results='asis'}
qc_description <- "Caregivers must be above 18 years old to be able provide consent for the child to be part in the study."
qc_rule <- "Children with a caregiver below 18 years old are removed from the database."
qc_type <- "underaged_cg"
df <- locked_day0_data
qc_text <- "a consenting caregiver below 18 years old"
qc_idx <- qc_underaged_cg_id
qc_export_label <- "underaged_cg"
qc_export_description <- "the consenting caregiver is below 18 years old"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
locked_day0_data <- cleaned_df
n_ineligible_cg <- nrow(qc_df)
```

### Incorrect enrolment date [context check `r qc_incorrect_enrolment_date`]\n\n

```{r, eval=!is.null(locked_day0_data), results='asis'}
qc_description <- "The enrolment date is defined as the start date of the form. However if research assistants reuse on old form to enrol a new participant, it is possible that the date on which the name of the participant is entered in the form is not on the same day it was started. As a consequence the enrolment date would not be correct."
qc_rule <- "No modification of the database, only reporting."
qc_type <- "date_discrepancy"
df <- locked_day0_data
col_date1 <- "start"
col_date2 <- "start_contact"
qc_text <- "an incorrect enrolment date"
qc_idx <- qc_incorrect_enrolment_date
qc_export_label <- "incorrect_enrolment_date"
qc_export_description <- "the enrolment date is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Non-timely completion [compliance check `r qc_nontimely_completion_id`]\n\n

```{r, eval=!is.null(locked_day0_data), results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- "No modification of the database, only reporting."
qc_type <- "date_discrepancy"
df <- locked_day0_data
col_date1 <- "start"
col_date2 <- "end"
qc_text <- "the submission was not finalised on the same day it was started"
qc_idx <- qc_nontimely_completion_id
qc_export_label <- "nontimely_day0_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Days between submission start and finalisation" ,
     ylab="Occurences",
     main="")
```

### Non-timely submission [compliance check `r qc_nontimely_submission_id`]\n\n

```{r, eval=!is.null(locked_day0_data), results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day). A delay superior to 12 days mean that the participant has never appeared in the Day 7 follow-up log on the tablet."
qc_rule <- "No modification of the database, only reporting."
qc_type <- "date_discrepancy"
df <- locked_day0_data
col_date1 <- "end"
col_date2 <- "submission_date"
qc_text <- "the submission was not transferred on the same day it was finalised"
qc_idx <- qc_nontimely_submission_id
qc_export_label <- "nontimely_day0_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Days between submission start and finalisation" ,
     ylab="Occurences",
     main="")
```

### Duplicate management\n\n

`r if ( is_tanzania | is_kenya | is_senegal ) { paste0('#### Initial check [compliance check ', qc_duplicate_id1, ']\n\n') }`

```{r, eval=!is.null(locked_day0_data)&(is_tanzania|is_kenya), results='asis'}
qc_description <- "All participants should have a distinct ID. Duplicated IDs generate errors for the conduct of follow-ups and lead to ambiguities once the database is deidentified."
qc_rule <- "child ID duplicates are detected and corrected proactively were possible."
qc_type <- "duplicates"
df <- locked_day0_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicate_id1
qc_export_label <- "timci_day0_data_id_duplicates"
qc_export_description <- "the submission was allocated the same ID that has been used for another participant in the databse"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if ( is_tanzania ) { '#### Test/dummy data manual deletion\n\n' }`

```{r, results='asis'}
out <- timci::delete_day0_child_ids(locked_day0_data)
locked_day0_data <- out[[1]]
dropped_records <- out[[2]]
if (!is.null(dropped_records)) {
  dropped_records %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

`r if ( is_tanzania ) { '#### Child ID repeat visit manual correction\n\n' }`

```{r, results='asis'}
out <- timci::edit_day0_child_ids(locked_day0_data)
locked_day0_data <- out[[1]]
duplicate_edits <- out[[2]]
if (!is.null(duplicate_edits)) {
  duplicate_edits %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

`r if ( is_tanzania | is_kenya | is_senegal ) { '#### Child ID duplicate manual edits\n\n' }`

```{r, results='asis'}
out <- timci::edit_day0_child_ids(locked_day0_data)
locked_day0_data <- out[[1]]
duplicate_edits <- out[[2]]
if (!is.null(duplicate_edits)) {
  duplicate_edits %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

`r if ( is_tanzania | is_kenya | is_senegal ) { paste0('#### Second check after manual edits [compliance check ', qc_duplicate_id2, ']\n\n') }`

```{r, eval=!is.null(locked_day0_data), results='asis'}
qc_description <- "All participants should have a distinct ID. Duplicated IDs generate errors for the conduct of follow-ups and lead to ambiguities once the database is deidentified."
qc_rule <- "Remaining child ID duplicates are removed in the database."
qc_type <- "duplicates"
df <- locked_day0_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "drop_all"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicate_id2
qc_export_label <- "timci_day0_data_id_duplicates"
qc_export_description <- "the submission was allocated the same ID that has been used for another participant in the database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
locked_day0_data <- cleaned_df
```

### Possible multiple enrolments\n\n

```{r}
multiple <- FALSE
```

```{r child_duplicate-subsection, child = if ( multiple ) 'database_export_sub_QC_child_multiple_enrolments.Rmd'}
```

### Withdrawal management\n\n

```{r, child = if(day0_is_not_empty) 'database_export_sub_rctls_withdrawals.Rmd'}
```

### Clinical presentation [Mandatory check `r qc_missing_cp_id`]\n\n

```{r, results='asis', eval=!is.null(locked_day0_data)}
qc_description <- "All participants should have complete information about their clinical presentation, i.e. a participant cannot have simultaneously:

* No convulsions (*sx_convulsions* != 1)
* No lethargy (*sx_lethargy* != 1)
* No vomiting (*sx_vomit* = 0 or *sx_vomit* = 98)
* No feeding less than usual (sx_less_feed = 0 or sx_less_feed = 98)
* No cough (sx_cough = 0 or sx_cough = 98)
* No difficulty breathing (sx_difficulty_breath = 0 or sx_difficulty_breath = 98)
* No diarrhoea (sx_diarrhoea = 0 or sx_diarrhoea = 98)
* No fever (sx_fever = 0 or sx_fever = 98)
* No other complaint (sx_var = 96)"
qc_rule <- "No modification of the database, only reporting."
qc_type <- "missing_clinical_presentation"
df <- locked_day0_data
qc_text <- "missing clinical presentation"
qc_idx <- qc_missing_cp_id
qc_export_label <- "missing_clinical_presentation"
qc_export_description <- "the clinical presentation is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_cp <- n_detected
```

### Diagnosis [Mandatory check `r qc_missing_diagnosis_id`]\n\n

```{r, results='asis', eval=!is.null(locked_day0_data)}
qc_description <- "All participants should have complete information about their diagnosis for their Day 0 visit."
qc_rule <- "No modification of the database, only reporting."
qc_type <- "missing_diagnosis"
df <- locked_day0_data
qc_text <- "missing diagnosis"
qc_idx <- qc_missing_diagnosis_id
qc_export_label <- "missing_diagnosis"
qc_export_description <- "the diagnosis is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_diagnosis <- n_detected
```

### Referral [Mandatory check `r qc_missing_referral_id`]\n\n

```{r, results='asis', eval=!is.null(locked_day0_data)}
qc_description <- "All participants should have complete information about the management at the facility for their Day 0 visit. This information is collected from 2 soures: the caregiver at the exit of the consultation and the facility registries/consultation notes. However, caregivers may be lost at the exit of the consultation, so that the referral information from this source would then be missing."
qc_rule <- "No modification of the database, only reporting."
qc_type <- "missing_referral"
df <- locked_day0_data
qc_text <- "missing referral information (source: caregiver at the exit of the consultation)"
qc_idx <- qc_missing_referral_id
qc_export_label <- "missing_referral_cg"
qc_export_description <- "the referral information that should have been obtained from the caregiver at the exit of the consultation is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_referral_cg <- n_detected
```

### Referral [Context check `r qc_missing_referral_id`]\n\n

To be updated

### Data cleaning summary\n\n

```{r, results = 'asis'}
timci::format_nrow("There are", locked_day0_data, "records in the locked Day 0 database.")
```

```{r}
timci::create_day0_qc_flowchart(n_raw_day0,
                                n_nonvalid_fids,
                                n_ineligible_cg,
                                nrow(locked_day0_data),
                                'NA',
                                'NA',
                                'NA',
                                'NA')
```

### Data export\n\n

```{r, eval=(!is.null(facility_data) & deidentification_on)}
deidentified_day0_data <- timci::deidentify_data(day0_data)
locked_day0_data <- timci::deidentify_data(locked_day0_data)
```

```{r, eval=!deidentification_on, results = 'asis'}
timci::dataset_export(day0_data,
                      "02",
                      "timci_day0_data",
                      rctls_dir,
                      "Raw Day 0 data")
```

```{r, eval=deidentification_on, results = 'asis'}
timci::dataset_export(deidentified_day0_data,
                      "02",
                      "timci_day0_data",
                      rctls_dir,
                      "Deidentified raw Day 0 data")
```

```{r, results = 'asis'}
timci::dataset_export(locked_day0_data,
                      "02",
                      "timci_day0_data",
                      locked_db_dir,
                      "Cleaned Day 0 data")
```

```{r split-pii-from-research-data, eval=!is.null(facility_data)}
ts <- timci::export_df2xlsx(pii,
                            tempdir(),
                            "timci_contact_data")
pii_pwd <- Sys.getenv("TIMCI_PII_PW")
zip(params$participant_zip, 
    files = file.path(tempdir(), "timci_contact_data.xlsx"), 
    flags = paste("-r9Xj --password", pii_pwd))
```

```{r export-visit-data, results = 'asis', eval=!is.null(facility_data)}
study_data <- timci::extract_all_visits(facility_data)
```

```{r, eval=!deidentification_on, results = 'asis'}
timci::dataset_export(study_data,
                      "03",
                      "timci_facility_visits_data",
                      rctls_dir,
                      "Facility visit data")
```

```{r, eval=deidentification_on, results = 'asis'}
deidentified_facility_data <- timci::deidentify_data(study_data)
timci::dataset_export(deidentified_facility_data,
                      "03",
                      "timci_facility_visits_data",
                      rctls_dir,
                      "Facility visit data")
```
