## Day 7 follow-up outcome data quality checks\n\n

```{r}
write("Export Day 7 follow-up outcome data (successful follow-ups only) and run corresponding quality checks", stderr())
```

This section only focus on successful follow-ups, i.e. follow-ups where the participant was successfully reached and where follow-up outcomes were collected.

```{r}
day7fu_data <- allday7fu_data %>%
  dplyr::filter ( proceed_day7 == 1 )
n_raw_successday7fu_records <- nrow(day7fu_data)
day7fu_is_not_null <- !is.null(day7fu_data)
day7fu_is_not_empty <- timci::is_not_empty(day7fu_data)
```

Among the **`r n_cleaned_allday7fu_records`** cleaned **`r db_name`** record(s), there are **`r n_raw_successday7fu_records`** record(s) corresponding to successful Day 7 follow-up(s).

```{r, eval=day7fu_is_not_empty}
day7fu_data <- day7fu_data %>%
  dplyr::mutate(window = ifelse(days >= 7 & days <= 10, 1, 0))
```

### Duplicate management\n\n

#### Successful follow-up duplicates [compliance check `r qc_duplicated_day7fu`]\n\n

```{r}
write(" o Successful follow-up duplicates", stderr())
```

`r if (is_kenya) {'##### Initial check'}`

```{r, eval=!is.null(day7fu_data)&is_kenya, results='asis'}
qc_description <- "It is possible to have more than one successful follow-up records available for the same participant."
qc_rule <- "Identify duplicated records that correspond to different participants (participants for whom duplicates were created at enrolment) and reallocate these records to the appropriate participant."
qc_type <- "duplicates"
df <- day7fu_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicated_day7fu
qc_export_label <- "duplicated_successful_day7fu"
qc_export_description <- "Day 7 follow-ups are duplicated"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if (is_kenya) {'##### Child ID duplicate manual edits'}`

```{r, results='asis', eval=is_kenya}
out <- timci::correct_day7_duplicates(day7fu_data)
day7fu_data <- out[[1]]
duplicate_edits <- out[[2]]
if (!is.null(duplicate_edits)) {
  duplicate_edits %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

`r if (is_kenya) {'##### Final check after manual edits'}`

```{r, eval=!is.null(day7fu_data), results='asis'}
qc_description <- "It is possible to have more than one successful follow-up records available for the same participant. In this case, following the guidance from the statistical analysis plan, Only the most recent successful Day 7 follow-up is kept."
qc_rule <- "Delete all older records and keep only the most recent when more than one successful follow-up is available for the same participant."
qc_type <- "duplicates"
df <- day7fu_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "keep_latest"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicated_day7fu
qc_export_label <- "duplicated_successful_day7fu"
qc_export_description <- "Day 7 follow-ups are duplicated"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_dropped_duplicate_day7fu_records <- nrow(day7fu_data) - nrow(cleaned_df)
day7fu_data <- cleaned_df
```

### Invalid date of hospitalisation [context check `r qc_hospit_before_enrolment_day7fu`]\n\n

```{r, eval=!is.null(day7fu_data), results='asis'}
qc_description <- "The reported hospital visit should have happened between enrolment at Day 0 and the Day 7 follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day7fu_data %>% 
  merge(day0_data,
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_hosp_day7"
col_date2 <- "date_visit"
qc_text <- "a date of hospitalisation before the enrolment date"
qc_idx <- qc_hospit_before_enrolment_day7fu
qc_export_label <- "hospit_before_enrolment"
qc_export_description <- "the reported date of hospitalisation was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Invalid date of death [context check `r qc_death_before_enrolment_day7fu`]\n\n

```{r, eval=!is.null(day7fu_data), results='asis'}
qc_description <- "The reported death should have happened between enrolment at Day 0 and the Day 7 follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day7fu_data %>% 
  merge(day0_data,
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_death_day7"
col_date2 <- "date_visit"
qc_text <- "a date of death before the enrolment date"
qc_idx <- qc_death_before_enrolment_day7fu
qc_export_label <- "death_before_enrolment"
qc_export_description <- "the reported date of death was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Data cleaning summary\n\n

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
n_cleaned_day7fu_records <- nrow(day7fu_data)
```

```{r}
timci::create_day7fu_outcome_qc_flowchart(n_raw_successday7fu_records,
                                          n_dropped_duplicate_day7fu_records,
                                          n_cleaned_day7fu_records)
```

### Data export\n\n

```{r}
write(" o Data export", stderr())
```

```{r, results = 'asis'}
timci::dataset_export(raw_successday7fu_data,
                      "04b",
                      "timci_followup_successful_day7_data",
                      rctls_dir,
                      "Raw successful Day 7 follow-up only)")
```

```{r}
day7fu_data <- day7fu_data %>%
  dplyr::mutate(across(c(device_id,
                         sys_submit_id,
                         cg_reached,
                         cg_ok,
                         status_day7,
                         cure_day7,
                         admission),
                       factor)) %>%
  dplyr::mutate(across(c(date_call,
                         date_hosp_day7),
                       ~format(as.Date(.), "%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start,
                         end),
                       ~format(as.Date(.), "%Y-%m-%d %H:%M:%S"))) %>%
  dplyr::mutate(across(c(location_death_day7),
                       as.character)) 
```

```{r, eval=!is_tanzania}
day7fu_data <- day7fu_data %>%
  dplyr::mutate(across(c(call_ok),
                       factor))
```

```{r, results = 'asis'}
timci::dataset_export(day7fu_data,
                      "04b",
                      "timci_followup_successful_day7_data",
                      locked_db_dir,
                      "Cleaned successful Day 7 follow-up data")
```

```{r day7-lost-to-followup}
ltfu <- NULL
if (!is.null(day7fu_data)) {
  ltfu <- timci::generate_ltfu_log(df = day0_data,
                                   fudf = allday7fu_data,
                                   end_date = 12,
                                   raw = FALSE)
}
```

```{r locked-day7-lost-to-followup}
locked_ltfu <- NULL
if (!is.null(allday7fu_data)) {
  if (nrow(allday7fu_data)>0) {
    locked_ltfu <- timci::generate_ltfu_log(df = day0_data,
                                            fudf = allday7fu_data,
                                            end_date = 12,
                                            raw = FALSE)
  }
}
```

```{r}
if (!is.null(ltfu)) {
  fn <- timci::export_df2xlsx(ltfu,
                              rctls_dir,
                              "04c_day7_lost_to_followup")
}
```

```{r}
if (!is.null(locked_ltfu)) {
  fn <- timci::export_df2xlsx(locked_ltfu,
                              locked_db_dir,
                              "04c_day7_lost_to_followup")
}
```

```{r}
# if (!is.null(pii) & !is.null(raw_day7fu_data)) {
#   fu7all <- timci::generate_fu_log(pii,
#                                    raw_day7fu_data,
#                                    0,
#                                    12,
#                                    7,
#                                    10,
#                                    ext = TRUE,
#                                    deidentify = TRUE)
#   fn <- timci::export_df2xlsx(fu7all,
#                               params$rctls_dir,
#                               "04d_timci_deidentified_day7_fu_weekly_log_all")
# }
```

### Data summary statistics\n\n

```{r, results='asis'}
skimr::skim(day7fu_data)
```
