```{r}
write("Export repeat visit data and run corresponding quality checks", stderr())
```

## Repeat visit quality checks

```{r}
db_name <- "Repeat visit"
repeat_data <- facility_data %>%
  dplyr::filter(repeat_consult == 1)
n_raw_repeat_records <- nrow(repeat_data)
repeat_is_not_null <- !is.null(repeat_data)
repeat_is_not_empty <- timci::is_not_empty(repeat_data)
```

Among the **`r n_cleaned_screening_records`** cleaned screening record(s), there are **`r nrow(repeat_data)`** record(s) corresponding to repeat visit(s) within the enrolment period.

### Format raw data

```{r}
repeat_pii_dictionary <- subset(dictionary, repeats_pii == 1)
repeat_dictionary <- subset(dictionary, repeats_exp == 1)
n_repeat_dictionary_vars <- nrow(repeat_dictionary)
```

There are **`r n_repeat_dictionary_vars`** variables exported from the raw `r db_name` database.

```{r, results='asis'}
repeat_dictionary %>%
  dplyr::select(new,
                old) %>%
  knitr::kable(col.names = c("Database reference",
                             "ODK reference"))
```

```{r}
repeat_data <- repeat_data %>% 
  dplyr::select(dplyr::any_of(c(repeat_pii_dictionary$new,
                                "fid_from_device"))) %>%
  dplyr::mutate(child_name = gsub('[0-9]+', '', tolower(paste(fs_name_check, ls_name_check, sep = ' '))))
```

### Participant identification

#### Repeat visits corresponding to participants enrolled outside the lock date range [Context check `r qc_pids_out_lock_range_repeat`]

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(repeat_data), results='asis'}
qc_description <- paste0("Repeat visits are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard repeat visit records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- repeat_data
idcol1 <- "prev_id"
refdf <- rbind(facility_data_before_start,
               facility_data_after_lock) %>%
  dplyr::filter( !is.na(child_id) )
idcol2 <- "child_id"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_repeat
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the repeat visit corresponds to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_repeat_records <- n_detected
repeat_data <- cleaned_df
```

#### Non-valid participant IDs [Context check `r qc_nonvalid_repeat`]

```{r}
write(" o Non-valid participant IDs", stderr())
```

```{r, eval=!is.null(repeat_data), results='asis'}
qc_description <- "Repeat visits are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_type <- "nonvalid_ids"
df <- repeat_data %>%
  dplyr::filter(!is.na(prev_id))
idcol1 <- "prev_id"
refdf <- allday0_data
idcol2 <- "child_id"
qc_text <- "non-valid participant IDs"
qc_idx <- qc_nonvalid_repeat
qc_export_label <- "nonvalid_pids_repeat"
qc_export_description <- "the child ID does not correspond to any ID found in the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_nonvalid_pids_repeat_records <- n_detected
repeat_data_part <- cleaned_df
repeat_data <- rbind(repeat_data %>%
                       dplyr::filter(is.na(prev_id)),
                     repeat_data_part)
```

```{r}
write(" o Non-valid participant IDs with matched names", stderr())
```

```{r, eval=!is.null(qc_reuse_df), results='asis'}
qc_description <- "Repeat visits are relevant only if they can be reconciled with a participant enrolled at Day 0. Non-reconciled repeat visits are searched for matched names."
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_type <- "matched_names"
df <- qc_reuse_df
refdf <- allday0_data
col_date <- "date_visit"
col_name <- "child_name"
ldate_diff <- -30
udate_diff <- -1
qc_text <- "non-valid participant IDs and matched names"
qc_idx <- qc_nonvalid_repeat
qc_export_label <- "nonvalid_pids_repeat_with_matched_names"
qc_export_description <- "the child ID does not correspond to any ID found in the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Non-consistent participant names [Context check `r qc_nonconsistent_name_repeat`]

```{r}
write(" o Non-consistent participant names", stderr())
```

```{r, eval=is_tanzania}
raw_day0_with_names <- day0_data %>% 
  merge(raw_pii %>%
          dplyr::select(fs_name,
                        ms_name,
                        ls_name,
                        uuid),
        by = "uuid")
```

```{r, eval=!is_tanzania}
raw_day0_with_names <- day0_data %>%
  merge(raw_pii %>%
          dplyr::select(fs_name,
                        ls_name,
                        uuid),
        by = "uuid")
```

```{r, eval=!is.null(repeat_data), results='asis'}
qc_description <- "Repeat visits are relevant only if the name of the participant matches the name of the participant enrolled at Day 0. Some errors can be introduced when participant IDs have been duplicated or follow-ups have been entered manually."
qc_rule <- "Keep only IDs of children whose name matches the name in the initial Day 0 database."
qc_type <- "inconsistent_names"
df <- repeat_data
refdf <- raw_day0_with_names
qc_text <- "non-consistent participant names"
qc_idx <- qc_nonconsistent_name_repeat
qc_export_label <- "nonconsistent_names_repeat"
qc_export_description <- paste0("the child name found in the ", db_name, " is not consistent with the name of the child with the same ID found in the locked Day 0 database")
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Dates and times

#### Repeat visit anterior to enrolment [Context check]

```{r}
write(" o Check for date of repeat visit anterior to date of enrolment", stderr())
```

```{r, eval=!is.null(repeat_data), results='asis'}
df <- repeat_data %>% 
  merge(day0_data %>%
          dplyr::select(child_id,
                        date_visit) %>%
          dplyr::rename(date_day0 = date_visit),
        by.x = "prev_id",
        by.y = "child_id",
        all.x = TRUE)
```

```{r, eval=!is.null(repeat_data), results='asis'}
# qc_description <- "Repeat visit should have happened after enrolment on Day 0."
# qc_rule <- action_alert_no_modification
# qc_type <- "date_discrepancy"
# col_date1 <- "date_visit"
# col_date2 <- "date_day0"
# qc_text <- "a date of repeat visit before the enrolment date"
# qc_idx <- qc_death_before_enrolment_day7fu
# qc_export_label <- "repeat_visit_before_enrolment"
# qc_export_description <- "the reported date of repeat visit was before the enrolment date"
# cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
#                       envir = environment(),
#                       quiet = TRUE))
```

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
n_cleaned_repeat_records <- nrow(repeat_data)
```

```{r}
timci::create_repeat_qc_flowchart(n_raw_repeat_records,
                                  n_nonvalid_pids_repeat_records,
                                  n_cleaned_repeat_records)
```

### Data overview

```{r}
write(" o Data overview", stderr())
```

```{r, eval = FALSE}
repeat_data <- repeat_data %>% 
  dplyr::select(dplyr::any_of(c(repeat_dictionary$new,
                                "fid_from_device")))
```

```{r, results='asis', eval=timci::is_not_empty(repeat_data), results='asis'}
fig_df <- repeat_data %>%
  dplyr::mutate(week = lubridate::floor_date(as.Date(start),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Repeat data overview"
facility_col <- "fid_from_device"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- ""
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
repeat_data <- repeat_data %>%
  dplyr::mutate(across(c(device_id,
                         sys_submit_id,
                         form_version,
                         fid_from_device,
                         who_age_ctg,
                         dob_knwn,
                         age_mo_knwn,
                         consult_reason,
                         main_cg,
                         main_cg_lbl,
                         repeat_consult),
                       factor)) %>%
  dplyr::mutate(across(c(age_yr,
                         age_mo),
                       as.integer)) %>% 
  dplyr::mutate(across(c(date_visit),
                       ~format(as.POSIXct(.),"%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start,
                         end,
                         submission_date),
                       as.POSIXct))
```

```{r, results='asis'}
skimr::skim(repeat_data)
```

### Data export

```{r}
write(" o Data export", stderr())
```

```{r, eval = FALSE}
raw_repeat_data <- raw_repeat_data %>% 
  dplyr::select(dplyr::any_of(c(repeat_dictionary$new,
                                "fid_from_device")))
```

```{r, eval=!deidentification_on, results = 'asis'}
timci::dataset_export(raw_repeat_data,
                      "02b",
                      "timci_repeat_data",
                      rctls_dir,
                      "Raw Repeat visit data")
```

```{r, results = 'asis'}
timci::dataset_export(repeat_data,
                      "02b",
                      "timci_repeat_data",
                      locked_db_dir,
                      "Cleaned Repeat visit data")
```
