\newpage

```{r}
write("Export hospital/hospitalisation data and run corresponding quality checks", stderr())
```

## Hospitalisation data quality checks

```{r}
db_name <- "hospitalisation follow-up"
```

<!-- Hospitalisation quality check IDs -->

```{r}
qc_root <- "DQC_HS"
qc_pids_out_lock_range_hospitfu <- paste(qc_root, "01", sep = "_")
qc_nonvalid_hospitfu <- paste(qc_root, "02", sep = "_")
qc_nonconsistent_name_hospitfu <- paste(qc_root, "03", sep = "_")
qc_duplicated_hospitfu <- paste(qc_root, "04", sep = "_")
qc_hospit_before_enrolment <- paste(qc_root, "05", sep = "_")
qc_death_before_enrolment <- paste(qc_root, "06", sep = "_")
qc_discharge_before_enrolment <- paste(qc_root, "07", sep = "_")
```

```{r}
hospit_data_uids <- NULL
locked_hospit_data <- NULL
hospit_fu <- NULL
hospitfu_pii_drops_is_not_empty <- NULL
```

```{r}
n_inconsistent_names_day7fu_records <- 0
n_death_prior_day0_hospitfu <- 0
n_hospit_prior_day0_hospitfu <- 0
n_discharge_prior_day0_hospitfu <- 0
```

### Format raw data

```{r format-RCT-LS-ODK-fu-hospit-data}
hospit_data <- timci::format_hospital_data(raw_hospit_data,
                                           is_deidentified = FALSE)
raw_hospit_data <- hospit_data
```

There are **`r if ( !is.null(raw_hospit_data) ) { nrow(raw_hospit_data) } else { 'NA' }`** record(s) in the raw `r db_name` database.

```{r}
hospitfu_dictionary <- timci::import_country_specific_xls_dict("hospit_dict.xlsx", Sys.getenv('TIMCI_COUNTRY'))
n_hospitfu_dictionary_vars <- nrow(hospitfu_dictionary)
```

There are **`r n_hospitfu_dictionary_vars`** variables exported from the raw `r db_name` database.

```{r, results='asis'}
hospitfu_dictionary %>%
  dplyr::select(new,
                old) %>%
  knitr::kable(col.names = c("Database reference",
                             "ODK reference"))
```

### Participant identification

#### Follow-ups corresponding to participants enrolled outside the lock date range [context check `r qc_pids_out_lock_range_hospitfu`]

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- paste0("Hospitalisation follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- hospit_data
idcol1 <- "child_id"
refdf <- facility_data_after_lock %>%
  dplyr::filter( !is.na(child_id) )
idcol2 <- "child_id"
col_date <- "date"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_hospitfu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up correspond to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_hospitfu_records <- n_detected
hospit_data <- cleaned_df
```

#### Non-valid participant IDs [compliance check `r qc_nonvalid_hospitfu`]

```{r}
write(" o Non-valid participant IDs", stderr())
```

`r paste0('[Initial check ', qc_nonvalid_hospitfu, 'a]{custom-style="underlined"}')`

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- "Hospitalisation follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of participant who are found in the locked Day 0 database."
qc_type <- "nonvalid_ids"
df <- hospit_data
idcol1 <- "child_id"
refdf <- allday0_data
idcol2 <- "child_id"
datecol <- "date_enrol"
ldate_diff <- -2
udate_diff <- 2
matched_names <- TRUE
cleaning <- "drop_all"
qc_text <- "non-valid participant IDs"
qc_idx <- paste0(qc_nonvalid_hospitfu, "a")
qc_export_label <- "nonvalid_pids_hospitfu_and_matched_names"
qc_export_description <- "the child ID does not correspond to any ID found the locked Day 0 database"

cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_pids_hospitfu <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
hospit_data <- cleaned_df
```

#### Non-consistent participant names [Context check `r qc_nonconsistent_name_hospitfu`]

```{r}
write(" o Non-consistent participant names", stderr())
```

`r paste0('[Initial check ', qc_nonconsistent_name_hospitfu, 'a]{custom-style="underlined"}')`

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- "Hospital follow-ups are relevant only if the name of the participant matches the name of the participant enrolled at Day 0. Some errors can be introduced when participant IDs have been duplicated or follow-ups have been entered manually."
qc_rule <- "Keep only IDs of children whose name matches the name in the initial Day 0 database."
qc_type <- "inconsistent_names"
df <- hospit_data
refdf <- allday0_data
datecol <- "date_enrol"
ldate_diff <- -2
udate_diff <- 2
matched_names <- TRUE
cleaning <- "drop_all"
qc_text <- "non-consistent participant names"
qc_idx <- paste0(qc_nonconsistent_name_hospitfu, "a")
qc_export_label <- "nonconsistent_names_hospitfu_with_matched_names"
qc_export_description <- paste0("the child name found in the ", db_name, " is not consistent with the name of the child with the same ID found in the locked Day 0 database")

cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_inconsistent_names_day7fu_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
hospit_data <- cleaned_df
```

```{r}
found_hospit_data <- hospit_data %>% 
  dplyr::filter(found == 1)
found_hospit_data_is_not_empty <- timci::is_not_empty(found_hospit_data)
```

#### Duplicate management [compliance check `r qc_duplicated_hospitfu`]

```{r}
write(" o Duplicate management", stderr())
```

```{r, eval=!found_hospit_data_is_not_empty, results='asis'}
cat("The dataset is empty. No check performed")
```

```{r, eval=found_hospit_data_is_not_empty, results='asis'}
qc_description <- "It is possible to have more than one successful follow-up records (**found** = 1) available for the same participant."
qc_rule <- action_alert_no_modification
qc_type <- "duplicates"
df <- found_hospit_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicated_hospitfu
qc_export_label <- "duplicated_hospitfu"
qc_export_description <- "successful hospitalisation follow-ups are duplicated"

cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_duplicates_hospitfu <- n_detected
```

### Dates and times

#### Invalid date of hospitalisation [Context check `r qc_hospit_before_enrolment`]

```{r}
write(" o Invalid date of hospitalisation", stderr())
```

```{r, eval=!found_hospit_data_is_not_empty, results='asis'}
cat("The dataset is empty. No check performed")
```

```{r, eval=found_hospit_data_is_not_empty, results='asis'}
qc_description <- "The reported hospital visit should have happened between enrolment at Day 0 and the hospitalisation follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- found_hospit_data %>% 
  merge(allday0_data %>%
          dplyr::select(child_id,
                        fid,
                        date_visit),
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_visit_rhf"
col_date2 <- "date_visit"
qc_text <- "a date of hospitalisation before the enrolment date"
qc_idx <- qc_hospit_before_enrolment
qc_export_label <- "hospit_before_enrolment"
qc_export_description <- "the reported date of hospitalisation was before the enrolment date"

cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_hospit_prior_day0_hospitfu <- n_detected
```

#### Invalid date of death [Context check `r qc_death_before_enrolment`]

```{r}
write(" o Invalid date of death", stderr())
```

```{r, eval=!found_hospit_data_is_not_empty, results='asis'}
cat("The dataset is empty. No check performed")
```

```{r, eval=found_hospit_data_is_not_empty, results='asis'}
qc_description <- "The reported death should have happened between enrolment at Day 0 and the hospitalisation follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- found_hospit_data %>% 
  merge(allday0_data %>%
          dplyr::select(child_id,
                        fid,
                        date_visit),
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_death"
col_date2 <- "date_visit"
qc_text <- "a date of death before the enrolment date"
qc_idx <- qc_death_before_enrolment
qc_export_label <- "death_before_enrolment"
qc_export_description <- "the reported date of death was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_death_prior_day0_hospitfu <- n_detected
```

#### Invalid date of discharge [Context check `r qc_discharge_before_enrolment`]

```{r}
write(" o Invalid date of discharge", stderr())
```

```{r, eval=!found_hospit_data_is_not_empty, results='asis'}
cat("The dataset is empty. No check performed")
```

```{r, eval=found_hospit_data_is_not_empty, results='asis'}
qc_description <- "The reported hospital visit should have happened between enrolment at Day 0 and the hospitalisation follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- found_hospit_data %>% 
  merge(allday0_data %>%
          dplyr::select(child_id,
                        fid,
                        date_visit),
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_discharge"
col_date2 <- "date_visit"
qc_text <- "a date of discharge before the enrolment date"
qc_idx <- qc_discharge_before_enrolment
qc_export_label <- "discharge_before_enrolment"
qc_export_description <- "the reported date of discharge was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_discharge_prior_day0_hospitfu <- n_detected
```

### Pseudonymisation

```{r}
write(" o Pseudonymisation", stderr())
```

```{r}
hospitfu_pii_drops <- hospitfu_dictionary %>%
  dplyr::filter(deidentified == 0)
```

There are **`r nrow(hospitfu_pii_drops)`** variables deleted from the anonymised cleaned `r db_name` database.

```{r, results='asis'}
hospitfu_pii_drops %>%
  dplyr::select(new) %>%
  knitr::kable(row.names = FALSE,
               caption = "Columns with PII dropped for cleaned data export")
```

```{r}
hospitfu_deidentified_dict <- hospitfu_dictionary %>%
  dplyr::filter(deidentified == 1)
```

There are **`r nrow(hospitfu_deidentified_dict)`** variables exported from the cleaned anonymised `r db_name` database.

```{r}
hospit_data_no_pii <- hospit_data %>%
  dplyr::select(dplyr::any_of(c(hospitfu_deidentified_dict$new)))
```

Pseudonymisation is performed using a cryptographic hash function (md5) that takes strings as input and produces a random-like fixed-length output.

```{r}
hospit_data_no_pii <- hospit_data_no_pii %>%
  dplyr::rowwise() %>%
  dplyr::mutate(uuid = ifelse(uuid != "", digest(uuid, algo = crypto_algo), ""),
                child_id = ifelse(child_id != "", digest(child_id, algo = crypto_algo), ""),
                device_id = ifelse(device_id != "", digest(device_id, algo = crypto_algo), "")) %>%
  dplyr::ungroup()
```

### Data cleaning summary

```{r}
timci::create_hospit_qc_flowchart(nrow(raw_hospit_data),
                                  n_afterlock_pids_hospitfu_records,
                                  n_nonvalid_pids_hospitfu,
                                  n_inconsistent_names_day7fu_records,
                                  n_duplicates_hospitfu,
                                  n_death_prior_day0_hospitfu,
                                  n_hospit_prior_day0_hospitfu,
                                  n_discharge_prior_day0_hospitfu,
                                  nrow(hospit_data))
```

### Data overview

```{r}
hospit_data_no_pii <- hospit_data_no_pii %>%
  dplyr::mutate(across(c(device_id,
                         form_version,
                         rhf_id,
                         rhf_name,
                         sex_hf,
                         dob_knwn_hf,
                         found,
                         time_visit_hf,
                         rr,
                         spo2,
                         hospit,
                         ward,
                         o2,
                         o2_type,
                         dx_admission,
                         adm_outcome,
                         dx_discharge,
                         o2_duration,
                         death_cause,
                         facility_trans),
                       factor)) %>%
  dplyr::mutate(across(c(spo2_meas,
                         rr_meas),
                       as.numeric)) %>% 
  dplyr::mutate(across(c(date,
                         date_visit_rhf,
                         date_discharge,
                         date_death),
                       ~format(as.Date(.), "%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start),
                       ~format(as.Date(.), "%Y-%m-%d %H:%M:%S"))) %>%
  dplyr::mutate(across(c(dx_admission_oth,
                         dx_discharge_oth,
                         facility_trans_oth,
                         ward_oth),
                       as.character)) 
```

```{r, results='asis'}
skimr::skim(hospit_data_no_pii)
```

### Data export

```{r, results = 'asis'}
timci::dataset_export(raw_hospit_data,
                      "05a",
                      "timci_followup_hospit_data",
                      rctls_dir,
                      "Raw hospitalisation data")
```

```{r, results = 'asis'}
timci::dataset_export(hospit_data_no_pii,
                      "05a",
                      "timci_followup_hospit_data",
                      locked_db_dir,
                      "Cleaned de-identified hospitalisation data")
```
