## Hospitalisation data quality checks\n\n

```{r}
write("Export hospital/hospitalisation data and run corresponding quality checks", stderr())
```

```{r format-RCT-LS-ODK-fu-hospit-data}
hospit_data <- timci::format_hospital_data(raw_hospit_data)
db_name <- "hospitalisation follow-up"
```

There are **`r if ( !is.null(hospit_data) ) { nrow(hospit_data) } else { 'NA' }`** record(s) in the raw `r db_name` database.

```{r}
hospit_data_uids <- NULL
locked_hospit_data <- NULL
hospit_fu <- NULL
```

### Participant identification

#### Follow-ups corresponding to participants enrolled outside the lock date range [context check `r qc_pids_out_lock_range_hospitfu`]

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- paste0("Hospitalisation follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- hospit_data
idcol1 <- "child_id"
refdf <- facility_data_after_lock %>%
  dplyr::filter( !is.na(child_id) )
idcol2 <- "child_id"
col_date <- "date"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_hospitfu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up correspond to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_hospitfu_records <- n_detected
hospit_data <- cleaned_df
```

#### Non-valid participant IDs [compliance check `r qc_nonvalid_hospitfu`]

```{r, eval=!is.null(hospit_data), results='asis'}
qc_description <- "Hospitalisation follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of participant who are found in the locked Day 0 database."
qc_type <- "nonvalid_ids"
df <- hospit_data
idcol1 <- "child_id"
refdf <- day0_data
idcol2 <- "child_id"
qc_text <- "non-valid participant IDs"
qc_idx <- qc_nonvalid_hospitfu
qc_export_label <- "nonvalid_pids_hospitfu"
qc_export_description <- "the child ID does not correspond to any ID found the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_pids_hospitfu <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
locked_hospit_data <- cleaned_df
```

#### Duplicate management [compliance check `r qc_duplicated_hospitfu`]

```{r}
write(" o Duplicate management", stderr())
```

```{r, eval=!is.null(locked_hospit_data), results='asis'}
qc_description <- "It is possible to have more than one successful follow-up records available for the same participant."
qc_rule <- action_alert_no_modification
qc_type <- "duplicates"
df <- locked_hospit_data %>% 
  dplyr::filter(found == 1)
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicated_hospitfu
qc_export_label <- "duplicated_hospitfu"
qc_export_description <- "hospitalisation follow-ups are duplicated"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_duplicates_hospitfu <- n_detected
```

### Dates and times

#### Invalid date of hospitalisation [Context check `r qc_hospit_before_enrolment`]

```{r}
write(" o Invalid date of hospitalisation", stderr())
```

```{r, eval=!is.null(locked_hospit_data), results='asis'}
qc_description <- "The reported hospital visit should have happened between enrolment at Day 0 and the hospitalisation follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- locked_hospit_data %>%
  dplyr::filter(found == 1) %>% 
  merge(day0_data %>%
          dplyr::select(child_id,
                        fid,
                        date_visit),
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_visit_rhf"
col_date2 <- "date_visit"
qc_text <- "a date of hospitalisation before the enrolment date"
qc_idx <- qc_hospit_before_enrolment
qc_export_label <- "hospit_before_enrolment"
qc_export_description <- "the reported date of hospitalisation was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Invalid date of death [Context check `r qc_hospit_before_enrolment`]

```{r}
write(" o Invalid date of death", stderr())
```

```{r, eval=!is.null(locked_hospit_data), results='asis'}
qc_description <- "The reported death should have happened between enrolment at Day 0 and the hospitalisation follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- locked_hospit_data %>%
  dplyr::filter(found == 1) %>% 
  merge(day0_data %>%
          dplyr::select(child_id,
                        fid,
                        date_visit),
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_death"
col_date2 <- "date_visit"
qc_text <- "a date of hospitalisation before the enrolment date"
qc_idx <- qc_hospit_before_enrolment
qc_export_label <- "death_before_enrolment"
qc_export_description <- "the reported date of death was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Invalid date of discharge [Context check `r qc_hospit_before_enrolment`]

```{r}
write(" o Invalid date of discharge", stderr())
```

```{r, eval=!is.null(locked_hospit_data), results='asis'}
qc_description <- "The reported hospital visit should have happened between enrolment at Day 0 and the hospitalisation follow-up."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- locked_hospit_data %>%
  dplyr::filter(found == 1) %>% 
  merge(day0_data %>%
          dplyr::select(child_id,
                        fid,
                        date_visit),
        by = "child_id",
        all.x = TRUE)
col_date1 <- "date_discharge"
col_date2 <- "date_visit"
qc_text <- "a date of hospitalisation before the enrolment date"
qc_idx <- qc_hospit_before_enrolment
qc_export_label <- "discharge_before_enrolment"
qc_export_description <- "the reported date of discharge was before the enrolment date"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Data cleaning summary

```{r}
timci::create_hospit_qc_flowchart(nrow(hospit_data),
                                  n_afterlock_pids_hospitfu_records,
                                  n_nonvalid_pids_hospitfu,
                                  n_duplicates_hospitfu,
                                  nrow(locked_hospit_data))
```

### Data export

```{r export-RCT-LS-ODK-fu-hospit-data, results = 'asis'}
timci::dataset_export(hospit_data,
                      "05a",
                      "timci_followup_hospit_data",
                      rctls_dir,
                      "Raw hospitalisation data")
```

```{r}
locked_hospit_data <- locked_hospit_data %>%
  dplyr::mutate(across(c(device_id,
                         sys_submit_id,
                         form_version,
                         rhf_id,
                         rhf_name,
                         sex,
                         sex_hf,
                         dob_knwn_hf,
                         found,
                         time_visit_hf,
                         rr,
                         spo2,
                         hospit,
                         ward,
                         o2,
                         o2_type,
                         dx_admission,
                         adm_outcome,
                         dx_discharge,
                         o2_duration,
                         death_cause,
                         facility_trans),
                       factor)) %>%
  dplyr::mutate(across(c(spo2_meas,
                         rr_meas),
                       as.numeric)) %>% 
  dplyr::mutate(across(c(date,
                         date_visit_rhf,
                         date_discharge,
                         date_death),
                       ~format(as.Date(.), "%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start,
                         end),
                       ~format(as.Date(.), "%Y-%m-%d %H:%M:%S"))) %>%
  dplyr::mutate(across(c(dx_admission_oth,
                         dx_discharge_oth,
                         facility_trans_oth,
                         ward_oth),
                       as.character)) 
```

```{r, results = 'asis'}
timci::dataset_export(locked_hospit_data,
                      "05a",
                      "timci_followup_hospit_data",
                      locked_db_dir,
                      "Cleaned hospitalisation data")
```

```{r, eval=!is.null(raw_pii)}
hospit_fu <- timci::generate_hospital_log(pii = raw_pii,
                                          fu7df = raw_day7fu_data,
                                          day0df = day0_data,
                                          hospitdf = raw_hospit_data,
                                          deidentify = TRUE,
                                          is_pilot = is_pilot)
```

```{r, results = 'asis'}
timci::dataset_export(hospit_fu,
                      "05c",
                      "timci_deidentified_hospit_fu_log_all",
                      rctls_dir,
                      "Hospitalisation log data")
```

### Data summary statistics

```{r, results='asis'}
skimr::skim(locked_hospit_data)
```
