## Day 0 data quality checks\n\n

```{r}
write("Export Day 0 data and run corresponding quality checks", stderr())
```

```{r}
db_name <- "Day 0"
day0_data <- facility_data %>%
    dplyr::filter(enrolled == 1)
n_raw_day0_records <- nrow(day0_data)
repeat_data <- facility_data %>%
    dplyr::filter(repeat_consult == 1)
day0_is_not_null <- !is.null(day0_data)
day0_is_not_empty <- timci::is_not_empty(day0_data)
```

Among the **`r n_cleaned_screening_records`** cleaned screening record(s), there are **`r n_raw_day0_records`** record(s) corresponding to new Day 0 enrolment(s) and **`r nrow(repeat_data)`** record(s) corresponding to repeat visit(s) within the enrolment period.

### Non-valid enrolling facility IDs [compliance `r if ( is_kenya | is_tanzania ) { 'checks' } else { paste0("check ", qc_nonvalid_fid2) }`]\n\n

```{r}
write(" o Non-valid enrolling facility IDs", stderr())
```

`r if ( is_kenya | is_tanzania ) { paste0('#### Initial check [compliance check', qc_nonvalid_fid1, ']\n\n') }`

```{r, eval=(day0_is_not_null & (is_kenya | is_tanzania)), results='asis'}
qc_description <- "The facility ID (Fxxxx) is extracted from the participant enrolment ID (X-Fxxxx-Pxxxx). It should correspond to the ID of one of the research facility listed in Section 2.2 of this report."
qc_rule <- "Records corresponding to facility IDs not listed in Section 2.2 of this report are detected and manually corrected before Day 7 follow-up is conducted where possible."
qc_type <- "nonvalid_ids_no_cleaning"
df <- day0_data
idcol1 <- "fid"
refdf <- research_facilities
idcol2 <- "facility_id"
qc_text <- "facility ID not valid"
qc_idx <- qc_nonvalid_fid1
qc_export_label <- "nonvalid_fids"
qc_export_description <- "the facility ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if ( is_kenya | is_tanzania ) {'#### Facility ID manual edits\n\n'}`

```{r}
edited_records <- NULL
edited_df_status_update <- ""
```

```{r, eval=is_kenya | is_tanzania}
out <- timci::correct_day0_non_valid_facilities(day0_data)
day0_data <- out[[1]]
edited_records <- out[[2]]
```

```{r, eval=(is_kenya | is_tanzania)&!is.null(edited_records)}
edited_df_status_update <- paste0('**', nrow(edited_records), '** record(s) were manually edited in the ', db_name, ' database.')
```

`r edited_df_status_update`

```{r, eval=(is_kenya | is_tanzania)&!is.null(edited_records), results='asis'}
edited_records %>%
  dplyr::select(old_child_id, uuid, new_child_id) %>%
  knitr::kable()
```

`r if (is_kenya | is_tanzania) { paste0('#### Final check after manual edits [compliance check', qc_nonvalid_fid2, ']\n\n') }`

```{r, eval=day0_is_not_null, results='asis'}
qc_description <- "The facility ID (Fxxxx) is extracted from the participant enrolment ID (X-Fxxxx-Pxxxx). It should correspond to the ID of one of the research facility listed in Section 2.2 of this report."
qc_rule <- "Records corresponding to facility IDs not listed in Section 2.2 of this report are deleted."
qc_type <- "nonvalid_ids"
df <- day0_data
idcol1 <- "fid"
refdf <- research_facilities
idcol2 <- "facility_id"
qc_text <- "facility ID not valid"
qc_idx <- qc_nonvalid_fid2
qc_export_label <- "nonvalid_fids"
qc_export_description <- "the facility ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_fid_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
day0_data <- cleaned_df
```

`r if (is_india) {'### Inconsistent facility information [Context check]\n\n'}`

`r if (is_india) {'**Rule**: records with inconsistent facility information are kept in the locked database, but will need to be checked more carefully (e.g: GPS data).\n\n'}`

```{r}
qc_inconsistent_facility <- NULL
if (Sys.getenv('TIMCI_COUNTRY') == 'India') {
  if (day0_is_not_null) {
    if (nrow(day0_data) > 0) {
      qc_inconsistent_facility <- day0_data[day0_data$fid != day0_data$fid_ra, ]
      qc_inconsistent_facility <- qc_inconsistent_facility[c("child_id", "fid", "fid_ra", "uuid")]
    }
  }
}
```

```{r, results='asis'}
if (!is.null(qc_inconsistent_facility)) {
  if (nrow(qc_inconsistent_facility) > 0) {
    cat(paste0("**", nrow(qc_inconsistent_facility), "** record(s) with inconsistent facility information detected."))
  }
}
```

```{r, results='asis'}
if (!is.null(qc_inconsistent_facility)) {
  if (nrow(qc_inconsistent_facility) > 0) {
    qc_inconsistent_facility %>%
      knitr::kable(row.names = FALSE)
  }
}
```

### Duplicate management\n\n

`r if ( (is_tanzania | is_kenya | is_senegal) & !is_pilot ) { paste0('#### Initial check [compliance check ', qc_duplicate_id1, ']\n\n') }`

```{r, eval=day0_is_not_null&(is_tanzania|is_kenya), results='asis'}
qc_description <- "All participants should have a distinct ID. Duplicated IDs may generate errors for the conduct of follow-ups in the field and results in ambiguous outcomes for duplicated participants once the database is deidentified."
qc_rule <- "Duplicated child IDs are detected and corrected proactively were possible."
qc_type <- "duplicates"
df <- day0_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicate_id1
qc_export_label <- "timci_day0_data_id_duplicates"
qc_export_description <- "the submission was allocated the same ID that has been used for another participant in the databse"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if ( is_tanzania & !is_pilot ) { '#### Manual deletion of test/dummy data recorded as duplicated IDs\n\n' }`

```{r}
deleted_records_status_update <- ""
out <- timci::delete_day0_records(day0_data)
day0_data <- out[[1]]
dropped_records <- out[[2]]
dropped_records_is_not_empty <- timci::is_not_empty(dropped_records)
```

```{r, eval=dropped_records_is_not_empty}
deleted_records_status_update <- paste0('After the manual deletion of the **', nrow(dropped_records), '** record(s) listed below, there are **', nrow(day0_data), '** record(s) in the ', db_name, ' database.')
```

`r deleted_records_status_update`

```{r, eval=dropped_records_is_not_empty, results='asis'}
dropped_records %>%
  select(old_child_id, uuid) %>%
  knitr::kable()
```

`r if ( (is_tanzania | is_kenya | is_senegal) & !is_pilot ) { '#### Manual correction of duplicated IDs\n\n' }`

```{r}
edited_records_status_update <- ""
out <- timci::edit_day0_child_ids(day0_data)
day0_data <- out[[1]]
duplicate_edits <- out[[2]]
duplicate_edits_is_not_empty <- timci::is_not_empty(duplicate_edits)
```

```{r, eval=duplicate_edits_is_not_empty}
edited_records_status_update <- paste0('**', nrow(duplicate_edits), '** record(s) manually corrected in the ', db_name, ' database.')
```

`r edited_records_status_update`

```{r, eval=duplicate_edits_is_not_empty, results='asis'}
duplicate_edits %>%
  select(old_child_id, uuid, new_child_id) %>%
  knitr::kable()
```

`r if ( (is_tanzania | is_kenya | is_senegal) & !is_pilot ) { paste0('#### Final check after manual edits [compliance check ', qc_duplicate_id2, ']\n\n') }`

```{r, eval=(day0_is_not_null & !is_pilot), results='asis'}
qc_description <- "All participants should have a distinct ID. Duplicated IDs may generate errors for the conduct of follow-ups in the field and results in ambiguous outcomes for duplicated participants once the database is deidentified."
qc_rule <- "Remaining duplicated child IDs are deleted from the database."
qc_type <- "duplicates"
df <- day0_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "drop_all"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicate_id2
qc_export_label <- "timci_day0_data_id_duplicates"
qc_export_description <- "the submission was allocated the same ID that has been used for another participant in the database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
day0_data <- cleaned_df
```

### Incorrect enrolment date [context check `r qc_incorrect_enrolment_date`]\n\n

```{r}
write(" o Incorrect enrolment date", stderr())
```

```{r}
qc_df <- NULL
n_incorrect_enroldate_records <- 0
cleaned_df <- NULL
```

```{r, eval=day0_is_not_null&is_tanzania, results='asis'}
qc_description <- "The enrolment date is defined as the creation (start) date of the form. However if research assistants reuse a form that already exist on their device to enrol a new participant, it is possible that the date on which the name of the participant is entered in the form is not on the same day it was started. As a consequence the enrolment date may be shifted and follow-up may not be triggered at the right time."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day0_data
col_date1 <- "start"
col_date2 <- "start_contact"
cleaning <- "replace_by_end_date"
qc_text <- "an incorrect date of enrolment"
qc_idx <- qc_incorrect_enrolment_date
qc_export_label <- "incorrect_enrolment_date"
qc_export_description <- "the enrolment date is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_incorrect_enroldate_records <- n_detected
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Number of days between submission start and entry of participant contact details" ,
     ylab="Occurences",
     main="")
```

### Non-timely completion [compliance check `r qc_nontimely_completion_id`]\n\n

```{r}
write(" o Non-timely completion", stderr())
```

```{r, eval=day0_is_not_null, results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day0_data
col_date1 <- "start"
col_date2 <- "end"
qc_text <- "the submission was not finalised on the same day it was started"
qc_idx <- qc_nontimely_completion_id
qc_export_label <- "nontimely_day0_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Number of days between submission start and finalisation" ,
     ylab="Occurences",
     main="")
```

### Non-timely submission [compliance check `r qc_nontimely_submission_id`]\n\n

```{r}
write(" o Non-timely submission", stderr())
```

```{r, eval=day0_is_not_null, results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day). A delay superior to 12 days mean that the participant has never appeared in the Day 7 follow-up log on the tablet."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- day0_data
col_date1 <- "end"
col_date2 <- "submission_date"
qc_text <- "the submission was not transferred on the same day it was finalised"
qc_idx <- qc_nontimely_submission_id
qc_export_label <- "nontimely_day0_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df)}
hist(as.numeric(qc_df$diff),
     breaks = c(1:max(as.numeric(qc_df$diff), na.rm = TRUE)),
     xlab="Number of days between submission finalisation and transfer" ,
     ylab="Occurences",
     main="")
```

### Detection of multiple 28-disease episodes for the same children\n\n

```{r}
write(" o Detection of multiple 28-disease episodes for the same children", stderr())
```

```{r}
multiple <- FALSE
```

`r if( !multiple) {'Only implemented for the final analysis - checks disabled for the interim analysis'}`

```{r child_duplicate-subsection, child = if ( multiple ) 'database_export_sub_QC_child_multiple_enrolments.Rmd'}
```

### Missing clinical presentation [Mandatory check `r qc_missing_cp_id`]\n\n

```{r}
write(" o Missing clinical presentation", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
qc_description <- "All participants should have complete information about their clinical presentation, i.e. a participant cannot have simultaneously:

* No convulsions (*sx_convulsions* $\\neq$ 1)
* No lethargy (*sx_lethargy* $\\neq$ 1)
* No vomiting (*sx_vomit* = 0 or *sx_vomit* = 98)
* No feeding less than usual (*sx_less_feed* = 0 or *sx_less_feed* = 98)
* No cough (*sx_cough* = 0 or *sx_cough* = 98)
* No difficulty breathing (*sx_difficulty_breath* = 0 or *sx_difficulty_breath* = 98)
* No diarrhoea (*sx_diarrhoea* = 0 or *sx_diarrhoea* = 98)
* No fever (*sx_fever* = 0 or *sx_fever* = 98)
* No other complaint (*sx_var* = 96)"
qc_rule <- action_alert_no_modification
qc_type <- "missing_clinical_presentation"
df <- day0_data
qc_text <- "missing clinical presentation"
qc_idx <- qc_missing_cp_id
qc_export_label <- "missing_clinical_presentation"
qc_export_description <- "the clinical presentation is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_cp <- n_detected
```

### Missing diagnosis [Mandatory check `r qc_missing_diagnosis_id`]\n\n

```{r}
write(" o Missing diagnosis", stderr())
```

```{r, results='asis', eval=day0_is_not_null&!is_india}
qc_description <- "All participants should have complete information about their diagnosis for their Day 0 visit, i.e. a participant cannot have simultaneously:

* No danger signs (*dx_severe* = 0)
* No pneumonia (*dx_pneumonia* = 0)
* No diarrhoea (*dx_diarrhoea* = 0)
* No dehydration (*dx_dehydration* = 0)
* No malaria (*dx_malaria* = 0)
* No ear infection (*dx_ear_infection* = 0)
* No malnutrition (*dx_malnutrition* = 0)
* No anaemia (*dx_anaemia == 0*)
* No other diagnoses (*sx_var* = 96 and *dx_oth_yn* = 1)"
qc_rule <- action_alert_no_modification
qc_type <- "missing_diagnosis"
df <- day0_data
qc_text <- "missing diagnosis"
qc_idx <- qc_missing_diagnosis_id
qc_export_label <- "missing_diagnosis"
qc_export_description <- "the diagnosis is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_diagnosis <- n_detected
```

### Missing referral [Mandatory check `r qc_missing_referral_id`]\n\n

```{r}
write(" o Missing referral", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
qc_description <- "All participants should have complete information about the management at the facility for their Day 0 visit. This information is collected from 2 soures: the caregiver at the exit of the consultation and the facility registries/consultation notes. However, caregivers may be lost at the exit of the consultation, so that the referral information from this source would be missing (*referral_cg* = 'NA')."
qc_rule <- action_alert_no_modification
qc_type <- "missing_referral"
df <- day0_data
qc_text <- "missing referral information (source: caregiver at the exit of the consultation)"
qc_idx <- qc_missing_referral_id
qc_export_label <- "missing_referral_cg"
qc_export_description <- "the referral information that should have been obtained from the caregiver at the exit of the consultation is missing"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_missing_referral_cg <- n_detected
```

### Clinical measurements\n\n

```{r}
write(" o Clinical measurements", stderr())
```

#### Temperature\n\n

```{r}
write("   o Temperature", stderr())
```

```{r, results='asis', eval=day0_is_not_null&!is_india}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = temp_meas)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 0.5) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666")
```

```{r, results='asis', eval=day0_is_not_null&!is_india}
dataMaid::identifyOutliers(day0_data$temp_meas,
                           nMax = 50)
```

```{r, results='asis', eval=day0_is_not_null&is_india}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = temp_meas_farenheit)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 0.2) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666")
```

```{r, results='asis', eval=day0_is_not_null&is_india}
dataMaid::identifyOutliers(day0_data$temp_meas_farenheit,
                           nMax = 50)
```

#### Pulse oximetry\n\n

```{r}
write("   o Pulse oximetry", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = spo2_meas1)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 1) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666")
```

```{r, results='asis', eval=day0_is_not_null}
dataMaid::identifyOutliers(day0_data$spo2_meas1,
                           nMax = 100)
```

#### Respiratory rate\n\n

```{r}
write("   o Respiratory rate", stderr())
```

```{r, results='asis', eval=day0_is_not_null}
day0_data %>%
  ggplot2::ggplot(ggplot2::aes(x = rr_meas)) +
  ggplot2::geom_histogram(ggplot2::aes(y=..density..),
                          colour="black",
                          fill="white",
                          binwidth = 5) + 
  ggplot2::geom_density(alpha = 0.2,
                        fill="#FF6666")
```

```{r, results='asis', eval=day0_is_not_null}
dataMaid::identifyOutliers(day0_data$rr_meas,
                           nMax = 150)
```

### Data cleaning summary\n\n

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
allday0_data <- day0_data
out <- timci::extract_pii(day0_data,
                          is_pilot)
day0_data <- out[[1]]
n_cleaned_day0_records <- nrow(day0_data)
```

```{r}
timci::create_day0_qc_flowchart(n_raw_day0_records,
                                n_nonvalid_fid_records,
                                n_incorrect_enroldate_records,
                                nrow(dropped_records),
                                nrow(duplicate_edits),
                                n_cleaned_day0_records)
```

### Data export\n\n

```{r}
write(" o Data export", stderr())
```

```{r, eval=!deidentification_on, results = 'asis'}
timci::dataset_export(raw_day0_data,
                      "02",
                      "timci_day0_data",
                      rctls_dir,
                      "Raw Day 0 data")
```

```{r, results = 'asis'}
timci::dataset_export(day0_data,
                      "02",
                      "timci_day0_data",
                      locked_db_dir,
                      "Cleaned Day 0 data")
```

```{r split-pii-from-research-data, eval=!is.null(facility_data)}
ts <- timci::export_df2xlsx(raw_pii,
                            tempdir(),
                            "timci_contact_data")
pii_pwd <- Sys.getenv("TIMCI_PII_PW")
zip(params$participant_zip, 
    files = file.path(tempdir(), "timci_contact_data.xlsx"), 
    flags = paste("-r9Xj --password", pii_pwd))
```

```{r export-visit-data, results = 'asis', eval=!is.null(facility_data)}
study_data <- timci::extract_all_visits(facility_data,
                                        is_pilot)
```

```{r, results = 'asis'}
timci::dataset_export(study_data,
                      "03",
                      "timci_facility_visits_data",
                      rctls_dir,
                      "Facility visit data")
```

### Data summary statistics\n\n

```{r}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(device_id,
                         sys_submit_id,
                         form_version,
                         fid,
                         who_age_ctg,
                         district,
                         facility,
                         dob_knwn,
                         age_mo_knwn,
                         enrolled,
                         mother_education),
                       factor)) %>%
  dplyr::mutate(across(c(date_visit), ~format(as.Date(.), "%Y-%m-%d"))) %>% 
  dplyr::mutate(across(c(start,
                         end), ~format(as.Date(.), "%Y-%m-%d %H:%M:%S")))
```

```{r, eval = (is_tanzania | is_kenya | is_senegal)}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(living_with_cg),
                       factor))
```

```{r, eval = (is_tanzania)}
day0_data <- day0_data %>%
  dplyr::mutate(across(c(district_ra,
                         location_lvl1,
                         location_lvl2,
                         location_lvl3,
                         location_lvl4),
                       factor))
```

```{r, results='asis'}
skimr::skim(day0_data)
```
