\newpage

```{r}
write("Export Day 7 follow-up data and run corresponding quality checks", stderr())
```

## Day 7 follow-up data quality checks

```{r}
db_name <- "Day 7 follow-up"
```

```{r}
n_nonvalid_pid_day7fu_records <- 0
n_edit_nonvalid_pid_day7fu_records <- 0
n_drop_nonvalid_pid_day7fu_records <- 0
n_inconsistent_name_day7fu_records <- 0
n_edit_inconsistent_name_day7fu_records <- 0
```


```{r}
day7fu_pii_drops <- c("name",
                      "cg_name",
                      "phone_nb")
```

```{r format-RCT-LS-ODK-fu-day7-data}
n_raw_allday7fu_data_records <- nrow(raw_allday7fu_data)
raw_allday7fu_is_not_empty <- timci::is_not_empty(raw_allday7fu_data)
```

There are **`r n_raw_allday7fu_data_records`** records in the raw `r db_name` database.

### Format raw data

```{r}
day7fu_dictionary <- timci::import_country_specific_xls_dict("day7_dict.xlsx", Sys.getenv('TIMCI_COUNTRY'))
n_day7fu_dictionary_vars <- nrow(day7fu_dictionary)
```

There are **`r n_day7fu_dictionary_vars`** variables exported from the raw `r db_name` database.

```{r, results='asis'}
day7fu_dictionary %>%
  dplyr::select(new,
                old,
                deidentified) %>%
  knitr::kable(col.names = c("Database reference",
                             "ODK reference",
                             "Deidentified export"))
```

### Dates and times

#### Late submissions [Compliance check `r qc_nontimely_submission_day7fu`]

```{r}
write(" o Inconsistent finalisation and submission", stderr())
```

```{r, eval=raw_allday7fu_is_not_empty, results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- raw_allday7fu_data
col_date1 <- "end"
col_date2 <- "submission_date"
cleaning <- "none"
qc_text <- "the submission was not transferred on the same day it was finalised"
qc_idx <- qc_nontimely_submission_day7fu
qc_export_label <- "nontimely_day7_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
fig_caption <- "Submissions not transferred on the same day they were finalised"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>% 
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(end), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = dplyr::case_when(
    diff < 3 ~ "Less than 3 days",
    diff >= 3 & diff < 7 ~ "3-6 days",
    diff >= 7 ~ "7 days and above"))

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

#### Late completions [Compliance check `r qc_nontimely_completion_day7fu`]

```{r}
write(" o Non-timely completion", stderr())
```

```{r, eval=raw_allday7fu_is_not_empty, results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- raw_allday7fu_data
col_date1 <- "start"
col_date2 <- "end"
cleaning <- "none"
qc_text <- "the submission was not finalised on the same day it was started"
qc_idx <- qc_nontimely_completion_day7fu
qc_export_label <- "nontimely_day7_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
fig_caption <- "Number of submissions not finalised on the same day they were started"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = dplyr::case_when(
    diff <= 1 ~ "1 day",
    diff > 1 & diff < 3 ~ "1-2 days",
    diff >= 3 ~ "3 days and above"))

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Participant identification

#### Follow-ups corresponding to participants enrolled in other TIMCI studies (India only) [Context check `r qc_other_fids_day7fu`]

```{r}
write(" o Follow-ups corresponding to participants enrolled in the CDSA pilot", stderr())
```

`r if (!is_india) {This check is only implemented for India.}`

```{r, eval=!is.null(raw_allday7fu_data)&is_india, results='asis'}
qc_description <- paste0("Exclude follow-ups that correspond to participants enrolled in the CDSA pilot.")
qc_rule <- "Discard follow-up records of participants who are enrolled in CDSA pilot facilities."
qc_text <- "follow-up records corresponding to records collected for another TIMCI study"
qc_idx <- qc_other_fids_day7fu
```

#### Follow-ups corresponding to participants enrolled outside the lock date range [Context check `r qc_pids_out_lock_range_day7fu`]

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(raw_allday7fu_data), results='asis'}
qc_description <- paste0("Day 7 follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- raw_allday7fu_data
idcol1 <- "child_id"
refdf <- rbind(facility_data_before_start,
               facility_data_after_lock) %>%
  dplyr::filter( !is.na(child_id) )
idcol2 <- "child_id"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_day7fu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up corresponds to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_day7fu_records <- n_detected
allday7fu_data <- cleaned_df
```

#### Non-valid participant IDs [Context check `r qc_nonvalid_day7fu`]

```{r}
write(" o Non-valid participant IDs", stderr())
```

::: {custom-style="redparagraph"}
Initial check `r qc_nonvalid_day7fu`a
:::

```{r, eval=!is.null(allday7fu_data), results='asis'}
qc_description <- "Day 7 follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID. Non-reconciled Day 7 follow-ups are searched for matched names."
qc_rule <- "IDs of children who cannot be found in the initial Day 0 database are detected and corrected where possible."
qc_type <- "nonvalid_ids_identify_names"
df <- allday7fu_data
idcol1 <- "child_id"
refdf <- allday0_data
idcol2 <- "child_id"
datecol <- "date_day0"
ldate_diff <- -2
udate_diff <- 2
matched_names <- TRUE
cleaning <- "none"
qc_text <- "non-valid participant IDs"
qc_idx <- paste0(qc_nonvalid_day7fu, "a")
qc_export_label <- "nonvalid_pids_day7fu_with_matched_names"
qc_export_description <- "the child ID does not correspond to any ID found in the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_nonvalid_pid_day7fu_records <- n_detected
```

```{r, eval=!is.null(allday7fu_data), results='asis'}
mc_description <- ""
to_correct_df <- allday7fu_data
correction_type <- "correct_day7_non_valid_ids"

# Parameters for the quality check following manual corrections
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_idx <- paste0(qc_nonvalid_day7fu, "b")
cleaning <- "drop_all"

cat(knitr::knit_child('database_export_sub_corrections.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_edit_nonvalid_pid_day7fu_records <- n_mc
n_drop_nonvalid_pid_day7fu_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
allday7fu_data <- cleaned_df
```

#### Non-consistent participant names [Context check `r qc_nonconsistent_name_day7fu`]

```{r}
write(" o Non-consistent participant names", stderr())
```

::: {custom-style="redparagraph"}
Initial check `r qc_nonconsistent_name_day7fu`a
:::

```{r, eval=!is.null(allday7fu_data), results='asis'}
qc_description <- "Day 7 follow-ups are relevant only if the name of the participant matches the name of the participant enrolled at Day 0. Some errors can be introduced when participant IDs have been duplicated or follow-ups have been entered manually."
qc_rule <- "Keep only IDs of children whose name matches the name in the initial Day 0 database."
qc_type <- "inconsistent_names"
df <- allday7fu_data
refdf <- allday0_data
datecol <- "date_day0"
ldate_diff <- -2
udate_diff <- 2
matched_names <- TRUE
qc_text <- "non-consistent participant names"
qc_idx <- paste0(qc_nonconsistent_name_day7fu, "a")
qc_export_label <- "nonconsistent_names_day7fu_with_matched_names"
qc_export_description <- paste0("the child name found in the ", db_name, " is not consistent with the name of the child with the same ID found in the locked Day 0 database")
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_inconsistent_name_day7fu_records <- n_detected
```

```{r, eval=!is.null(allday7fu_data), results='asis'}
mc_description <- ""
to_correct_df <- allday7fu_data
correction_type <- "correct_day7_inconsistent_names"

# Parameters for the quality check following manual corrections
qc_idx <- paste0(qc_nonconsistent_name_day7fu, "b")
cleaning <- "drop_all"

cat(knitr::knit_child('database_export_sub_corrections.Rmd',
                      envir = environment(),
                      quiet = TRUE))

n_edit_inconsistent_name_day7fu_records <- n_mc
n_inconsistent_names_day7fu_records2 <- n_detected
```

```{r, eval=!is.null(cleaned_df)}

allday7fu_data <- cleaned_df
```

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
n_cleaned_allday7fu_records <- nrow(allday7fu_data)
```

```{r}
timci::create_day7fu_qc_flowchart(n_raw_allday7fu_data_records,
                                  n_afterlock_pids_day7fu_records,
                                  n_nonvalid_pid_day7fu_records,
                                  n_edit_nonvalid_pid_day7fu_records,
                                  n_drop_nonvalid_pid_day7fu_records,
                                  n_inconsistent_name_day7fu_records,
                                  n_edit_inconsistent_name_day7fu_records,
                                  n_cleaned_allday7fu_records)
```

### Data overview

```{r}
write(" o Data overview", stderr())
```

```{r, results='asis', eval=timci::is_not_empty(allday7fu_data), results='asis'}
fig_df <- allday7fu_data %>%
  dplyr::mutate(Status = dplyr::case_when(
    proceed_day7 == 1 ~ "Done",
    .default     = "Not done")) %>% 
  dplyr::mutate(week = lubridate::floor_date(as.Date(start),
                                             "week",
                                             week_start = getOption("lubridate.week.start", 1)))

fig_caption <- "Day 7 follow-up data overview over time by facility"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
fill_col <- "Status"
comparison <- "type"

cat(knitr::knit_child('database_export_sub_facet_bar_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, results='asis'}
skimr::skim(allday7fu_data)
```

### Data export

```{r}
write(" o Data export", stderr())
```

```{r}
raw_allday7fu_data <- raw_allday7fu_data[ , !(names(raw_allday7fu_data) %in% day7fu_pii_drops)]
```

```{r, results = 'asis'}
timci::dataset_export(raw_allday7fu_data,
                      "04a",
                      "timci_followup_day7_data",
                      rctls_dir,
                      "Raw Day 7 follow-up data")
```

```{r}
allday7fu_data_no_pii <- allday7fu_data[ , !(names(allday7fu_data) %in% day7fu_pii_drops)]
```

```{r, results = 'asis'}
timci::dataset_export(allday7fu_data_no_pii,
                      "04a",
                      "timci_followup_day7_data",
                      locked_db_dir,
                      "Cleaned Day 7 follow-up data")
```

```{r, results='hide'}
rm(raw_allday7fu_data)
gc()
```
