---
title: "TIMCI Data Quality Report"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King George s Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 3
  word_document:
    toc: true
    reference_docx: word_styles1.docx
    fig_width: 7.5
  html_document: default
params:
  research_facilities: !r data.frame(deviceid = character(0), district = character(0), facility = character(0))
  rctls_dir: !r tempdir()
  participant_zip: !r file.path(tempdir(),"participants.zip")
  spa_dir: !r tempdir()
  qual1_dir: !r tempdir()
  cost_dir: !r tempdir()
  facility_data: NULL
  lock_date: NULL
  facility_data_audit: NULL
  raw_day7fu_data: NULL
  raw_hospit_data: NULL
  raw_day28fu_data: NULL
  raw_withdrawal_data: NULL
  raw_problem_data: NULL
  spa_cgei_data: NULL
  spa_fa_data: NULL
  spa_hcpi_data: NULL
  spa_sco_data: NULL
  tf_data: NULL
  pm_data: NULL
  medical_cost_data: NULL
  hospital_cost_data: NULL
  cgidi_invitation_data: NULL
  cgidi_encryption_data: NULL
  cgidi_interview_data: NULL
---

```{r setup-rmd, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE)
library(dplyr)
```

```{r setup-variables, echo = FALSE}

deidentification_on <- 0

spa_pid <- Sys.getenv("TIMCI_SPA_PID")
qpid <- Sys.getenv("TIMCI_QUAL_PID")
cgidi3_fid <- Sys.getenv("TIMCI_QUAL_CGIDI3_FID")

lock_date <- params$lock_date
lock_rctls_dir <- file.path(params$rctls_dir, "locked")
dir.create(lock_rctls_dir, showWarnings = FALSE)

qual1_dir <- params$qual1_dir
cost_dir <- params$cost_dir

research_facilities <- params$research_facilities

if (!is.null(params$facility_data)) {
  
  facility_data <- params$facility_data
  facility_data_audit <- params$facility_data_audit
  raw_day7fu_data <- params$raw_day7fu_data
  raw_hospit_data <- params$raw_hospit_data
  raw_day28fu_data <- params$raw_day28fu_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  raw_problem_data <- params$raw_problem_data
  spa_cgei_data <- params$spa_cgei_data
  spa_fa_data <- params$spa_fa_data
  spa_hcpi_data <- params$spa_hcpi_data
  spa_sco_data <- params$spa_sco_data
  tf_data <- params$tf_data
  pm_data <- params$pm_data
  medical_cost_data <- params$medical_cost_data
  hospital_cost_data <- params$hospital_cost_data
  cgidi_invitation_data <- params$cgidi_invitation_data
  cgidi_encryption_data <- params$cgidi_encryption_data
  cgidi_interview_data <- params$cgidi_interview_data
  
}
```

\newpage

# Context

## Dates

```{r load-RCT-LS-ODK-facility-data, results='asis'}
start_date <- NULL
end_date <- NULL
if (!is.null(facility_data)) {
  if (nrow(facility_data) > 0) {
    start_date <- min(facility_data$date_visit)
    end_date <- max(facility_data$date_visit)
    if (is.null(lock_date)) {
      lock_date <- end_date
    }
    week_nb <- ceiling(difftime(as.Date(lock_date), as.Date(start_date) - 1,units = "weeks"))
    if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {
      cat(paste0("* Début de la collecte au niveau des postes de santé : **", start_date, "**"))
    } else {
      cat(paste0("* Facility data collection start: **", start_date, "**"))
    }
  }
}
```
```{r, results='asis'}
if (!is.null(spa_sco_data)) {
  if (nrow(spa_sco_data) > 0) {
    spa_start_date <- min(spa_sco_data$date)
    spa_week_nb <- ceiling(difftime(as.Date(spa_start_date), as.Date(start_date) - 1,units = "weeks"))
   if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {
      cat(paste0("* Début de la collecte SPA : **", spa_start_date, "**"))
    } else {
      cat(paste0("* SPA data collection start: **", spa_start_date, "**"))
    }
  }
}
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(facility_data) > 0) {
    if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {
      cat(paste0("* Clôture de la base de données : **", lock_date, "** (semaine **", week_nb,"** de la collecte)"))
    } else {
      cat(paste0("* Database lock: **", lock_date, "** (week **", week_nb,"** of the collect)"))
    }
  }
}
```

## Study facilities

```{r, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {
  research_facilities <- research_facilities[, c("lvl2", "facility_id", "facility_name")]
  research_facilities <- research_facilities[!duplicated(research_facilities$facility_id), ]
  # Sort by district and rename columns
  facilities <- research_facilities %>%
    dplyr::arrange(lvl2) %>%
    dplyr::rename('District sanitaire' = 'lvl2',
                  'ID' = 'facility_id',
                  'Poste de santé' = 'facility_name')
} else{
  research_facilities <- research_facilities[, c("lvl2", "facility_id", "facility_name", "type")]
  research_facilities <- research_facilities[!duplicated(research_facilities$facility_id), ]
  # Sort by district then type of facility
  facilities <- research_facilities %>%
    dplyr::arrange(lvl2, type) %>%
    dplyr::rename('District' = 'lvl2',
                  'ID' = 'facility_id',
                  'Facility' = 'facility_name',
                  'Type' = 'type')
  
}
facilities %>% knitr::kable()
```

```{r, results='asis'}
cat(paste0("Data collection is planned in ", nrow(facilities), " facilities."))
```

## Facility / device correspondence

```{r, results='asis'}
facility_device <- facility_data[facility_data$fid %in% research_facilities$facility_id, ] %>%
  dplyr::select(c('device_id', 'fid')) %>%
  unique()
facility_device <- facility_device %>%
  merge(research_facilities, by.x = 'fid', by.y = 'facility_id', all.x = TRUE) %>%
  dplyr::select(c('device_id', 'fid', 'facility_name'))

# Remove row for Senegal (RA used wrong QR codes)
facility_device <- facility_device[!(facility_device$device_id  == "collect:Qrefi36S3VGHH9VP" & facility_device$fid == "F0059"),]

facility_device %>%
  knitr::kable(col.names = c("Device ID", "Facility ID", "Facility name"))
```

```{r, results='asis'}
cat(paste0("Data collection has been done using ", nrow(facility_device), " tablets."))
```

\newpage

# `r if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India"){'Pragmatic cluster RCT'} else{'Longitudinal Observational Study'}`

## Facility data quality checks

```{r}
screening_data <- timci::extract_screening_data(facility_data)

if (Sys.getenv('TIMCI_COUNTRY') != 'Tanzania') {
  screening_data <- screening_data %>%
    merge(facility_device, by = 'device_id', all.x = TRUE) %>%
    dplyr::rename('facility.x' = 'facility',
                  'facility.y' = 'facility_name')
}

# Order entries by date
screening_data <- screening_data %>%
  dplyr::arrange(date_visit = as.Date(date_visit, "%Y-%m-%d"))
res <- timci::extract_enrolled_participants(facility_data)
day0_data <- res[[1]]
pii <- res[[2]]
n_enrolled <- nrow(day0_data)
```

```{r, results = 'asis'}
locked_screening_data <- screening_data %>% dplyr::filter(date_visit <= as.Date(lock_date, "%Y-%m-%d"))
locked_day0_data <- day0_data %>% dplyr::filter(date_visit <= as.Date(lock_date, "%Y-%m-%d"))
locked_pii <- pii %>% dplyr::filter(date_visit <= as.Date(lock_date, "%Y-%m-%d"))
cat(paste0("There are ", nrow(locked_day0_data), " records between ", start_date, " and ", lock_date, " in the raw Day 0 database."))
```

### Non-valid enrolment facilities [compliance check]

```{r, results='asis'}
cat("Rule: records from facilities different from the ones listed in the first section of this report are removed from the locked database.")
```

```{r, results='asis'}
invalid_facilities <- locked_day0_data[!locked_day0_data$fid %in% research_facilities$facility_id, ]
locked_day0_data <- locked_day0_data[locked_day0_data$fid %in% research_facilities$facility_id, ]
if (nrow(invalid_facilities) > 0) {
  invalid_facilities$child_id %>% knitr::kable(col.names = c("child_id"))
}
```

```{r, results='asis'}
cat(paste0(nrow(invalid_facilities), " records with non-valid enrolment facilities were automatically detected and removed in the locked Day 0 database."))
```

### Non-valid enrolment [compliance check]

#### Caregiver eligibility

```{r, results='asis'}
cat("Rule: Participants with a caregiver below 18 years old are removed from the locked database.")
```

```{r, results='asis'}
underaged_cg <- locked_day0_data[locked_day0_data$cg_eligibility == 0, ]
underaged_cg[c('child_id', 'main_cg_lbl', 'cg_age_yr', 'cg_age_ctg')] %>% knitr::kable(caption = "Underaged caregivers", row.names = FALSE)
```

```{r, results='asis'}
locked_day0_data <- locked_day0_data[locked_day0_data$cg_eligibility == 1, ]
```

```{r, results='asis'}
if (nrow(underaged_cg) == 1) {
  cat(nrow(underaged_cg), "participant with an ineligible caregiver was detected and removed from the locked database.")
} else{
  cat(nrow(underaged_cg), "participants with an ineligible caregiver were detected and removed from the locked database.")
}
```

### Duplicate management

#### Child ID duplicates [compliance check] 

```{r, results='asis'}
cat("Rule: child ID duplicates are removed from the locked database.")
```

```{r check-RCT-LS-ODK-facility-data-001, results='asis'}
day0_qc <- NULL
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    day0_qc <- timci::detect_id_duplicates(locked_day0_data)
    id_duplicates <- day0_qc[day0_qc$id_fq > 1,]
    if (nrow(id_duplicates) > 0) { 
      id_duplicates %>% knitr::kable(caption = "ID duplicates", row.names = FALSE)
    }
  }
}
```

```{r, results='asis'}
day0_data_id_duplicates <- NULL
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (nrow(id_duplicates) > 0) { 
      # Remove duplicate child IDs from the clean database
      day0_data_id_duplicates <- locked_day0_data[locked_day0_data$child_id %in% id_duplicates$child_id, ]
      locked_day0_data <- locked_day0_data[!locked_day0_data$child_id %in% id_duplicates$child_id, ]
      cat(paste0("", nrow(id_duplicates), " duplicated IDs (corresponding to ", nrow(day0_data_id_duplicates), " participants) were automatically detected and removed in the locked Day 0 database."))
    } else {
      cat("No duplicated IDs were detected.")
    }
  } else {
    cat("N/A")
  }
}
```

#### Possible participant duplicates

```{r, results='asis'}
cat("Rule: possible participant duplicates are detected based on their name, sex and date of birth. No specific action at the moment.")
```

```{r check-RCT-LS-ODK-facility-data-002, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    day0_qc1 <- timci::detect_participant_duplicates(locked_pii)
    day0_qc <- merge(day0_qc, day0_qc1, by = 'child_id')
    duplicates <- day0_qc[(day0_qc$ex_name_fq > 1) | (day0_qc$sw_name_fq > 1),]
    if (length(duplicates) > 0 & nrow(duplicates) > 0) { 
      duplicates %>% knitr::kable(caption = "Possible participant duplicates based on their name, sex and date of birth")
    }
  }
}
```

```{r check-RCT-LS-ODK-facility-data-002-disp, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    if (length(duplicates) > 0 & nrow(duplicates) > 0) { 
      cat(paste0("", nrow(duplicates), " possible participant duplicates were detected based on their name, sex and date of birth. No specific action was taken."))
    } else {
      cat("No duplicated names detected")
    }
  } else {
    cat("N/A")
  }
}
  
# Approximate String Matching (Fuzzy Matching)
#df <- dplyr::mutate(pii, full_name = tolower(paste(fs_name, ls_name, sep = ' ')))
#df3 <- df[c("child_id", "full_name")]
#qc3 <- lapply(list(df3$full_name), agrep, x = list(df3$full_name), value = TRUE)
#print(qc3)
```

#### Possible participant duplicates with sex discrepancy

```{r, results='asis'}
cat("Rule: possible participant duplicates detected based on their name and date of birth, but with a sex discrepancy. No specific action at the moment.")
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    day0_qc2 <- timci::detect_namedob_duplicates(locked_pii)
    day0_qc <- merge(day0_qc, day0_qc2, by = 'child_id')
    duplicates2 <- day0_qc[(day0_qc$ex_name2_fq > 1 & day0_qc$ex_name2_fq > day0_qc$ex_name_fq) | (day0_qc$sw_name2_fq > 1 & day0_qc$sw_name2_fq > day0_qc$sw_name_fq),]
    if (length(duplicates2) > 0 & nrow(duplicates2) > 0) { 
      duplicates2 %>% knitr::kable(caption = "Possible participant duplicates based on their name and date of birth, but with a sex discrepancy")
    }
  }
}
```

```{r check-RCT-LS-ODK-facility-data-003-disp, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    if (length(duplicates2) > 0 & nrow(duplicates2) > 0) { 
      cat(paste0("", nrow(duplicates2), " possible participant duplicates detected based on their name and date of birth, but with sex discrepancy. No specific action was taken."))
    } else {
      cat("No possible participant duplicates detected based on their name and date of birth, but with sex discrepancy detected")
    }
  } else {
    cat("N/A")
  }
}
  
# Approximate String Matching (Fuzzy Matching)
#df <- dplyr::mutate(pii, full_name = tolower(paste(fs_name, ls_name, sep = ' ')))
#df3 <- df[c("child_id", "full_name")]
#qc3 <- lapply(list(df3$full_name), agrep, x = list(df3$full_name), value = TRUE)
#print(qc3)
```

```{r export-duplicates}
if (!is.null(day0_qc)) {
  fn <- timci::export_df2xlsx(day0_qc, params$rctls_dir,
                              "07_data_quality_checks")
}
```

### Withdrawal management

```{r, results='asis'}
cat("Rule: withdrawals with documented child IDs are kept in the locked Day 0 database, then removed from all the databases where entries are posterior to the date of withdrawal. If withdrawn IDs cannot be found in the locked Day 0 database, it is assumed that the caregiver withdrew during data collection. More information will be collected about this in the withdrawal form.")
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(raw_withdrawal_data)) {
      if (nrow(raw_withdrawal_data) > 0) { 
        raw_withdrawal_data$child_id <- ifelse(!is.na(raw_withdrawal_data$'page-a1_a_4'), raw_withdrawal_data$'page-a1_a_4', raw_withdrawal_data$'page-a1_a_4a')
        withdrawal_data2 <- raw_withdrawal_data[!is.na(raw_withdrawal_data$child_id), ]
        withdrawal_data2$child_id <- gsub("O", "0", withdrawal_data2$child_id)
        withdrawal_data2 %>%
          
          dplyr::select(c("child_id", "date")) %>%
          knitr::kable(col.names = c("Child ID", "Withdrawal date"))
      }
    }
  }
}
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(raw_withdrawal_data)) {
      if (nrow(raw_withdrawal_data) > 0) { 
        cat(paste0(nrow(raw_withdrawal_data), " withdrawals were reported (among which ", nrow(withdrawal_data2)," withdrawals with documented child IDs)."))
      } else {
        cat("No withdrawal reported.")
      }
    }
  } else {
    cat("N/A")
  }
}
```

```{r, results='asis'}
day0_data_id_withdrawal <- NULL
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(raw_withdrawal_data)) {
      if (nrow(raw_withdrawal_data) > 0) { 
        day0_data_id_withdrawal <- locked_day0_data[locked_day0_data$child_id %in% withdrawal_data2$child_id, ]
        day0_data_id_withdrawal <- day0_data_id_withdrawal %>%
          merge(withdrawal_data2, by = 'child_id', all.x = TRUE)
        if (nrow(day0_data_id_withdrawal) > 0) { 
          day0_data_id_withdrawal %>%
            dplyr::select(c("child_id", "date_visit", "date")) %>%
            knitr::kable(col.names = c("Child ID", "Enrolment date", "Withdrawal date"))
        }
      }
    }
  }
}
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(day0_data_id_withdrawal)) {
      if (nrow(day0_data_id_withdrawal) == 1) {
        cat(paste0(nrow(day0_data_id_withdrawal), " participant who withdrew was found in the locked Day 0 database."))
      } else {
        cat(paste0(nrow(day0_data_id_withdrawal), " participants who withdrew were found in the locked Day 0 database."))
      }
    }
  }
}
```

### Data cleaning summary

```{r, results = 'asis'}
cat(paste0("There are ", nrow(locked_day0_data), " records in the locked Day 0 database."))
```

### Data export

```{r export-screening-data, results = 'asis'}
screening_export_name <- "01_timci_screening_data"
if (!is.null(facility_data)) { 
  fn <- timci::export_df2csvxlsx(screening_data,
                                 params$rctls_dir,
                                 screening_export_name)
}
cat(paste0("* Screening data are exported in ", screening_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
```

```{r export-locked-screening-data, results = 'asis'}
if (!is.null(facility_data)) {
  fn <- timci::export_df2csvxlsx(locked_screening_data,
                                 lock_rctls_dir,
                                 screening_export_name)
}
cat(paste0("* Locked screening data are exported in ", screening_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
```

```{r export-facility-audit}
if (!is.null(facility_data_audit)) { 
  fn <- timci::export_df2csvxlsx(facility_data_audit,
                                 params$rctls_dir,
                                 "00_facility_audit_data")
}
```

```{r split-pii-from-research-data}
if (!is.null(facility_data)) {
  
  if (deidentification_on == 1) {
    deidentified_day0_data <- timci::deidentify_data(day0_data)
    fn <- timci::export_df2csvxlsx(deidentified_day0_data,
                                   params$rctls_dir,
                                   "02_timci_day0_data")
    
    locked_day0_data <- timci::deidentify_data(locked_day0_data)
    fn <- timci::export_df2csvxlsx(locked_day0_data,
                                   lock_rctls_dir,
                                   "02_timci_day0_data")
    
    if (!is.null(day0_data_id_duplicates)) {
      deidentified_day0_data_id_duplicates <- timci::deidentify_data(day0_data_id_duplicates)
      fn <- timci::export_df2csvxlsx(deidentified_day0_data_id_duplicates,
                                     lock_rctls_dir,
                                     "02a_timci_day0_data_id_duplicates")
    }
  } else {
    fn <- timci::export_df2csvxlsx(day0_data,
                                   params$rctls_dir,
                                   "02_timci_day0_data")
    
    fn <- timci::export_df2csvxlsx(locked_day0_data,
                                   lock_rctls_dir,
                                   "02_timci_day0_data")
    
    if (!is.null(day0_data_id_duplicates)) {
      fn <- timci::export_df2csvxlsx(day0_data_id_duplicates,
                                     lock_rctls_dir,
                                     "02a_timci_day0_data_id_duplicates")
    }
  }
  
  xlsx_fname <- timci::export_df2xlsx(pii, tempdir(),
                                      "timci_contact_data")
  pii_pwd <- Sys.getenv("TIMCI_PII_PW")
  zip(params$participant_zip, 
      files = xlsx_fname, 
      flags = paste("-r9Xj --password", pii_pwd))
}
```

```{r, results = 'asis'}
cat(paste0("* Raw Day 0 data are exported in ", "02_timci_day0_data", ".csv/xslx in the ", params$rctls_dir, " folder"))
```

```{r, results = 'asis'}
cat(paste0("* Locked Day 0 data are exported in ", "02_timci_day0_data", ".csv/xslx in the ", lock_rctls_dir, " folder"))
```

```{r export-visit-data, results = 'asis'}
facility_data_name <- "03_timci_facility_visits_data"
if (!is.null(facility_data)) {
  study_data <- timci::extract_all_visits(facility_data)
  
  if (deidentification_on == 1) {
    deidentified_facility_data <- timci::deidentify_data(study_data)
    fn <- timci::export_df2csvxlsx(deidentified_facility_data,
                                  params$rctls_dir,
                                  "03_timci_facility_visits_data")
  } else {
    fn <- timci::export_df2csvxlsx(study_data,
                                  params$rctls_dir,
                                  "03_timci_facility_visits_data")
  }
  #cat(paste0("* Raw facility visit data are exported in ", facility_data_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r export-RCT-LS-ODK-withdrawal, results = 'asis'}
withdrawal_export_name <- "99_withdrawal_data"
if (!is.null(raw_withdrawal_data)) {
  fn <- timci::export_df2csvxlsx(raw_withdrawal_data,
                                params$rctls_dir,
                                withdrawal_export_name)
  cat(paste0("* Raw withdrawal data are exported in ", withdrawal_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(raw_withdrawal_data)) {
  if (!is.null(day0_data_id_withdrawal)) {
    fn <- timci::export_df2csvxlsx(day0_data_id_withdrawal,
                                   lock_rctls_dir,
                                   withdrawal_export_name)
    cat(paste0("* Locked withdrawal data are exported in ", withdrawal_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
  }
}
```

## Day 7 data quality checks

```{r format-RCT-LS-ODK-fu-day7-data}
day7fu_data <- NULL
allday7fu_data <- NULL
if (!is.null(raw_day7fu_data)) {
  if (nrow(raw_day7fu_data) > 0) {
    res <- timci::format_day7_data(raw_day7fu_data)
    day7fu_data <- res[[1]]
    allday7fu_data <- res[[3]]
  }
}
```

```{r, results = 'asis'}
cat(paste0("There are ", nrow(allday7fu_data), " records in the raw Day 7 follow-up database, among which ", nrow(day7fu_data), " records documenting successful follow-ups."))
```

### Non-valid participant IDs [compliance check]

Rule: keep only IDs of children who are enrolled in the locked Day 0 database (note: if data collection is still going-on, all participants enrolled after the lock will be considered as 'invalid' IDs).

```{r}
if (!is.null(raw_day7fu_data)) {
  if (nrow(raw_day7fu_data) > 0) {
    # All follow-ups
    locked_allday7fu_data <- allday7fu_data[allday7fu_data$child_id %in% locked_day0_data$child_id, ]
    allday7fu_data_uids <- allday7fu_data[!allday7fu_data$child_id %in% locked_day0_data$child_id, ]
    # Successful follow-ups
    locked_day7fu_data <- day7fu_data[day7fu_data$child_id %in% locked_day0_data$child_id, ]
    day7fu_data_uids <- day7fu_data[!day7fu_data$child_id %in% locked_day0_data$child_id, ]
    locked_day7fu_data <- locked_day7fu_data %>% dplyr::mutate(window = ifelse(days >= 7 & days <= 10, 1, 0))
    
    allday7fu_data_uids$child_id %>% knitr::kable(col.names = c("child_id"))
  }
}
```

```{r, results='asis'}
if (!is.null(raw_day7fu_data)) {
  if (nrow(raw_day7fu_data) > 0) {
    cat(paste0(nrow(allday7fu_data_uids), " records with non-valid participant IDs were automatically detected and removed in the locked Day 7 follow-up database.\n\n"))
     cat(paste0(nrow(day7fu_data_uids), " records with non-valid participant IDs were automatically detected and removed in the locked successful Day 7 follow-up database."))
  }
}
```

### Duplicate management

#### Successful follow-up duplicates  

```{r, results='asis'}
cat("Rule: only one successful follow-up is kept with the following priority rule: day 7 > day 8 > day 9 > day 10 > day 6 > day 11 and above")
```

```{r check-RCT-LS-ODK-fu-day7-data, results='asis'}
if (!is.null(day7fu_data)) {
  day7fu_qc <- timci::detect_id_duplicates(locked_day7fu_data)
  day7fu_duplicates <- day7fu_qc[day7fu_qc$id_fq > 1,]
  if (length(day7fu_duplicates) > 0) { 
    knitr::kable(day7fu_duplicates,
                 caption = "ID duplicates",
                 row.names = FALSE)
  }
}

if (!is.null(day7fu_data)) {
  if (length(day7fu_duplicates) > 0) { 
    cat(paste0(nrow(day7fu_duplicates), " duplicated successful follow-ups detected."))
  }
}

```

```{r}
if (!is.null(day7fu_data)) {
  # Process duplicates separately
  day7fu_data_duplicates <- locked_day7fu_data[locked_day7fu_data$child_id %in% day7fu_duplicates$child_id, ]
  # Remove all duplicates from the dataframe
  locked_day7fu_data <- locked_day7fu_data[!locked_day7fu_data$child_id %in% day7fu_duplicates$child_id, ]
  # Process duplicates
  processed_day7fu_data_duplicates <- day7fu_data_duplicates %>%
    dplyr::group_by(child_id) %>%
    dplyr::slice_max(order_by = window) %>%
    dplyr::slice_min(order_by = days)
  # Concatenate with processed duplicates
  locked_day7fu_data <- rbind(locked_day7fu_data, processed_day7fu_data_duplicates)
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0(nrow(day7fu_data_duplicates) - nrow(processed_day7fu_data_duplicates), " records were removed in the locked successful Day 7 follow-up database. Note that records duplicated on the same day are kept - we need to define a rule for this."))
}
```

### Day 7 follow-up anterior to enrolment date [consistency check]

To be implemented

### Data cleaning summary

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("There are ", nrow(locked_allday7fu_data), " records in the locked Day 7 follow-up database."))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("There are ", nrow(locked_day7fu_data), " records in the locked successful Day 7 follow-up database."))
}
```

```{r}
if (!is.null(day7fu_data)) {
  ltfu <- timci::generate_ltfu_log(df = day0_data,
                                   fudf = allday7fu_data,
                                   end_date = 12,
                                   raw = FALSE)
}
```

```{r}
if (!is.null(locked_day7fu_data)) {
  locked_ltfu <- timci::generate_ltfu_log(df = locked_day0_data,
                                          fudf = locked_allday7fu_data,
                                          end_date = 12,
                                          raw = FALSE)
}
```

### Data export

```{r export-RCT-LS-ODK-fu-day7-data, results = 'asis'}
day7_export_name <- "04b_timci_followup_successful_day7_data"
if (!is.null(day7fu_data)) {
  
  fn <- timci::export_df2csvxlsx(day7fu_data,
                                 params$rctls_dir,
                                 day7_export_name)
  fn <- timci::export_df2csvxlsx(locked_day7fu_data,
                                lock_rctls_dir,
                                day7_export_name)
}
if (!is.null(allday7fu_data)) {
  
  fn <- timci::export_df2csvxlsx(allday7fu_data,
                                 params$rctls_dir,
                                 "04a_timci_followup_day7_data")
  fn <- timci::export_df2csvxlsx(locked_allday7fu_data,
                                lock_rctls_dir,
                                "04a_timci_followup_day7_data")
  fn <- timci::export_df2csvxlsx(allday7fu_data_uids,
                                lock_rctls_dir,
                                "04c_timci_followup_day7_data_unknown_ids")
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Raw Day 7 follow-up data are exported in ", "04a_timci_followup_day7_data", ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Locked Day 7 follow-up data are exported in ", "04a_timci_followup_day7_data", ".csv/xslx in the ", lock_rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Raw successful Day 7 follow-up data are exported in ", day7_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Locked successful Day 7 follow-up data are exported in ", day7_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
}
```

```{r}
if (!is.null(ltfu)) {
  fn <- timci::export_df2xlsx(ltfu,
                              params$rctls_dir,
                              "04c_day7_lost_to_followup")
}
```

```{r}
if (!is.null(locked_ltfu)) {
  fn <- timci::export_df2xlsx(locked_ltfu,
                              lock_rctls_dir,
                              "04c_day7_lost_to_followup")
}
```

```{r}
if (!is.null(pii) & !is.null(raw_day7fu_data)) {
  fu7all <- timci::generate_fu_log(pii,
                                   raw_day7fu_data,
                                   0,
                                   12,
                                   7,
                                   10,
                                   ext = TRUE,
                                   deidentify = TRUE)
  fn <- timci::export_df2xlsx(fu7all,
                              params$rctls_dir,
                              "04d_timci_deidentified_day7_fu_weekly_log_all")
}
```

## Hospitalisation data quality checks

```{r format-RCT-LS-ODK-fu-hospit-data}
hospit_data <- NULL
if (!is.null(raw_hospit_data)) {
  hospit_data <- timci::format_hospital_data(raw_hospit_data)
}
```

```{r}
if (!is.null(pii)) {
  hospit_fu <- timci::generate_hospital_log(pii = pii,
                                            fu7df = raw_day7fu_data,
                                            day0df = day0_data,
                                            hospitdf = raw_hospit_data,
                                            deidentify = TRUE)
}
```

```{r, results = 'asis'}
cat(paste0("There are ", nrow(hospit_data), " records in the raw hospitalisation follow-up database."))
```

### Non-valid participant IDs

Rule: keep only IDs of children who are enrolled in the locked Day 0 database.

```{r}
if (!is.null(hospit_data)) {
  hospit_data_uids <- hospit_data[!hospit_data$child_id %in% locked_day0_data$child_id, ]
  locked_hospit_data <- hospit_data[hospit_data$child_id %in% locked_day0_data$child_id, ]
}
```

```{r, results='asis'}
if (!is.null(hospit_data)) {
  cat(paste0(nrow(hospit_data_uids), " records with non-valid participant IDs were automatically detected and removed in the locked hospitalisation database."))
}
```

### Duplicate management

```{r, results='asis'}
if (!is.null(hospit_data)) {
  cat("Rule: keep duplicated records if they correspond to different hospitalisations")
}
```

```{r check-RCT-LS-ODK-fu-hospit-data, results='asis'}
if (!is.null(hospit_data)) {
  if (length(hospit_data) > 0) { 
    hospit_data_qc <- timci::detect_id_duplicates(locked_hospit_data)
    hospit_data_duplicates <- hospit_data_qc[hospit_data_qc$id_fq > 1,]
    if (length(hospit_data_duplicates) > 0) {
      if (nrow(hospit_data_duplicates) > 0) { 
         knitr::kable(hospit_data_duplicates, caption = "ID duplicates")
      }
    } else {
      cat("No ID duplicates detected")
    }
  }
}
```

```{r, results='asis'}
if (!is.null(hospit_data)) {
  cat(paste0("", nrow(hospit_data_duplicates), " duplicated IDs were automatically detected and removed in the locked hospitalisation database."))
}
```

### Data export

```{r export-RCT-LS-ODK-fu-hospit-data}
hospit_export_name <- "05a_timci_followup_hospit_data"
if (!is.null(hospit_data)) {
  fn <- timci::export_df2csvxlsx(hospit_data,
                                 params$rctls_dir,
                                 hospit_export_name)
  fn <- timci::export_df2csvxlsx(locked_hospit_data,
                                 lock_rctls_dir,
                                 hospit_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Raw hospitalisation data are exported in ", hospit_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
```

```{r, results = 'asis'}
cat(paste0("* Locked hospitalisation data are exported in ", hospit_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
```

```{r}
if (!is.null(hospit_fu)) {
  hospit_fu_export_name <- "05b_timci_deidentified_hospit_fu_log_all"
  fn <- timci::export_df2xlsx(hospit_fu,
                              params$rctls_dir,
                              hospit_fu_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Hospitalisation log is exported in ", hospit_fu_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat("## Day 28 data quality checks")
}
```

```{r format-RCT-LS-ODK-fu-day28-data}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  day28fu_data <- NULL
  allday28fu_data <- NULL
  if (!is.null(raw_day28fu_data)) {
    if (nrow(raw_day28fu_data) > 0) {
      res <- timci::format_day28_data(raw_day28fu_data)
      day28fu_data <- res[[1]]
      allday28fu_data <- res[[3]]
    }
  }
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat(paste0("There are ", nrow(allday28fu_data), " records in the raw Day 28 follow-up database, among which ", nrow(day28fu_data), " records documenting successful follow-ups."))
}
```


```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat("### Non-valid participant IDs\n\n")
  cat("Rule: keep only IDs of children who are enrolled in the locked Day 0 database.")
}
```

```{r}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  if (!is.null(day28fu_data)) {
    # All follow-ups
    locked_allday28fu_data <- allday28fu_data[allday28fu_data$child_id %in% locked_day0_data$child_id, ]
    allday28fu_data_uids <- allday28fu_data[!allday28fu_data$child_id %in% locked_day0_data$child_id, ]
    # Successful follow-ups
    locked_day28fu_data <- day28fu_data[day28fu_data$child_id %in% locked_day0_data$child_id, ]
    day28fu_data_uids <- day28fu_data[!day28fu_data$child_id %in% locked_day0_data$child_id, ]
    locked_day28fu_data <- locked_day28fu_data %>% dplyr::mutate(window = ifelse(days >= 28 & days <= 32, 1, 0))
    allday28fu_data_uids$child_id %>% knitr::kable(col.names = c("child_id"))
  }
}
```

```{r, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat(paste0(nrow(allday28fu_data_uids), " records with non-valid participant IDs were automatically detected and removed in the locked Day 28 follow-up database."))
}
```

```{r, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat(paste0(nrow(day28fu_data_uids), " records with non-valid participant IDs were automatically detected and removed in the locked successful Day 28 follow-up database."))
}
```

### Duplicate management

```{r, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat("Rule: only one successful follow-up is kept with the following priority rule: day 28 > day 29 > day 30 > day 31 > day 32 > day 27 > day 33 > day 34 > day 35 and above.")
}
```

```{r check-RCT-LS-ODK-fu-day28-data, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  if (!is.null(day28fu_data)) {
    day28fu_qc <- timci::detect_id_duplicates(locked_day28fu_data)
    day28fu_duplicates <- day28fu_qc[day28fu_qc$id_fq > 1,]
    if (length(day28fu_duplicates) > 0) { 
         knitr::kable(day28fu_duplicates,
                      caption = "ID duplicates",
                      row.names = FALSE)
    } else {
      cat("No ID duplicates detected")
    }
  }
}
```

```{r}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  if (!is.null(day28fu_data)) {
    # Process duplicates separately
    day28fu_data_duplicates <- locked_day28fu_data[locked_day28fu_data$child_id %in% day28fu_duplicates$child_id, ]
    processed_day28fu_data_duplicates <- day28fu_data_duplicates %>%
      dplyr::group_by(child_id) %>%
      dplyr::slice_max(order_by = window) %>%
      dplyr::slice_min(order_by = days)
    # Remove all duplicates from the list and concatenate with the filtered list
    locked_day28fu_data <- locked_day28fu_data[!locked_day28fu_data$child_id %in% day28fu_duplicates$child_id, ]
    locked_day28fu_data <- rbind(locked_day28fu_data, processed_day28fu_data_duplicates)
  }
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  n <- nrow(day28fu_data_duplicates) - nrow(processed_day28fu_data_duplicates)
  if (n > 1) {
    cat(paste0(n, " records were removed in the locked successful Day 28 follow-up database (records duplicated on the same day may be kept - we need to define a rule for this)."))
  } else if (n == 1) {
    cat(paste0(n, " record was removed in the locked successful Day 28 follow-up database (records duplicated on the same day may be kept - we need to define a rule for this)."))
  } else{
    cat(paste0("No records were removed in the locked successful Day 28 follow-up database."))
  }
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat("### Data cleaning summary")
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  if (!is.null(day28fu_data)) {
    cat(paste0("There are ", nrow(locked_day28fu_data), " records in the locked Day 28 follow-up database."))
  } else{
    cat("N/A")
  }
}
```

```{r export-RCT-LS-ODK-fu-day28-data, results = 'asis'}
day28_export_name <- "06a_timci_followup_day28_data"
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat("### Data export")
  if (!is.null(day28fu_data)) {
    
    fn <- timci::export_df2csvxlsx(day28fu_data,
                                   params$rctls_dir,
                                   "06_timci_followup_successful_day28_data")
    fn <- timci::export_df2csvxlsx(locked_day28fu_data,
                                   lock_rctls_dir,
                                   "06_timci_followup_successful_day28_data")
  }
  if (!is.null(allday7fu_data)) {
    
    fn <- timci::export_df2csvxlsx(allday28fu_data,
                                   params$rctls_dir,
                                   day28_export_name)
    fn <- timci::export_df2csvxlsx(locked_allday28fu_data,
                                   lock_rctls_dir,
                                   day28_export_name)
    fn <- timci::export_df2csvxlsx(allday28fu_data_uids,
                                   lock_rctls_dir,
                                   "06c_timci_followup_day28_data_unknown_ids")
  }
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat(paste0("* Raw Day 28 data are exported in ", day28_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  cat(paste0("* Locked Day 28 data are exported in ", day28_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (Sys.getenv('TIMCI_COUNTRY') == "Tanzania" || Sys.getenv('TIMCI_COUNTRY') == "India") {
  if (!is.null(pii) & !is.null(raw_day28fu_data)) {
    fu28all <- timci::generate_fu_log(pii,
                                      raw_day28fu_data,
                                      0,
                                      32,
                                      28,
                                      32,
                                      ext = TRUE,
                                      deidentify = TRUE)
    timci::export_df2xlsx(fu28all, params$rctls_dir, "06d_timci_day28_fu_weekly_log_all")
  }
}
```

## Problem report data

```{r export-RCT-LS-ODK-problem}
problem_export_name <- "98_problem_data"
if (!is.null(raw_problem_data)) {
  fn <- timci::export_df2csvxlsx(raw_problem_data,
                                 params$rctls_dir,
                                 problem_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Problem reports are exported in ", problem_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
```

\newpage

# Service Provision Assessment (SPA)

## Facility assessment

### Data export

```{r facility-assessment-export}
spa_fa_export_name <- "01_timci_spa_facility_assessment_data"
if (!is.null(spa_fa_data)) {
  fn <- timci::export_df2csvxlsx(spa_fa_data,
                                 params$spa_dir,
                                 spa_fa_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Raw SPA facility assessment data are exported in ", spa_fa_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
```

## Caregiver exit interview

### Data export

```{r cg-exit-interview-export}
spa_cgei_export_name <- "03_timci_spa_exit_interview_data"
if (!is.null(spa_cgei_data)) {
  fn <- timci::export_df2csvxlsx(spa_cgei_data,
                                 params$spa_dir,
                                 spa_cgei_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Raw SPA caregiver exit interview data are exported in ", spa_cgei_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
```

## Sick child observation data quality checks

```{r, results = 'asis'}
locked_spa_sco_data <- NULL
if (!is.null(spa_sco_data)) {
  locked_spa_sco_data <- spa_sco_data %>% dplyr::filter(date <= as.Date(lock_date, "%Y-%m-%d"))
  cat(paste0("There are ", nrow(locked_spa_sco_data), " records between ", spa_start_date, " and ", lock_date, " in the raw SPA sick child observation database."))
}
```

### Non-valid participant IDs

Rule: keep only IDs of children who are enrolled in the locked Day 0 database.

```{r}
spa_sco_data_uids <- NULL
if (!is.null(spa_sco_data)) {
  # Extract entries of child IDs enrolled in the Day 0 database
  spa_sco_data_uids <- locked_spa_sco_data[!locked_spa_sco_data$'child_identification-pid' %in% locked_day0_data$child_id, ]
  locked_spa_sco_data <- locked_spa_sco_data[locked_spa_sco_data$'child_identification-pid' %in% locked_day0_data$child_id, ]
  
  spa_sco_data_uids$'child_identification-pid' %>% knitr::kable(col.names = c("child_id"))
}
```

```{r, results='asis'}
if (!is.null(spa_sco_data_uids)) {
  n <- nrow(spa_sco_data_uids)
  if (n > 1) {
    cat(paste0(n, " records with non-valid participant IDs were automatically detected and removed in the locked SPA sick child observation database."))
  } else if (n == 1) {
    cat(paste0(n, " record with non-valid participant IDs was automatically detected and removed in the locked SPA sick child observation database."))
  } else{
    cat("No records with non-valid participant IDs were automatically detected.")
  }
}
```

### Duplicate management

```{r, results='asis'}
cat("Rule: keep duplicated records and investigate the reason for having duplicates")
```

```{r, results='asis'}
if (!is.null(spa_sco_data)) {
  if (length(spa_sco_data) > 0) {
    spa_sco_data_qc <- timci::detect_id_duplicates(locked_spa_sco_data %>% dplyr::rename(child_id = 'child_identification-pid'))
    spa_sco_data_duplicates <- spa_sco_data_qc[spa_sco_data_qc$id_fq > 1,]
    if (length(spa_sco_data_duplicates) > 0) {
      if (nrow(spa_sco_data_duplicates) > 0) {
         knitr::kable(spa_sco_data_duplicates, caption = "ID duplicates")
      }
    } else {
      cat("No ID duplicates detected")
    }
  }
}
```

```{r, results='asis'}
if (!is.null(spa_sco_data)) {
  if (length(spa_sco_data_duplicates) > 0) { 
    cat(paste0(nrow(spa_sco_data_duplicates), " duplicated IDs were automatically detected. No action was taken in the locked SPA sick child observation database."))
  } else {
    cat(paste0("No duplicated IDs were automatically detected. No action was taken in the locked SPA sick child observation database."))
  }
}
```

### Data cleaning summary

```{r, results = 'asis'}
if (!is.null(spa_sco_data)) {
  cat(paste0("There are ", nrow(locked_spa_sco_data), " records in the locked SPA sick child observation database."))
}
```

### Data export

```{r sick-child-observation-export}
spa_sco_export_name <- "04_timci_spa_consultation_obs_data"
if (!is.null(spa_sco_data)) {
  if (deidentification_on == 1) {
    deidentified_spa_sco_data <- timci::deidentify_spa_data(spa_sco_data)
    fn <- timci::export_df2csvxlsx(deidentified_spa_sco_data,
                                   params$spa_dir,
                                   spa_sco_export_name)
    fn <- timci::export_df2csvxlsx(locked_spa_sco_data,
                                   lock_rctls_dir,
                                   spa_sco_export_name)
    
    fn <- timci::export_df2csvxlsx(spa_sco_data_uids,
                                   lock_rctls_dir,
                                   "04_timci_spa_consultation_obs_data_unknown_ids")
  } else {
    fn <- timci::export_df2csvxlsx(spa_sco_data,
                                   params$spa_dir,
                                   spa_sco_export_name)
    fn <- timci::export_df2csvxlsx(locked_spa_sco_data,
                                   lock_rctls_dir,
                                   spa_sco_export_name)
    fn <- timci::export_df2csvxlsx(spa_sco_data_uids,
                                   lock_rctls_dir,
                                   "04_timci_spa_consultation_obs_data_unknown_ids")
  }
  
}
```

```{r, results = 'asis'}
cat(paste0("* Raw SPA sick child observation data are exported in ", spa_sco_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
```

```{r, results = 'asis'}
cat(paste0("* Locked SPA sick child observation data are exported in ", spa_sco_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
```

## Healthcare provider interview data quality checks


```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  spa_hcpi_data <- process_spa_hcpi_data(spa_hcpi_data)
  cat(paste0("There are ", nrow(spa_hcpi_data), " records in the raw SPA healthcare provider interview database."))
}
```

### Non-valid participant IDs

Rule: keep only IDs of healthcare providers who are observed in the locked SPA sick child observation database.

```{r}
# Extract entries of child IDs enrolled in the Day 0 database
if (!is.null(spa_hcpi_data)) {
  spa_hcpi_data_uids <- spa_hcpi_data[!spa_hcpi_data$hcp_id %in% locked_spa_sco_data$'hcp_identification-hcpid', ]
  locked_spa_hcpi_data <- spa_hcpi_data[spa_hcpi_data$hcp_id %in% locked_spa_sco_data$'hcp_identification-hcpid', ]
  
  spa_hcpi_data_uids$hcp_id %>% knitr::kable(col.names = c("hcp_id"))
}
```

```{r, results='asis'}
if (!is.null(spa_hcpi_data)) {
  n <- nrow(spa_hcpi_data_uids)
  if (n > 1) {
    cat(paste0(n, " records with non-valid participant IDs were automatically detected and removed in the locked SPA healthcare provider interview database."))
  } else if (n == 1) {
    cat(paste0(n, " record with non-valid participant IDs was automatically detected and removed in the locked SPA healthcare provider interview database."))
  } else{
    cat("No records with non-valid participant IDs were automatically detected.")
  }
}
```

### Duplicate management

```{r, results='asis'}
cat("Rule: keep duplicated records and investigate the reason for duplicates")
```

```{r check-SPA-hcp-interview-data, results='asis'}
if (!is.null(spa_hcpi_data)) {
  if (length(spa_hcpi_data) > 0) { 
    spa_hcpi_data_qc <- timci::detect_id_duplicates(locked_spa_hcpi_data, hcp_id)
    spa_hcpi_data_duplicates <- spa_hcpi_data_qc[spa_hcpi_data_qc$id_fq > 1,]
    if (length(spa_hcpi_data_duplicates) > 0) {
      if (nrow(spa_hcpi_data_duplicates) > 0) {
        knitr::kable(spa_hcpi_data_duplicates, caption = "ID duplicates")
      }
    } else {
      cat("No ID duplicates detected")
    }
  }
}
```

```{r, results='asis'}
if (!is.null(spa_hcpi_data)) {
  if (length(spa_hcpi_data_duplicates) > 0) { 
    cat(paste0(nrow(spa_hcpi_data_duplicates), " duplicated IDs were automatically detected. No action was taken in the locked SPA healthcare provider interview database."))
  } else {
    cat(paste0("No duplicated IDs were automatically detected. No action was taken in the locked SPA healthcare provider interview database."))
  }
}
```

### Data cleaning summary

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  cat(paste0("There are ", nrow(locked_spa_hcpi_data), " records in the locked SPA healthcare provider interview database."))
}
```

### Data export

```{r hcp-interview-export}
spa_hcpi_export_name <- "02_timci_spa_provider_interview_data"
if (!is.null(spa_hcpi_data)) {
  fn <- timci::export_df2csvxlsx(spa_hcpi_data,
                                 params$spa_dir,
                                 spa_hcpi_export_name)
  
  fn <- timci::export_df2csvxlsx(locked_spa_hcpi_data,
                                 lock_rctls_dir,
                                 spa_hcpi_export_name)
}
```

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  cat(paste0("* Raw SPA healthcare provider interview data are exported in ", spa_hcpi_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  cat(paste0("* Locked SPA healthcare provider interview data are exported in ", spa_hcpi_export_name, ".csv/xslx in the ", lock_rctls_dir, " folder"))
}
```

\newpage

# Process mapping & Time-flow

## Time-flow

```{r time-flow-export}
if (!is.null(tf_data)) {
  if (!is.null(tf_data[[1]])) {
    fn <- timci::export_df2csvxlsx(tf_data[[1]],
                                   params$spa_dir,
                                   "05a_timci_timeflow_data")
  }
  if (!is.null(tf_data[[2]])) {
    fn <- timci::export_df2csvxlsx(tf_data[[2]],
                                   params$spa_dir,
                                   "05b_timci_timeflow_audit")
  }
  if (!is.null(tf_data[[3]])) {
    fn <- timci::export_df2csvxlsx(tf_data[[3]],
                                   params$spa_dir,
                                   "05c_timci_timeflow_steps")
  }
}
```

```{r, results = 'asis'}
if (!is.null(tf_data)) {
  cat(paste0("* Raw time-flow data are exported in ", "05a_timci_timeflow_data", ".csv/xslx in the ", params$spa_dir, " folder"))
}
```

## Process mapping

```{r process-mapping-export}
pm_export_name <- "06_timci_processmapping_data"
if (!is.null(pm_data)) {
  fn <- timci::export_df2csvxlsx(pm_data,
                                 params$spa_dir,
                                 pm_export_name)
}
```

```{r, results = 'asis'}
if (!is.null(pm_data)) {
  cat(paste0("* Raw process mapping data are exported in ", pm_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
}
```

\newpage

# Cost & Cost-effectiveness

## Medical costs

```{r medical-cost-export}
medical_cost_export_name <- "01_timci_medical_cost_data"
if (!is.null(medical_cost_data)) {
  fn <- timci::export_df2csvxlsx(medical_cost_data,
                                 cost_dir,
                                 medical_cost_export_name)
}
```

## Hospital costs

```{r hospital-cost-export}
hospital_cost_export_name <- "02_timci_hospital_cost_data"
if (!is.null(hospital_cost_data)) {
  fn <- timci::export_df2csvxlsx(hospital_cost_data,
                                 cost_dir,
                                 hospital_cost_export_name)
}
```

\newpage

# Qualitative studies

## Caregiver in-depth interview

No data cleaning for the lock.

```{r cg-idi-potential-participants}
if (!is.null(day0_data) && !is.null(day7fu_data)) {
  cg_qual_export_data <- timci::generate_cg_log(day0_data, day7fu_data)
  fn <- timci::export_df2csvxlsx(cg_qual_export_data,
                                 qual1_dir,
                                 "cg_idi_participants")
}
```

```{r cg-idi-invitation-export}
if (!is.null(cgidi_invitation_data)) {
  fn <- timci::export_df2csvxlsx(cgidi_invitation_data,
                                 qual1_dir,
                                 "01_timci_cg_invitation_data")
}
```

```{r cg-idi-encryption-export}
if (!is.null(cgidi_encryption_data)) {
  fn <- timci::export_df2csvxlsx(cgidi_encryption_data,
                                 qual1_dir,
                                 "02_timci_cg_encryption_data")
}
```

```{r cg-idi-interview-export}
if (!is.null(cgidi_interview_data)) {
  
  # Filter data
  drops <- c("encryption-name",
             "encryption-child_name",
             "encryption-phonenb1",
             "encryption-phonenb2",
             "other_participant-cg2_name")
  cgidi_interview_data <- cgidi_interview_data[, !(names(cgidi_interview_data) %in% drops)]
  
  fn <- timci::export_df2csvxlsx(cgidi_interview_data,
                                 qual1_dir,
                                 "03_timci_cg_interview_data")

  sl <- ruODK::submission_list(pid = qpid,
                               fid = cgidi3_fid)
  
  # Loop on all rows
  for (i in 1:nrow(sl)) {
    crow <- cgidi_interview_data[i,]
    uuid <- crow$'meta-instanceID'
    cpath <- file.path(qual1_dir, crow$'encryption-participant')
    print(paste0("Participant: ", crow$'encryption-participant'))
    dir.create(cpath, showWarnings = FALSE)
    # Create a new dataframe using the transpose of crow
    tcrow <- as.data.frame(t(as.matrix(crow)))
    names(tcrow)[names(tcrow) == "V1"] <- "values"
    fn <- export_df2xlsx(tcrow, cpath, "data")
    
    # Download attachments
    al <- ruODK::get_one_submission_attachment_list(pid = qpid,
                                                    fid = cgidi3_fid,
                                                    uuid)
    for (j in 1:nrow(al)) {
      aid <- al$name[[j]]
      print(paste0("Attachment: ", aid))
      ruODK::attachment_get(pid = qpid,
                            fid = cgidi3_fid,
                            uuid, 
                            aid,
                            local_dir = cpath)
    }
  }
}
```
