---
title: "TIMCI Data Quality Report"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King Georges Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M GMT%z')`"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 4
    extra_dependencies:
      float: null
      flafter: null
      bm: null
      babel: ["french","english"]
      graphicx: null
      fancyhdr: null
      lastpage: null
  word_document:
    toc: true
    toc_depth: 4
    reference_docx: word_styles1.docx
    fig_width: 7.5
  html_document: default
params:
  research_facilities: !r data.frame(deviceid = character(0), district = character(0), facility = character(0))
  rctls_dir: !r tempdir()
  participant_zip: !r file.path(tempdir(),"participants.zip")
  spa_dir: !r tempdir()
  qualcg_dir: !r tempdir()
  qualhcp_dir: !r tempdir()
  qualkii_dir: !r tempdir()
  qualos_dir: !r tempdir()
  cost_dir: !r tempdir()
  qc_dir: !r tempdir()
  locked_db_dir: !r tempdir()
  facility_data: NULL
  lock_date: NULL
  facility_data_audit: NULL
  raw_day7fu_data: NULL
  raw_hospit_data: NULL
  raw_day28fu_data: NULL
  raw_withdrawal_data: NULL
  raw_problem_data: NULL
  spa_cgei_data: NULL
  spa_fa_data: NULL
  spa_hcpi_data: NULL
  spa_sco_data: NULL
  tf_data: NULL
  pm_data: NULL
  medical_cost_data: NULL
  hospital_cost_data: NULL
  cgidi_invitation_data: NULL
  cgidi_encryption_data: NULL
  cgidi_interview_data: NULL
  hcpidi_interview_data: NULL
  kii_interview_data: NULL
  online_survey_data: NULL
  is_pilot: FALSE
---

```{r setup-library, include=FALSE}
library(dplyr)
library(knitr)
library(skimr)
library(dataMaid)
```

```{r setup-options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
options(knitr.table.format = "pipe",
        knitr.kable.NA = "")
```

```{r}
is_india <- Sys.getenv('TIMCI_COUNTRY') == 'India'
is_tanzania <- Sys.getenv('TIMCI_COUNTRY') == 'Tanzania'
is_kenya <- Sys.getenv('TIMCI_COUNTRY') == 'Kenya'
is_senegal <- Sys.getenv('TIMCI_COUNTRY') == 'Senegal'
is_rct <- is_tanzania | is_india
```

```{r translations}
if (is_senegal) {
  notice_str <- ""
  screening_times_str <- "Heures de screening"
} else {
  notice_str <- ""
  screening_times_str <- "Screening times"
}
```

```{r setup-variables, echo = FALSE}
deidentification_on <- FALSE

spa_pid <- Sys.getenv("TIMCI_SPA_PID")
qpid <- Sys.getenv("TIMCI_QUAL_PID")
cgidi3_fid <- Sys.getenv("TIMCI_QUAL_CGIDI3_FID")

lock_date <- params$lock_date

rctls_dir <- params$rctls_dir
qualcg_dir <- params$qualcg_dir
qualhcp_dir <- params$qualhcp_dir
qualkii_dir <- params$qualkii_dir
qualos_dir <- params$qualos_dir
cost_dir <- params$cost_dir
locked_db_dir <- params$locked_db_dir
qc_dir <- params$qc_dir

research_facilities <- params$research_facilities

if (!is.null(params$facility_data)) {
  
  facility_data <- params$facility_data
  facility_data_audit <- params$facility_data_audit
  raw_day7fu_data <- params$raw_day7fu_data
  raw_hospit_data <- params$raw_hospit_data
  raw_day28fu_data <- params$raw_day28fu_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  raw_problem_data <- params$raw_problem_data
  spa_cgei_data <- params$spa_cgei_data
  spa_fa_data <- params$spa_fa_data
  spa_hcpi_data <- params$spa_hcpi_data
  spa_sco_data <- params$spa_sco_data
  tf_data <- params$tf_data
  pm_data <- params$pm_data
  medical_cost_data <- params$medical_cost_data
  hospital_cost_data <- params$hospital_cost_data
  cgidi_invitation_data <- params$cgidi_invitation_data
  cgidi_encryption_data <- params$cgidi_encryption_data
  cgidi_interview_data <- params$cgidi_interview_data
  hcpidi_interview_data <- params$hcpidi_interview_data
  kii_interview_data <- params$kii_interview_data
  online_survey_data <- params$online_survey_data
  is_pilot <- params$is_pilot
  
}
```

```{r}
qc_screening_w_nonvalid_deviceid <- "DQC_00_01"
qc_underaged_cg_id <- "DQC_00_02"
qc_dup_repeats_id1 <- "DQC_00_03a"
qc_dup_repeats_id2 <- "DQC_00_03b"
qc_screening_after_lockdate <- "DQC_00_04"
qc_nonvalid_fid1 <- "DQC_00_05a"
qc_nonvalid_fid2 <- "DQC_00_05b"
qc_incorrect_enrolment_date <- "DQC_00_06"
qc_nontimely_completion_id <- "DQC_00_07"
qc_nontimely_submission_id <- "DQC_00_08"
qc_duplicate_id1 <- "DQC_00_09a"
qc_duplicate_id2 <- "DQC_00_09b"
qc_multiple_enrolment_id <- "DQC_00_10"
qc_multiple_enrolment_sex_discrepancy_id <- "DQC_00_11"
qc_missing_cp_id <- "DQC_00_12"
qc_missing_diagnosis_id <- "DQC_00_13"
qc_missing_referral_id <- "DQC_00_14"
qc_pox_ <- "DQC_00_15"
qc_summary_id <- "DQC_00_16"
qc_pids_out_lock_range_day7fu <- "DQC_07_01"
qc_nonvalid_day7fu <- "DQC_07_02"
qc_duplicated_day7fu <- "DQC_07_03"
qc_hospit_before_enrolment_day7fu <- "DQC_07_04"
qc_death_before_enrolment_day7fu <- "DQC_07_05"
qc_pids_out_lock_range_hospitfu <- "DQC_HS_01"
qc_nonvalid_hospitfu <- "DQC_HS_02"
qc_duplicated_hospitfu <- "DQC_HS_03"
qc_hospit_before_enrolment <- "DQC_HS_04"
qc_pids_out_lock_range_day28fu <- "DQC_28_01"
qc_nonvalid_day28fu <- "DQC_28_02"
qc_duplicated_day28fu <- "DQC_28_03"
qc_hospit_before_enrolment_day28fu <- "DQC_28_04"
qc_death_before_enrolment_day28fu <- "DQC_28_05"
qc_nonreconciled_withdrawals_id <- "DQC_WD_01"
qc_spa_sco_nonvalid_ids <- "DQC_SP_01"
qc_spa_sco_duplicates <- "DQC_SP_02"
qc_spa_sco_incomplete <- "DQC_SP_03"
qc_spa_hcpi_nonvalid_ids <- "DQC_SP_04"
qc_spa_hcpi_duplicates <- "DQC_SP_05"

action_alert_no_modification <- "Alert to the study team. No modification of the database."
```

\newpage

# Context

```{r}
write(formats2h2("Context"),stderr())
write("Write contextual information including dates, study facilities, facility and device correspondence", stderr())
```

```{r}
start_date <- NULL
end_date <- NULL
facility_data_is_not_null <- !is.null(facility_data)
facility_data_is_not_empty <- timci::is_not_empty(facility_data)
```

## Dates

```{r load-RCT-LS-ODK-facility-data, results='asis', eval=facility_data_is_not_empty}
start_date <- min(facility_data$date_visit)
end_date <- max(facility_data$date_visit)
if (is.null(lock_date)) {
  lock_date <- end_date
}
week_nb <- ceiling(difftime(as.Date(lock_date), as.Date(start_date) - 1,units = "weeks"))
if (is_senegal) {
  cat(paste0("* Début de la collecte longitudinale au niveau des postes de santé : **", start_date, "**"))
} else {
  cat(paste0("* Facility data collection start: **", start_date, "**"))
}
```

```{r, results='asis'}
spa_start_date <- NULL
if (!is.null(spa_sco_data)) {
  if (nrow(spa_sco_data) > 0) {
    spa_start_date <- min(spa_sco_data$date)
    spa_week_nb <- ceiling(difftime(as.Date(spa_start_date), as.Date(start_date) - 1,units = "weeks"))
   if (is_senegal) {
      cat(paste0("* Début de la collecte SPA : **", spa_start_date, "**"))
    } else {
      cat(paste0("* SPA data collection start: **", spa_start_date, "**"))
    }
  }
}
```

```{r, results='asis', eval=facility_data_is_not_empty}
if (is_senegal) {
  cat(paste0("* Clôture de la base de données : **", lock_date, "** (semaine **", week_nb,"** de la collecte)"))
} else {
  cat(paste0("* Database lock: **", lock_date, "** (week **", week_nb,"** of the data collection)"))
}
```

## Study facilities

```{r context-load-facilities, results='asis'}
if (is_senegal) {
  research_facilities <- research_facilities[, c("lvl2", "facility_id", "facility_name", "training_date", "rollout_date")]
  research_facilities <- research_facilities[!duplicated(research_facilities$facility_id), ]
} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {
  research_facilities <- research_facilities[, c("lvl2", "facility_id", "facility_name", "type", "training_date", "rollout_date")]
  research_facilities <- research_facilities[!duplicated(research_facilities$facility_id), ]
} else{
  research_facilities <- research_facilities[, c("lvl2", "facility_id", "facility_name", "type")]
  research_facilities <- research_facilities[!duplicated(research_facilities$facility_id), ]
}
```

```{r context-format-facility-info, results='asis'}
if (is_senegal) {
  # Sort by district and rename columns
  facility_disp <- research_facilities %>%
    dplyr::arrange(lvl2) %>%
    dplyr::rename('District sanitaire' = 'lvl2',
                  'ID' = 'facility_id',
                  'Poste de santé' = 'facility_name',
                  "Fin pré-intervention" = 'training_date',
                  "Début post-intervention" = 'rollout_date')
} else if(is_kenya){
  # Sort by County then type of facility
  facility_disp <- research_facilities %>%
    dplyr::arrange(lvl2, type) %>%
    dplyr::rename('County' = 'lvl2',
                  'ID' = 'facility_id',
                  'Facility' = 'facility_name',
                  'Type' = 'type',
                  "Baseline end" = 'training_date',
                  "Roll-out date" = 'rollout_date')
  
} else {
  # Sort by district then type of facility
  facility_disp <- research_facilities %>%
    dplyr::arrange(lvl2, type) %>%
    dplyr::rename('District' = 'lvl2',
                  'ID' = 'facility_id',
                  'Facility' = 'facility_name',
                  'Type' = 'type')
}
```

```{r, results='asis'}
cat(paste0("Data collection was planned in **", nrow(research_facilities), "** facilities."))
```

```{r, results='asis'}
facility_disp %>%
  knitr::kable()
```

## Facility / device correspondence

```{r, results='asis'}
facility_device <- facility_data[facility_data$fid %in% research_facilities$facility_id, ] %>%
  dplyr::select(c('device_id', 'fid')) %>%
  unique()
facility_device <- facility_device %>%
  merge(research_facilities, by.x = 'fid', by.y = 'facility_id', all.x = TRUE) %>%
  dplyr::select(c('device_id', 'fid', 'facility_name'))
```

```{r, results='asis'}
if (is_senegal){
  # Remove row for Senegal (RA used wrong QR codes)
  facility_device <- facility_device[!(facility_device$device_id  == "collect:Qrefi36S3VGHH9VP" & facility_device$fid == "F0059"),]
}
```

```{r, results='asis'}
cat(paste0("Data collection has been done using **", nrow(facility_device), "** tablets."))
```

```{r, results='asis'}
facility_device %>%
  knitr::kable(col.names = c("Device ID", "Facility ID", "Facility name"))
```

\newpage

# `r if (is_rct) {'Pragmatic cluster Randomised Controlled Trial (RCT)'} else {'Longitudinal Observational Study (LS)'}`

```{r db-export-screening-subsection, child = 'database_export_sub_rctls_screening.Rmd'}
```

\newpage

```{r db-export-day0-subsection, child = 'database_export_sub_rctls_day0.Rmd'}
```

\newpage

```{r}
day7fu_is_not_null <- !is.null(raw_day7fu_data)
day7fu_is_not_empty <- timci::is_not_empty(raw_day7fu_data)
```

```{r db-export-day7fu-subsection, child = if(day7fu_is_not_empty) 'database_export_sub_rctls_day7.Rmd'}
```

\newpage

```{r db-export-successfulday7fu-subsection, child = if(day7fu_is_not_empty) 'database_export_sub_rctls_day7_outcome.Rmd'}
```

\newpage

```{r}
hospitfu_is_not_null <- !is.null(raw_hospit_data)
hospitfu_is_not_empty <- timci::is_not_empty(raw_hospit_data)
```

```{r db-export-hospit-subsection, child = if(hospitfu_is_not_empty) 'database_export_sub_rctls_hospit.Rmd'}
```

```{r}
day28fu_is_not_null <- !is.null(raw_day28fu_data)
day28fu_is_not_empty <- timci::is_not_empty(raw_day28fu_data)
```

```{r db-export-day28fu-subsection, child = if (is_rct & day28fu_is_not_empty) 'database_export_sub_rctls_day28.Rmd'}
```

```{r db-export-successfulday28fu-subsection, child = if(is_rct & day28fu_is_not_empty) 'database_export_sub_rctls_day28_outcome.Rmd'}
```

\newpage

```{r db-export-withdrawals-subsection, child = if(day0_is_not_empty) 'database_export_sub_rctls_withdrawals.Rmd'}
```

```{r db-export-deaths-subsection, child = if (day7fu_is_not_empty) 'database_export_sub_rctls_deaths.Rmd'}
```

\newpage

# Service Provision Assessment (SPA)

```{r db-export-spa-subsection, child = 'database_export_sub_spa.Rmd'}
```

\newpage

# Process mapping & Time-flow

```{r db-export-pmtf-subsection, child = 'database_export_sub_pmtf.Rmd'}
```

\newpage

# Cost & Cost-effectiveness

```{r db-export-cost-subsection, child = 'database_export_sub_cost.Rmd'}
```

\newpage

# Qualitative studies

```{r db-export-qual-subsection, child = 'database_export_sub_qual.Rmd'}
```

\newpage

# Technical information

```{r, results='asis'}
df_session <- devtools::session_info(include_base = TRUE)
```

```{r, results='asis'}
df_session_platform <- df_session$platform %>% 
  unlist(.) %>% 
  as.data.frame(.) %>% 
  tibble::rownames_to_column(.)
colnames(df_session_platform) <- c("Setting", "Value")
df_session_platform %>%
  knitr::kable()
```

```{r, results='asis', echo=FALSE}
df_session_packages <- df_session$packages[c("loadedversion", "date", "source")]
colnames(df_session_packages) <- c("Loaded version", "Date", "Source")
df_session_packages %>%
  knitr::kable()
```

```{r}
locked_day0_data <- day0_data
locked_allday7fu_data <- allday7fu_data
```

```{r, eval=is_rct}

locked_allday28fu_data <- allday28fu_data

# Save locked data to *.rda file to be reused in other rmarkdown documents if needed
save(locked_day0_data,
     locked_allday7fu_data,
     locked_allday28fu_data,
     locked_hospit_data,
     locked_spa_sco_data,
     locked_spa_hcpi_data,
     spa_cgei_data,
     spa_fa_data,
     file = "timci_locked_data.rda")
```

```{r, eval=!is_rct}
# Save locked data to *.rda file to be reused in other rmarkdown documents if needed
save(locked_day0_data,
     locked_allday7fu_data,
     locked_hospit_data,
     locked_spa_sco_data,
     locked_spa_hcpi_data,
     spa_cgei_data,
     spa_fa_data,
     file = "timci_locked_data.rda")
```
