---
title: "TIMCI Data Quality Report"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King Georges Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M GMT%z')`"
output:
  pdf_document:
    number_sections: true
    toc: true
    toc_depth: 4
    extra_dependencies:
      float: null
      flafter: null
      bm: null
      babel: ["french","english"]
      graphicx: null
      fancyhdr: null
      lastpage: null
  word_document:
    toc: true
    toc_depth: 4
    reference_docx: word_styles1.docx
    fig_width: 7.5
  html_document: default
params:
  research_facilities: !r data.frame(deviceid = character(0), district = character(0), facility = character(0))
  rctls_dir: !r tempdir()
  participant_zip: !r file.path(tempdir(),"participants.zip")
  spa_dir: !r tempdir()
  qualcg_dir: !r tempdir()
  qualhcp_dir: !r tempdir()
  qualkii_dir: !r tempdir()
  qualos_dir: !r tempdir()
  cost_dir: !r tempdir()
  qc_dir: !r tempdir()
  locked_db_dir: !r tempdir()
  facility_data: NULL
  start_date: NULL
  lock_date: NULL
  facility_data_audit: NULL
  raw_drug_data: NULL
  raw_day7fu_data: NULL
  raw_hospit_data: NULL
  raw_day28fu_data: NULL
  raw_withdrawal_data: NULL
  raw_problem_data: NULL
  spa_cgei_data: NULL
  spa_fa_data: NULL
  spa_hcpi_data: NULL
  spa_sco_data: NULL
  tf_data: NULL
  pm_data: NULL
  medical_cost_data: NULL
  hospital_cost_data: NULL
  cgidi_invitation_data: NULL
  cgidi_encryption_data: NULL
  cgidi_interview_data: NULL
  hcpidi_interview_data: NULL
  kii_interview_data: NULL
  online_survey_data: NULL
  is_pilot: FALSE
---

```{r setup-library, include=FALSE}
library(dplyr)
library(knitr)
library(skimr)
library(dataMaid)
library(ggplot2)
library(extrafont)
library(lubridate)
library(rlang)
loadfonts()
```

```{r setup-options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
options(knitr.table.format = "pipe",
        knitr.kable.NA = "")
```

```{r}
is_india <- Sys.getenv('TIMCI_COUNTRY') == 'India'
is_tanzania <- Sys.getenv('TIMCI_COUNTRY') == 'Tanzania'
is_kenya <- Sys.getenv('TIMCI_COUNTRY') == 'Kenya'
is_senegal <- Sys.getenv('TIMCI_COUNTRY') == 'Senegal'
is_ls <- is_kenya | is_senegal
is_rct <- is_tanzania | is_india
```

```{r translations}
if (is_senegal) {
  notice_str <- ""
  screening_times_str <- "Heures de screening"
} else {
  notice_str <- ""
  screening_times_str <- "Screening times"
}
```

```{r setup-variables, echo = FALSE}
deidentification_on <- FALSE

spa_pid <- Sys.getenv("TIMCI_SPA_PID")
qpid <- Sys.getenv("TIMCI_QUAL_PID")
cgidi3_fid <- Sys.getenv("TIMCI_QUAL_CGIDI3_FID")

start_date <- params$start_date
lock_date <- params$lock_date

rctls_dir <- params$rctls_dir
qualcg_dir <- params$qualcg_dir
qualhcp_dir <- params$qualhcp_dir
qualkii_dir <- params$qualkii_dir
qualos_dir <- params$qualos_dir
cost_dir <- params$cost_dir
locked_db_dir <- params$locked_db_dir
qc_dir <- params$qc_dir

research_facilities <- params$research_facilities

if (!is.null(params$facility_data)) {
  
  facility_data <- params$facility_data
  facility_data_audit <- params$facility_data_audit
  raw_drug_data <- params$raw_drug_data
  raw_day7fu_data <- params$raw_day7fu_data
  raw_hospit_data <- params$raw_hospit_data
  raw_day28fu_data <- params$raw_day28fu_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  raw_problem_data <- params$raw_problem_data
  spa_cgei_data <- params$spa_cgei_data
  spa_fa_data <- params$spa_fa_data
  spa_hcpi_data <- params$spa_hcpi_data
  spa_sco_data <- params$spa_sco_data
  tf_data <- params$tf_data
  pm_data <- params$pm_data
  medical_cost_data <- params$medical_cost_data
  hospital_cost_data <- params$hospital_cost_data
  cgidi_invitation_data <- params$cgidi_invitation_data
  cgidi_encryption_data <- params$cgidi_encryption_data
  cgidi_interview_data <- params$cgidi_interview_data
  hcpidi_interview_data <- params$hcpidi_interview_data
  kii_interview_data <- params$kii_interview_data
  online_survey_data <- params$online_survey_data
  is_pilot <- params$is_pilot
  
}
```

```{r}
###################
# Export settings #
###################

# Screening quality check IDs
##############################
qc_screening_w_nonvalid_deviceid <- "DQC_00_0SG_01"
qc_nontimely_submission_id <- "DQC_00_0SG_02"
qc_nontimely_completion_id <- "DQC_00_0SG_03"
qc_incorrect_date_setup <- "DQC_00_0SG_04"
qc_screening_before_startdate <- "DQC_00_0SG_05"
qc_screening_after_lockdate <- "DQC_00_0SG_06"
qc_screening_other_fids <- "DQC_00_0SG_07"
qc_underaged_cg_id <- "DQC_00_0SG_08"
qc_dup_repeats_id1 <- "DQC_00_0SG_09a"
qc_dup_repeats_id2 <- "DQC_00_0SG_09b"

# Day 0 drug quality check IDs
###############################
qc_drug_duplicate_id <- "DQC_00_1DG_01"

# Day 0 quality check IDs
##########################
qc_nonvalid_fid1 <- "DQC_00_2ED_01a"
qc_nonvalid_fid2 <- "DQC_00_2ED_01b"
qc_duplicate_id1 <- "DQC_00_2ED_02a"
qc_duplicate_id2 <- "DQC_00_2ED_02b"
qc_incorrect_enrolment_date <- "DQC_00_2ED_03"
qc_multiple_enrolment_id <- "DQC_00_2ED_04"
qc_multiple_enrolment_sex_discrepancy_id <- "DQC_00_2ED_05"
qc_missing_cp_id <- "DQC_00_2ED_06"
qc_missing_diagnosis_id <- "DQC_00_2ED_07"
qc_missing_referral_id <- "DQC_00_2ED_08"
qc_missing_treatment_id <- "DQC_00_2ED_09"
qc_negative_nb_days_id <- "DQC_00_2ED_10"
qc_free_text_rx_id <- "DQC_00_2ED_11"
qc_pox_ <- "DQC_00_2ED_12"
qc_summary_id <- "DQC_00_2ED_13"

# Day 7 quality check IDs
##########################
qc_nontimely_submission_day7fu <- "DQC_07_01"
qc_nontimely_completion_day7fu <- "DQC_07_02"
qc_pids_out_lock_range_day7fu <- "DQC_07_03"
qc_nonvalid_day7fu <- "DQC_07_04"
qc_nonconsistent_name_day7fu <- "DQC_07_05"
qc_duplicated_day7fu <- "DQC_07_06"
qc_missing_hospit_date_day7fu <- "DQC_07_07"
qc_hospit_before_enrolment_day7fu <- "DQC_07_08"
qc_missing_death_date_day7fu <- "DQC_07_09"
qc_death_before_enrolment_day7fu <- "DQC_07_10"
qc_death_before_hospit_day7fu <- "DQC_07_11"

# Hospitalisation quality check IDs
####################################
qc_pids_out_lock_range_hospitfu <- "DQC_HS_01"
qc_nonvalid_hospitfu <- "DQC_HS_02"
qc_duplicated_hospitfu <- "DQC_HS_03"
qc_hospit_before_enrolment <- "DQC_HS_04"

# Day 28 quality check IDs
###########################
qc_nontimely_submission_day28fu <- "DQC_28_01"
qc_nontimely_completion_day28fu <- "DQC_28_02"
qc_pids_out_lock_range_day28fu <- "DQC_28_03"
qc_nonvalid_day28fu <- "DQC_28_04"
qc_nonconsistent_name_day28fu <- "DQC_28_05"
qc_duplicated_day28fu <- "DQC_28_06"
qc_missing_hospit_date_day28fu <- "DQC_28_07"
qc_hospit_before_enrolment_day28fu <- "DQC_28_08"
qc_missing_death_date_day28fu <- "DQC_28_09"
qc_death_before_enrolment_day28fu <- "DQC_28_10"

# Withdrawals quality check IDs
################################
qc_nonreconciled_withdrawals_id <- "DQC_WD_01"
qc_withdrawal_before_enrolment <- "DQC_WD_02"

# SPA quality check IDs
########################
qc_spa_sco_nonvalid_ids <- "DQC_SP_01"
qc_spa_sco_duplicates <- "DQC_SP_02"
qc_spa_sco_incomplete <- "DQC_SP_03"
qc_spa_hcpi_nonvalid_ids <- "DQC_SP_04"
qc_spa_hcpi_duplicates <- "DQC_SP_05"
```

```{r}
action_alert_no_modification <- "Alert to the study team. No modification of the database."

if (is_india) {
  hospit_value <- 13
} else{
  hospit_value <- 1
}
```

```{r}
#################
# Plot settings #
#################
tsize <- 7
tfont <- "Cambria"
dbreak_duration <- "4 months"
nfacetperrow <- 4
time_break_str <- "4 hours"
time_format <- "%H:%M"
y_min <- NA
y_max <- NA
```

\newpage

# Abbreviations & Definitions

## Abbreviations

| Abbreviation | Meaning                                                    |
|-------------------|-----------------------------------------------------|
| .CSV         | Comma-Separated Value                                      |
| DB           | DataBase                                                   |
| LS           | Longitudinal Observational Study                           |
| ODK          | Open Data Toolkit                                          |
| RCT          | Randomised Controlled Trial                                |
| SPA          | Service Provision Assessment                               |
| TIMCI        | Tools for the Integrated Management of Childhood Illnesses |

: List of abbreviations

## Definitions

-   **Example**: Definition

\newpage

# Introduction and aim

This document describes the data review processes and outputs for the Tools for Integrated Management of Childhood Illness (TIMCI) project.

Data cleaning and coding activities include data de-identification, duplicate management and free text management.

-   Mandatory checks
-   Compliance checks
-   Reasonability checks
-   Context checks
-   Logic checks
-   Expert knowledge checks

Note that the data collection tools contain a list of in-built range and consistency checks to prevent errors during data manipulation.

## Roles and responsibilities

Procedures for cleaning and coding quantitative data are developed by the lead data manager at Swiss TPH to ensure consistency across countries.

Data cleaning and coding activities are supervised by the in-country data manager in charge in each country, with possible country-specific additions.

## Frequency

Data quality checks will be run on a daily basis.

At critical junctures of the pragmatic cluster RCT, the research database will be reviewed and cleaned per established procedures, before being locked.

Consistency between the data cleaning procedures in each country will be regularly reviewed.

## Distribution

Each updated version is to be circulated to by the data management team to the research team in each TIMCI country.

\newpage

# `r if (is_rct) {'Pragmatic cluster Randomised Controlled Trial (RCT)'} else {'Longitudinal Observational Study (LS)'}`

```{r db-export-context-subsection, child = 'database_export_sub_rctls_context.Rmd'}
```

\newpage

```{r db-export-screening-subsection, child = 'database_export_sub_rctls_screening.Rmd'}
```

```{r db-export-day0-drug-subsection, child = if(is_ls) 'database_export_sub_rctls_day0_drug.Rmd'}
```

\newpage

```{r db-export-day0-subsection, child = 'database_export_sub_rctls_day0.Rmd'}
```

\newpage

```{r db-export-withdrawals-subsection, child = if(day0_is_not_empty) 'database_export_sub_rctls_withdrawals.Rmd'}
```

\newpage

```{r db-export-repeats-subsection, child = 'database_export_sub_rctls_repeats.Rmd'}
```

\newpage

```{r}
day7fu_is_not_null <- !is.null(raw_day7fu_data)
day7fu_is_not_empty <- timci::is_not_empty(raw_day7fu_data)
```

```{r db-export-day7fu-subsection, child = if(day7fu_is_not_empty) 'database_export_sub_rctls_day7.Rmd'}
```

\newpage

```{r db-export-successfulday7fu-subsection, child = if(day7fu_is_not_empty) 'database_export_sub_rctls_day7_outcome.Rmd'}
```

\newpage

```{r}
hospitfu_is_not_null <- !is.null(raw_hospit_data)
hospitfu_is_not_empty <- timci::is_not_empty(raw_hospit_data)
```

```{r db-export-hospit-subsection, child = if(hospitfu_is_not_empty) 'database_export_sub_rctls_hospit.Rmd'}
```

```{r}
day28fu_is_not_null <- !is.null(raw_day28fu_data)
day28fu_is_not_empty <- timci::is_not_empty(raw_day28fu_data)
```

```{r db-export-day28fu-subsection, child = if (is_rct & day28fu_is_not_empty) 'database_export_sub_rctls_day28.Rmd'}
```

```{r db-export-successfulday28fu-subsection, child = if(is_rct & day28fu_is_not_empty) 'database_export_sub_rctls_day28_outcome.Rmd'}
```

```{r db-export-deaths-subsection, child = if (day7fu_is_not_empty) 'database_export_sub_rctls_deaths.Rmd'}
```

\newpage

# Service Provision Assessment (SPA)

## Cross-sectional quantitative studies

```{r}
end_date <- NULL
facility_data_is_not_null <- !is.null(facility_data)
facility_data_is_not_empty <- timci::is_not_empty(facility_data)

tf_cond <- timci::is_not_empty(tf_data)
pm_cond <- FALSE# timci::is_not_empty(pm_data)
```

```{r, results='asis'}
spa_start_date <- NULL
if (!is.null(spa_sco_data)) {
  if (nrow(spa_sco_data) > 0) {
    spa_start_date <- min(spa_sco_data$date)
    spa_week_nb <- ceiling(difftime(as.Date(spa_start_date), as.Date(start_date) - 1,units = "weeks"))
   if (is_senegal) {
      cat(paste0("* Début de la collecte SPA : **", spa_start_date, "**"))
    } else {
      cat(paste0("* SPA data collection start: **", spa_start_date, "**"))
    }
  }
}
```

-   First round: **`r spa_start_date`** to **`r Sys.getenv("TIMCI_SPA_Q1_END_DATE")`**
-   Second round: **`r Sys.getenv("TIMCI_SPA_Q1_END_DATE")`** to **`r Sys.getenv("TIMCI_SPA_Q2_END_DATE")`**
-   Third round: **`r Sys.getenv("TIMCI_SPA_Q2_END_DATE")`** to **`r Sys.getenv("TIMCI_SPA_Q3_END_DATE")`**

```{r, results='asis', eval=timci::is_not_empty(spa_sco_data), fig.asp=1}
timci::generate_calendar_heatmap2(spa_sco_data,
                                  date,
                                  legendtitle = "Calendar heatmap of SPA submissions")
```

```{r, results='asis', eval=tf_cond, fig.asp=1}
timci::generate_calendar_heatmap2(tf_data[[1]],
                                  date,
                                  legendtitle = "Calendar heatmap of time-flow submissions")
```

```{r db-export-spa-subsection, child = 'database_export_sub_spa.Rmd'}
```

\newpage

# Process mapping & Time-flow

```{r db-export-pmtf-subsection, child = 'database_export_sub_pmtf.Rmd'}
```

\newpage

# Cost & Cost-effectiveness

```{r db-export-cost-subsection, child = 'database_export_sub_cost.Rmd'}
```

\newpage

# Qualitative studies

```{r db-export-qual-subsection, child = 'database_export_sub_qual.Rmd'}
```

\newpage

# Technical information

```{r, results='asis'}
df_session <- devtools::session_info(include_base = TRUE)
```

```{r, results='asis'}
df_session_platform <- df_session$platform %>% 
  unlist(.) %>% 
  as.data.frame(.) %>% 
  tibble::rownames_to_column(.)
colnames(df_session_platform) <- c("Setting", "Value")
df_session_platform %>%
  knitr::kable()
```

```{r, results='asis', echo=FALSE}
df_session_packages <- df_session$packages[c("loadedversion", "date", "source")]
colnames(df_session_packages) <- c("Loaded version", "Date", "Source")
df_session_packages %>%
  knitr::kable()
```

```{r}
locked_day0_data <- day0_data
locked_allday7fu_data <- allday7fu_data
```

```{r, eval=is_rct}
locked_allday28fu_data <- allday28fu_data

# Save locked data to *.rda file to be reused in other rmarkdown documents if needed
save(locked_day0_data,
     locked_allday7fu_data,
     locked_allday28fu_data,
     locked_hospit_data,
     locked_spa_sco_data,
     locked_spa_hcpi_data,
     spa_cgei_data,
     spa_fa_data,
     file = "timci_locked_data.rda")
```

```{r, eval=is_ls}
# Save locked data to *.rda file to be reused in other rmarkdown documents if needed
save(locked_day0_data,
     locked_allday7fu_data,
     locked_hospit_data,
     locked_spa_sco_data,
     locked_spa_hcpi_data,
     spa_cgei_data,
     spa_fa_data,
     file = "timci_locked_data.rda")
```
