```{r}
write("Export service provision assessment (SPA) data and run corresponding quality checks", stderr())
```

## Facility assessment

### Data export

```{r facility-assessment-export}
spa_fa_export_name <- "01_timci_spa_facility_assessment_data"
if (!is.null(spa_fa_data)) {
  fn <- timci::export_df2csvxlsx(spa_fa_data,
                                 params$spa_dir,
                                 spa_fa_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Raw SPA facility assessment data are exported in ", spa_fa_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
```

## Caregiver exit interview

### Data export

```{r cg-exit-interview-export}
spa_cgei_export_name <- "03_timci_spa_exit_interview_data"
if (!is.null(spa_cgei_data)) {
  fn <- timci::export_df2csvxlsx(spa_cgei_data,
                                 params$spa_dir,
                                 spa_cgei_export_name)
}
```

```{r, results = 'asis'}
cat(paste0("* Raw SPA caregiver exit interview data are exported in ", spa_cgei_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
```

## Sick child observation data quality checks

```{r, results = 'asis'}
locked_spa_sco_data <- NULL
if (!is.null(spa_sco_data)) {
  locked_spa_sco_data <- spa_sco_data %>% dplyr::filter(date <= as.Date(lock_date, "%Y-%m-%d"))
  cat(paste0("There are ", nrow(locked_spa_sco_data), " records between ", spa_start_date, " and ", lock_date, " in the raw SPA sick child observation database."))
}
```

### Non-valid provider IDs

```{r, results='asis', eval=!is.null(spa_sco_data)}
out <- timci::correct_spa_sco_hcp_ids(locked_spa_sco_data)
locked_spa_sco_data <- out[[1]]
spa_sco_data_hcp_edits <- out[[2]]
knitr::kable(spa_sco_data_hcp_edits, caption = "Healthcare provider ID to be corrected")
```

### Non-valid participant IDs

Rule: keep only IDs of children who are enrolled in the locked Day 0 database.

```{r}
spa_sco_data_uids <- NULL
if (!is.null(spa_sco_data)) {
  # Extract entries of child IDs enrolled in the Day 0 database
  spa_sco_data_uids <- locked_spa_sco_data[!locked_spa_sco_data$'child_identification-pid' %in% locked_day0_data$child_id, ]
  locked_spa_sco_data <- locked_spa_sco_data[locked_spa_sco_data$'child_identification-pid' %in% locked_day0_data$child_id, ]
  
  spa_sco_data_uids$'child_identification-pid' %>%
    knitr::kable(col.names = c("child_id"))
}
```

```{r, results='asis'}
if (!is.null(spa_sco_data_uids)) {
  n <- nrow(spa_sco_data_uids)
  if (n > 1) {
    cat(paste0(n, " records with non-valid participant IDs were detected and removed in the locked SPA sick child observation database."))
  } else if (n == 1) {
    cat(paste0(n, " record with non-valid participant IDs was detected and removed in the locked SPA sick child observation database."))
  } else{
    cat("No records with non-valid participant IDs were detected.")
  }
}
```

### Duplicate management

```{r, results='asis'}
cat("Rule: keep duplicated records and investigate the reason for having duplicates")
```

```{r, results='asis'}
if (!is.null(spa_sco_data)) {
  if (length(spa_sco_data) > 0) {
    spa_sco_data_qc <- timci::detect_id_duplicates(locked_spa_sco_data %>% dplyr::rename(child_id = 'child_identification-pid'))
    spa_sco_data_duplicates <- spa_sco_data_qc[spa_sco_data_qc$id_fq > 1,]
    if (length(spa_sco_data_duplicates) > 0) {
      if (nrow(spa_sco_data_duplicates) > 0) {
         knitr::kable(spa_sco_data_duplicates, caption = "ID duplicates")
      }
    } else {
      cat("No ID duplicates detected")
    }
  }
}
```

```{r, results='asis'}
if (!is.null(spa_sco_data)) {
  if (length(spa_sco_data_duplicates) > 0) { 
    cat(paste0(nrow(spa_sco_data_duplicates), " duplicated IDs were detected. No action was taken in the locked SPA sick child observation database."))
  } else {
    cat(paste0("No duplicated IDs were detected. No action was taken in the locked SPA sick child observation database."))
  }
}
```

### Data cleaning summary

```{r, results = 'asis'}
if (!is.null(spa_sco_data)) {
  cat(paste0("There are ", nrow(locked_spa_sco_data), " records in the locked SPA sick child observation database."))
}
```

### Data export

```{r sick-child-observation-export}
spa_sco_export_name <- "04_timci_spa_consultation_obs_data"
if (!is.null(spa_sco_data)) {
  if (deidentification_on == 1) {
    deidentified_spa_sco_data <- timci::deidentify_spa_data(spa_sco_data)
    fn <- timci::export_df2csvxlsx(deidentified_spa_sco_data,
                                   params$spa_dir,
                                   spa_sco_export_name)
    fn <- timci::export_df2csvxlsx(locked_spa_sco_data,
                                   locked_db_dir,
                                   spa_sco_export_name)
    
    fn <- timci::export_df2csvxlsx(spa_sco_data_uids,
                                   qc_dir,
                                   "04_timci_spa_consultation_obs_data_unknown_ids")
  } else {
    fn <- timci::export_df2csvxlsx(spa_sco_data,
                                   params$spa_dir,
                                   spa_sco_export_name)
    fn <- timci::export_df2csvxlsx(locked_spa_sco_data,
                                   locked_db_dir,
                                   spa_sco_export_name)
    fn <- timci::export_df2csvxlsx(spa_sco_data_uids,
                                   qc_dir,
                                   "04_timci_spa_consultation_obs_data_unknown_ids")
  }
  
}
```

```{r, results = 'asis'}
cat(paste0("* Raw SPA sick child observation data are exported in ", spa_sco_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
```

```{r, results = 'asis'}
cat(paste0("* Locked SPA sick child observation data are exported in ", spa_sco_export_name, ".csv/xslx in the ", locked_db_dir, " folder"))
```

## Healthcare provider interview data quality checks

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  spa_hcpi_data <- process_spa_hcpi_data(spa_hcpi_data)
  cat(paste0("There are ", nrow(spa_hcpi_data), " records in the raw SPA healthcare provider interview database."))
}
```

### Non-valid participant IDs

Rule: keep only IDs of healthcare providers who are observed in the locked SPA sick child observation database.

```{r}
# Extract entries of child IDs enrolled in the Day 0 database
if (!is.null(spa_hcpi_data)) {
  spa_hcpi_data_uids <- spa_hcpi_data[!spa_hcpi_data$hcp_id %in% locked_spa_sco_data$'hcp_identification-hcpid', ]
  locked_spa_hcpi_data <- spa_hcpi_data[spa_hcpi_data$hcp_id %in% locked_spa_sco_data$'hcp_identification-hcpid', ]
  
  spa_hcpi_data_uids$hcp_id %>% knitr::kable(col.names = c("hcp_id"))
}
```

```{r, results='asis'}
if (!is.null(spa_hcpi_data)) {
  n <- nrow(spa_hcpi_data_uids)
  if (n > 1) {
    cat(paste0(n, " records with non-valid participant IDs were detected and removed in the locked SPA healthcare provider interview database."))
  } else if (n == 1) {
    cat(paste0(n, " record with non-valid participant IDs was detected and removed in the locked SPA healthcare provider interview database."))
  } else{
    cat("No records with non-valid participant IDs were detected.")
  }
}
```

### Duplicate management

```{r, results='asis'}
cat("Rule: keep duplicated records and investigate the reason for duplicates")
```

```{r check-SPA-hcp-interview-data, results='asis'}
if (!is.null(spa_hcpi_data)) {
  if (length(spa_hcpi_data) > 0) { 
    spa_hcpi_data_qc <- timci::detect_id_duplicates(locked_spa_hcpi_data, hcp_id)
    spa_hcpi_data_duplicates <- spa_hcpi_data_qc[spa_hcpi_data_qc$id_fq > 1,]
    if (length(spa_hcpi_data_duplicates) > 0) {
      if (nrow(spa_hcpi_data_duplicates) > 0) {
        knitr::kable(spa_hcpi_data_duplicates, caption = "ID duplicates")
      }
    } else {
      cat("No ID duplicates detected")
    }
  }
}
```

```{r, results='asis'}
if (!is.null(spa_hcpi_data)) {
  if (length(spa_hcpi_data_duplicates) > 0) { 
    cat(paste0(nrow(spa_hcpi_data_duplicates), " duplicated IDs were detected. No action was taken in the locked SPA healthcare provider interview database."))
  } else {
    cat(paste0("No duplicated IDs were detected. No action was taken in the locked SPA healthcare provider interview database."))
  }
}
```

### Data cleaning summary

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  cat(paste0("There are ", nrow(locked_spa_hcpi_data), " records in the locked SPA healthcare provider interview database."))
}
```

### Data export

```{r hcp-interview-export}
spa_hcpi_export_name <- "02_timci_spa_provider_interview_data"
if (!is.null(spa_hcpi_data)) {
  fn <- timci::export_df2csvxlsx(spa_hcpi_data,
                                 params$spa_dir,
                                 spa_hcpi_export_name)
  
  fn <- timci::export_df2csvxlsx(locked_spa_hcpi_data,
                                 locked_db_dir,
                                 spa_hcpi_export_name)
}
```

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  cat(paste0("* Raw SPA healthcare provider interview data are exported in ", spa_hcpi_export_name, ".csv/xslx in the ", params$spa_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(spa_hcpi_data)) {
  cat(paste0("* Locked SPA healthcare provider interview data are exported in ", spa_hcpi_export_name, ".csv/xslx in the ", locked_db_dir, " folder"))
}
```
