```{r}
write("Export SPA healthcare provider interview data and run corresponding quality checks", stderr())
```

```{r}
spa_hcpi_data <- process_spa_hcpi_data(spa_hcpi_data)
n_raw_spa_hcpi_data <- nrow(spa_hcpi_data)
spa_hcpi_db_name <- "SPA healthcare provider interview"
```

There are **`r n_raw_spa_hcpi_data`** records in the raw `r spa_hcpi_db_name` database.

### Non-valid participant IDs [compliance check `r qc_spa_hcpi_nonvalid_hcpid`]\n\n

```{r, eval=!is.null(spa_hcpi_data), results='asis'}
qc_description <- ""
qc_rule <- "Keep only records for which the healthcare provider ID (X-Fxxx-Hxx) has been found in the locked SPA sick child observation database."
qc_type <- "nonvalid_ids"
df <- spa_hcpi_data
idcol1 <- "hcp_id"
refdf <- locked_spa_sco_data
idcol2 <- "hcp_identification-hcpid"
qc_text <- "healthcare provider ID not valid"
db_name <- spa_hcpi_db_name
qc_idx <- qc_spa_hcpi_nonvalid_hcpid
qc_export_label <- "nonvalid_hcpid"
qc_export_description <- "non-valid participant ID"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
locked_spa_hcpi_data <- cleaned_df
```

### Duplicate management

**Rule:** keep duplicated records and investigate the reason for duplicates.

```{r check-SPA-hcp-interview-data, results='asis'}
spa_hcpi_data_qc <- timci::detect_id_duplicates(locked_spa_hcpi_data, hcp_id)
spa_hcpi_data_duplicates <- spa_hcpi_data_qc[spa_hcpi_data_qc$id_fq > 1,]
if (timci::is_not_empty(spa_hcpi_data_duplicates)) {
  spa_hcpi_data_duplicates %>%
    knitr::kable(caption = "ID duplicates")
} else {
  cat("No ID duplicates detected")
}
```

```{r, results='asis', eval=(length(spa_hcpi_data_duplicates) > 0)}
cat(paste0(nrow(spa_hcpi_data_duplicates), " duplicated IDs detected. No action was taken in the locked SPA healthcare provider interview database."))
```

```{r, results='asis', eval=(length(spa_hcpi_data_duplicates) == 0)}
cat(paste0("No duplicated IDs were detected. No action was taken in the locked SPA healthcare provider interview database."))
```

```{r}
n_locked_spa_hcpi_data <- nrow(locked_spa_hcpi_data)
```

### Data cleaning summary

There are **`r n_locked_spa_hcpi_data`** records in the locked SPA healthcare provider interview database.

### Data export

```{r hcp-interview-export-raw-data, results='asis'}
timci::dataset_export(spa_hcpi_data,
                      "02",
                      "timci_spa_provider_interview_data",
                      params$spa_dir,
                      "Raw SPA healthcare provider interview data")
```

```{r hcp-interview-export-cleaned-data, results='asis'}
timci::dataset_export(locked_spa_hcpi_data,
                      "02",
                      "timci_spa_provider_interview_data",
                      locked_db_dir,
                      "Cleaned SPA healthcare provider interview data")
```
