## Screening data quality checks

```{r}
write("Export screening data and run corresponding quality checks", stderr())
```

```{r}
db_name <- "screening"

# Screening data
raw_screening_data <- timci::extract_screening_data(facility_data, is_pilot)

n_raw_screening_records <- nrow(raw_screening_data)

# Split into PII and deidentified raw data
out <- timci::extract_enrolled_participants(facility_data, is_pilot)
raw_day0_data <- out[[1]]
raw_pii <- out[[2]]
```

Initially, there are **`r n_raw_screening_records`** record(s) in the raw `r db_name` database from the start of the study on **`r start_date`**.

### Non-valid device IDs [Context check `r qc_screening_w_nonvalid_deviceid`]

```{r}
write(" o Non-valid device IDs", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Devices different from the ones whose IDs are listed in Section 2.3 of this report are considered as *non-valid* and may have been used for instance for training purposes. Records submitted by non-valid devices should not be considered as part of the main database."
qc_rule <- "Records submitted by devices different from the ones listed in Section 2.3 of this report are deleted."
qc_type <- "nonvalid_deviceids"
df <- facility_data
qc_text <- "non-valid device IDs"
qc_idx <- qc_screening_w_nonvalid_deviceid
qc_export_label <- "nonvalid_deviceids"
qc_export_description <- "the device ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_nonvalid_deviceid_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Inconsistent finalisation and submission dates [Context check `r qc_nontimely_submission_id`]

```{r}
write(" o Non-timely submission", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day). A delay superior to 12 days mean that the participant has never appeared in the Day 7 follow-up log on the tablet."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- facility_data
col_date1 <- "end"
col_date2 <- "submission_date"
cleaning <- "none"
qc_text <- "an actual transfer date later than the finalisation date"
qc_idx <- qc_nontimely_submission_id
qc_export_label <- "nontimely_day0_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
qc_df <- qc_df %>% 
  dplyr::mutate(Status = ifelse(is.na(fid), "Not enrolled", "Enrolled")) %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(end), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = ifelse(diff < 3,
                                    "Less than 3 days", ifelse(diff < 7,
                                                       "3-7 days",
                                                       "Above 7 days")))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df), fig.asp=1, fig.cap="Submissions not transferred on the same day they were finalised"}
ggplot2::ggplot(qc_df, ggplot2::aes(x = week, fill = Status)) +
  ggplot2::geom_bar() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::facet_wrap(~ fid_from_device, ncol = nfacetperrow) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank())
```

```{r, results='asis', eval=timci::is_not_empty(qc_df), fig.asp=1, fig.cap="Submissions not transferred on the same day they were finalised"}
ggplot2::ggplot(qc_df, ggplot2::aes(x = week, fill = Difference)) +
  ggplot2::geom_bar() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::facet_wrap(~ fid_from_device, ncol = nfacetperrow) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank())
```

### Non-timely completion [Context check `r qc_nontimely_completion_id`]

```{r}
write(" o Non-timely completion", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- facility_data
col_date1 <- "start"
col_date2 <- "end"
cleaning <- "none"
qc_text <- "an actual finalisation date later than the start date"
qc_idx <- qc_nontimely_completion_id
qc_export_label <- "nontimely_day0_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
qc_df <- qc_df %>% 
  dplyr::mutate(Status = ifelse(is.na(fid), "Not enrolled", "Enrolled")) %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = ifelse(diff < 1,
                                    "Less than 1 day", ifelse(diff < 3,
                                                       "1-3 days",
                                                       "Above 3 days")))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df), fig.asp=1, fig.cap="Number of submissions not finalised on the same day they were started"}
ggplot2::ggplot(qc_df, ggplot2::aes(x = week, fill = Status)) +
  ggplot2::geom_bar() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::facet_wrap(~ fid_from_device, ncol = nfacetperrow) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank())
```

```{r, results='asis', eval=timci::is_not_empty(qc_df), fig.asp=1, fig.cap="Number of submissions not finalised on the same day they were started"}
ggplot2::ggplot(qc_df, ggplot2::aes(x = week, fill = Difference)) +
  ggplot2::geom_bar() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::facet_wrap(~ fid_from_device, ncol = nfacetperrow) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank())
```

### Facility IDs from other TIMCI studies [context check `r qc_screening_other_fids`]

```{r}
write(" o Facility IDs from other facilities (India only)", stderr())
```

`r if ( !is_india ) { paste0('This check is only implemented for India.') }`

```{r}
qc_df <- NULL
n_other_fid_records <- 0
cleaned_df <- NULL
```

```{r, eval=facility_data_is_not_null&is_india, results='asis'}
qc_description <- "Records submitted by facilities which are part of a different TIMCI study and stored in the same ODK Central project should not be considered as part of the main database."
qc_rule <- "Records submitted by non-study facilities listed in Section 2.3 of this report are deleted."
qc_type <- "other_study_fids"
df <- facility_data
qc_text <- "facility IDs corresponding to another TIMCI study"
qc_idx <- qc_screening_other_fids
qc_export_label <- "screening_other_fids"
qc_export_description <- "the facility ID correspond to another TIMCI study"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_other_fid_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Caregiver eligibility [compliance check `r qc_underaged_cg_id`]

```{r}
write(" o Caregiver eligibility", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Caregivers must be above 18 years old to be able provide consent for the child to be part in the study."
qc_rule <- "Children with a caregiver below 18 years old are kept in the screening database but excluded from the study."
qc_type <- "underaged_cg"
df <- facility_data
qc_text <- "a consenting caregiver below 18 years old"
qc_idx <- qc_underaged_cg_id
qc_export_label <- "underaged_cg"
qc_export_description <- "the consenting caregiver is below 18 years old"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_ineligible_cg_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Repeat visits incorrectly recorded as new enrolments [compliance check `r qc_dup_repeats_id1`]

```{r}
write(" o Repeat visits incorrectly recorded as new enrolments", stderr())
```

`r if ( is_tanzania ) { paste0('#### Initial check [compliance check ', qc_dup_repeats_id1, ']') }`

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Participants who come back within 28 days after their enrolment should be recorded as repeat visits. If they are recorded as new enrolments with their participant ID, this creates duplicates in the database."
qc_rule <- "Repeat visits incorrectly recorded as new enrolments are detected and corrected proactively were possible."
qc_type <- "duplicates_check_pii"
df <- facility_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_dup_repeats_id1
qc_export_label <- "timci_repeat_visit_duplicates"
qc_export_description <- "the repeat visit was allocated the same ID that has been used for another participant in the database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

`r if ( is_tanzania ) { '#### Manual correction of repeat visits recorded as duplicated IDs' }`

`r if ( is_tanzania ) { paste0('Confirmed repeat records are manually edited in the ', db_name, ' database as described below:* variable *repeat_consult* set to 1* variable *consent* set to NA* variable *enrolled* set to NA') }`

```{r}
repeat_visit_edits_is_not_empty <- FALSE
edited_records_status_update <- ""
n_repeat_edit_records <- 0
```

```{r, eval=is_tanzania}
out <- timci::edit_day0_to_repeat(facility_data)
facility_data <- out[[1]]
repeat_visit_edits <- out[[2]]
repeat_visit_edits_is_not_empty <- timci::is_not_empty(repeat_visit_edits)
n_repeat_edit_records <- nrow(repeat_visit_edits)
```

```{r, eval=repeat_visit_edits_is_not_empty}
edited_records_status_update <- paste0('After correction of the **', n_repeat_edit_records, '**  record(s) detected by this check, there are still **', nrow(facility_data), '** record(s) in the ', db_name, ' database.')
```

`r edited_records_status_update`

```{r, eval=repeat_visit_edits_is_not_empty, results='asis'}
repeat_visit_edits %>%
  select(old_child_id, uuid) %>%
  knitr::kable()
```

`r if ( is_tanzania ) { paste0('#### Final check after manual edits [compliance check ', qc_dup_repeats_id2, ']') }`

```{r, eval=facility_data_is_not_null&is_tanzania, results='asis'}
qc_description <- "Remaining repeat visits incorrectly recorded as new enrolments are deleted from the database." 
qc_rule <- action_alert_no_modification
qc_type <- "duplicates_check_pii"
df <- facility_data
col_id <- "child_id"
col_date <- "start"
cleaning <- "none"
qc_text <- "duplicated IDs"
qc_idx <- qc_dup_repeats_id2
qc_export_label <- "timci_repeat_visit_duplicates"
qc_export_description <- "the repeat visit was allocated the same ID that has been used for another participant in the databse"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Incorrect date and time setup on the device [context check `r qc_incorrect_date_setup`]

```{r}
write(" o Incorrect data and time setup on the device", stderr())
```

```{r}
qc_df <- NULL
n_incorrect_date_setup_records <- 0
cleaned_df <- NULL
```

```{r, results='asis'}
qc_description <- "The enrolment date is defined as the creation (start) date of the form. However if for any reason the date is not setup correctly on the tablet, the enrolment date is not correct and follow-up is not triggered on the right date."
qc_rule <- "If the submission date is anterior to the creation date in the database, the (incorrect) creation date is replaced by the submission date."
qc_type <- "date_discrepancy"
df <- facility_data
col_date1 <- "submission_date"
col_date2 <- "start"
cleaning <- "replace_by_start_date"
qc_text <- "an incorrect date setup on the tablet"
qc_idx <- qc_incorrect_date_setup
qc_export_label <- "incorrect_date_setup"
qc_export_description <- "the date setup is not correct"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_incorrect_date_setup_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

```{r}
qc_df <- qc_df %>% 
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1))))
```

```{r, results='asis', eval=timci::is_not_empty(qc_df), fig.asp=1}
ggplot2::ggplot(qc_df, ggplot2::aes(x = week)) +
  ggplot2::geom_bar() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::facet_wrap(~ fid_from_device,
                      ncol = nfacetperrow,
                      drop = FALSE) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank())
```

### Lock date [context check `r qc_screening_after_lockdate`]

```{r}
write(" o Lock date context", stderr())
```

```{r, eval=facility_data_is_not_null, results='asis'}
qc_description <- "Screening data are considered valid only until the date for the lock. Note that follow-up data will be managed differently, since they are considered valid after the lock data as soon as they correspond to a participant enrolled before the date of the lock."
qc_rule <- paste0("Records entered after the lock date on ", lock_date, " are removed in the locked database.")
qc_type <- "posterior_to_lockdate"
df <- facility_data
qc_text <- paste0("an entry date posterior to the lock date on **", lock_date, "**")
qc_idx <- qc_screening_after_lockdate
qc_export_label <- "posterior_to_lockdate"
qc_export_description <- "the device ID is not valid"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
facility_data_after_lock <- qc_df
n_after_lockdate_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
facility_data <- cleaned_df
```

### Hour and time of entry

```{r, results='asis', fig.asp=1}
ggplot2::ggplot(facility_data %>%
                  dplyr::mutate(start_time1 = as.POSIXct(paste0("2022-09-23 ", df$start_time), tz = Sys.getenv("TZ"))) %>% 
                  dplyr::mutate(week = lubridate::floor_date(as.Date(end),
                                                             "week",
                                                             week_start = getOption("lubridate.week.start", 1))),
                ggplot2::aes(x = week, y = start_time1)) +
  ggplot2::geom_point() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::scale_y_datetime(date_labels = "%H:%M",
                            date_breaks = "4 hours") +
  ggplot2::facet_wrap(~ fid_from_device,
                      ncol = nfacetperrow) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank())
```

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
screening_data <- timci::extract_screening_data(facility_data,
                                                is_pilot)
n_cleaned_screening_records <- nrow(screening_data)
```

```{r}
timci::create_screening_qc_flowchart(n_raw_screening_records,
                                     n_nonvalid_deviceid_records,
                                     n_other_fid_records,
                                     n_after_lockdate_records,
                                     n_ineligible_cg_records,
                                     n_repeat_edit_records,
                                     n_incorrect_date_setup_records,
                                     n_cleaned_screening_records)
```

### Data export

```{r}
write(" o Data export", stderr())
```

```{r export-screening-data, results = 'asis'}
timci::dataset_export(raw_screening_data,
                      "01",
                      "timci_screening_data",
                      rctls_dir,
                      "Raw screening data")
```

```{r export-locked-screening-data, results = 'asis'}
timci::dataset_export(screening_data,
                      "01",
                      "timci_screening_data",
                      locked_db_dir,
                      "Cleaned screening data")
```

```{r, results='asis', fig.asp=1}
ggplot2::ggplot(screening_data %>% 
                  dplyr::mutate(Status = ifelse(!is.na(repeat_consult) & repeat_consult == 1,
                                                "Previously enrolled",
                                                ifelse(!is.na(consent) & consent == 1,
                                                       "Newly enrolled",
                                                       "Not enrolled"))) %>%
                  dplyr::mutate(week = lubridate::floor_date(as.Date(submission_date),
                                                             "week",
                                                             week_start = getOption("lubridate.week.start", 1))),
                ggplot2::aes(x = week, fill = Status)) +
  ggplot2::geom_bar() +
  ggplot2::labs(x = "Weeks",
                y = "Number of records") +
  ggplot2::scale_x_date(date_breaks = dbreak_duration,
                        date_labels = "%b%y") +
  ggplot2::facet_wrap(~ fid_from_device, ncol = nfacetperrow) +
  ggplot2::theme(text = element_text(size = tsize),
                 panel.grid.major.x = element_blank(),
                 panel.grid.minor.x = element_blank()) 
```

```{r export-facility-audit, results = 'asis'}
timci::dataset_export(facility_data_audit,
                      "00",
                      "timci_facility_audit_data",
                      rctls_dir,
                      "Screening audit data")
```
