```{r}
write(timci::formats2h2("Review, process and export facility data"), stderr())
```

```{r}
write("Export Day 0 data and run corresponding quality checks", stderr())
```

## Day 0 data quality checks

```{r}
screening_data <- timci::extract_screening_data(facility_data)
n_screening <- nrow(facility_data)
res <- timci::extract_enrolled_participants(facility_data)
day0_data <- res[[1]]
n_day0 <- nrow(day0_data)
pii <- res[[2]]
```

```{r, results = 'asis'}
cat(paste0("Initially, there are **", n_screening, "** screening record(s) in the raw facility database from the start of the study on ", start_date, ", including **", n_day0, "** record(s) corresponding to new Day 0 enrolments."))
```

### Non-valid device IDs [context check]

**Rule:** records from devices different from the ones listed in the first section of this report are removed in the locked database. These *non-valid* devices were either used to collect training data or to collect data for another study than the one considered for this report.

```{r}
locked_screening_data <- timci::allocate_screening_facility(screening_data,
                                                            research_facilities)
n_locked_screening <- nrow(locked_screening_data)
```

```{r}
locked_day0_data <- timci::allocate_screening_facility(day0_data,
                                                       research_facilities)
n_locked_day0 <- nrow(locked_day0_data)
locked_pii <- timci::allocate_screening_facility(pii,
                                                 research_facilities)
```

```{r, results = 'asis'}
cat(paste0("**", n_screening - n_locked_screening, "** record(s) with non-valid device IDs detected and removed in the locked facility database, including **", n_day0 - n_locked_day0, "** Day 0 records."))
```

```{r}
# Replace Day 0 data by locked Day 0 data so that non-valid device IDs/facilities do not appear in the export
day0_data <- locked_day0_data
```

### Lock date [context check]

**Rule:** records entered after the lock date on `r lock_date` are removed in the locked database.

```{r}
locked_screening_data <- locked_screening_data %>%
  dplyr::filter(date_visit <= as.Date(lock_date, "%Y-%m-%d")) %>%
  dplyr::arrange(date_visit = as.Date(date_visit, "%Y-%m-%d")) # Order entries by date
locked_day0_data <- locked_day0_data %>%
  dplyr::filter(date_visit <= as.Date(lock_date, "%Y-%m-%d"))
locked_pii <- locked_pii %>%
  dplyr::filter(date_visit <= as.Date(lock_date, "%Y-%m-%d"))
```

```{r, results = 'asis'}
cat(paste0("**", n_locked_screening - nrow(locked_screening_data), "** record(s) with an entry date posterior to the lock date on **", lock_date, "** detected and removed in the locked facility database, including **", n_locked_day0 - nrow(locked_day0_data), "** Day 0 record(s)."))
```

### Non-valid enrolling facility IDs [compliance check]

```{r, results='asis', eval=(is_tanzania | is_kenya)}
cat("#### Initial check")
```

```{r, results='asis', eval=(is_tanzania | is_kenya)}
cat("**Rule:** records from facility IDs not listed in the first section of this report are detected and corrected proactively where possible.")
```

```{r, results='asis'}
invalid_facilities <- locked_day0_data[!locked_day0_data$fid %in% research_facilities$facility_id, ]
```

```{r, results='asis'}
cat(paste0("**", nrow(invalid_facilities), "** record(s) with non-valid enrolling facility IDs detected and removed in the locked Day 0 database."))
```

```{r, results='asis'}
if (nrow(invalid_facilities) > 0) {
  invalid_facilities[c("child_id", "uuid")] %>%
    knitr::kable(row.names = FALSE)
}
```

```{r, results='asis'}
cat("#### Facility ID manual edits")
```

```{r, results='asis'}
out <- timci::correct_day0_non_valid_facilities(locked_day0_data)
locked_day0_data <- out[[1]]
facility_edits <- out[[2]]
if (!is.null(facility_edits)) {
  facility_edits %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

```{r, results='asis'}
invalid_facilities <- locked_day0_data[!locked_day0_data$fid %in% research_facilities$facility_id, ]
locked_day0_data <- locked_day0_data[locked_day0_data$fid %in% research_facilities$facility_id, ]
```

```{r, results='asis'}
if (nrow(invalid_facilities) > 0) {
  invalid_facilities[c("child_id", "uuid")] %>%
    knitr::kable(row.names = FALSE)
}
```

#### Second check after manual edits

**Rule:** records from facility IDs not listed in the first section of this report are removed in the locked database.

```{r, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == 'India') {
  cat("### Inconsistent facility information [Context check]\n\n")
  cat("**Rule**: records with inconsistent facility information are kept in the locked database, but will need to be checked more carefully (e.g: GPS data).\n\n")
}
```

```{r}
qc_inconsistent_facility <- NULL
if (Sys.getenv('TIMCI_COUNTRY') == 'India') {
  if (!is.null(locked_day0_data)) {
    if (nrow(locked_day0_data) > 0) {
      qc_inconsistent_facility <- locked_day0_data[locked_day0_data$fid != locked_day0_data$fid_ra, ]
      qc_inconsistent_facility <- qc_inconsistent_facility[c("child_id", "fid", "fid_ra", "uuid")]
    }
  }
}
```

```{r, results='asis'}
if (!is.null(qc_inconsistent_facility)) {
  if (nrow(qc_inconsistent_facility) > 0) {
    cat(paste0("**", nrow(qc_inconsistent_facility), "** record(s) with inconsistent facility information detected."))
  }
}
```

```{r, results='asis'}
if (!is.null(qc_inconsistent_facility)) {
  if (nrow(qc_inconsistent_facility) > 0) {
    qc_inconsistent_facility %>%
      knitr::kable(row.names = FALSE)
  }
}
```

### Non-valid enrolment [compliance check]

#### Caregiver eligibility

**Rule:** Participants with a caregiver below 18 years old are removed in the locked database.

```{r, results='asis'}
underaged_cg <- locked_day0_data[locked_day0_data$cg_eligibility == 0, ]
cat(paste0("**", nrow(underaged_cg), "** record(s) with a consenting caregiver below 18 years old detected and removed in the locked database."))
```

```{r, results='asis'}
if (nrow(underaged_cg) > 0) {
  underaged_cg[c('child_id', 'main_cg_lbl', 'cg_age_yr', 'cg_age_ctg')] %>%
    knitr::kable(row.names = FALSE)
}
```

```{r}
locked_day0_data <- locked_day0_data[locked_day0_data$cg_eligibility == 1, ]
```

### Submission timeliness [compliance checks]

#### Non-timely completion [compliance check]

```{r}
qc_completion_ab1day <- NULL
```

```{r, eval=!is.null(facility_data)}
if (nrow(locked_day0_data) > 0) {
  qc <- detect_non_timely_completion(locked_day0_data)
  qc_completion_ab1day <- qc[qc$diff > 0,]
}
```

**Definition:** Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)

```{r, results='asis', eval=!is.null(qc_completion_ab1day)}
cat(paste0("**", nrow(qc_completion_ab1day), "** participant(s) for whom the submission was not finalised on the same day it was started."))
```

```{r, results='asis', eval=!is.null(qc_completion_ab1day)}
qc_completion_fn <- "DQC_01_01_nontimely_day0_completion"
fn <- timci::export_df2xlsx(qc_completion_ab1day,
                            qc_dir,
                            qc_completion_fn)
cat(paste0("The table of participants for whom the submission was not finalised on the same day it was started is exported to **", qc_completion_fn, "**."))
```

```{r, results='asis', eval=!is.null(qc_completion_ab1day)}
if (nrow(qc_completion_ab1day) > 0) {
  hist(as.numeric(qc_completion_ab1day$diff),
       breaks = c(1:max(as.numeric(qc_completion_ab1day$diff), na.rm = TRUE)),
       xlab="Days between submission start and finalisation" ,
       ylab="Occurences",
       main="")
}
```

#### Non-timely submission [compliance check]

**Definition:** transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day). A delay superior to 12 days mean that the participant has never appeared in the Day 7 follow-up log on the tablet.

```{r}
qc_transfer_ab1day <- NULL
qc_transfer_ab7days <- NULL
qc_transfer_ab12days <- NULL

if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    qc_transfer <- detect_non_timely_submission(locked_day0_data)
    qc_transfer_ab1day <- qc_transfer[qc_transfer$diff > 0,]
    qc_transfer_ab7days <- qc_transfer[qc_transfer$diff > 6,]
    qc_transfer_ab12days <- qc_transfer[qc_transfer$diff > 11,]
  }
}
```

```{r, results='asis'}
if (!is.null(qc_transfer_ab1day)) {
  if (nrow(qc_transfer_ab1day) > 0) {
    cat(paste0("**", nrow(qc_transfer_ab1day), "** participant(s) for whom the submission was not transferred on the same day it was finalised."))
  }
}
```

```{r, results='asis'}
if (!is.null(qc_transfer_ab7days)) {
  if (nrow(qc_transfer_ab7days) > 0) {
    cat(paste0("**", nrow(qc_transfer_ab7days), "** participant(s) for whom the submission was transferred after 7 days and more."))
  }
}
```

```{r, results='asis'}
if (!is.null(qc_transfer_ab7days)) {
  if (nrow(qc_transfer_ab7days) > 0) {
    qc_transfer_ab7days %>%
      knitr::kable(row.names = FALSE)
  }
}
```

```{r, results='asis'}
if (!is.null(qc_transfer_ab12days)) {
  if (nrow(qc_transfer_ab12days) > 0) {
    cat(paste0("**", nrow(qc_transfer_ab12days), "** participants for which the submission was transferred after 12 days and more (participant never displayed in the Day 7 follow-up log on the tablet)."))
  }
}
```

```{r, results='asis'}
if (!is.null(qc_transfer_ab12days)) {
  if (nrow(qc_transfer_ab12days) > 0) {
    qc_transfer_ab12days %>%
      knitr::kable(row.names = FALSE)
  }
}
```

```{r, results='asis', eval=!is.null(qc_transfer_ab1day)}
qc_transfer_fn <- "DQC_01_01_nontimely_day0_transfer"
fn <- timci::export_df2xlsx(qc_transfer_ab1day,
                            qc_dir,
                            qc_transfer_fn)
cat(paste0("The table of participants for which the submission was transferred strictly after the day it was finalised is exported to **", qc_transfer_fn, "**."))
```

```{r, results='asis', eval=!is.null(qc_transfer_ab1day)}
if (nrow(qc_transfer_ab1day) > 0) {
  hist(as.numeric(qc_transfer_ab1day$diff),
       breaks = c(1:max(as.numeric(qc_transfer_ab1day$diff), na.rm = TRUE)),
       xlab="Days between submission start and finalisation" ,
       ylab="Occurences",
       main="")
}
```

### Duplicate management

```{r child_duplicate-subsection, child = 'database_export_QC_child_duplicates.Rmd'}
```

#### Possible participant duplicates

```{r, results='asis'}
cat("**Rule:** possible participant duplicates are detected based on their name, sex and date of birth. No specific action at the moment.")
```

```{r check-RCT-LS-ODK-facility-data-002, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    day0_qc1 <- timci::detect_participant_duplicates(locked_pii)
    day0_qc <- merge(day0_qc, day0_qc1, by = 'child_id')
    duplicates <- day0_qc[(day0_qc$ex_name_fq > 1) | (day0_qc$sw_name_fq > 1),]
    if (length(duplicates) > 0 & nrow(duplicates) > 0) { 
      duplicates %>% knitr::kable(row.names = FALSE)
    }
  }
}
```

```{r check-RCT-LS-ODK-facility-data-002-disp, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    if (length(duplicates) > 0 & nrow(duplicates) > 0) { 
      cat(paste0("", nrow(duplicates), " possible participant duplicates detected based on their name, sex and date of birth. No specific action was taken."))
    } else {
      cat("No duplicated names detected")
    }
  } else {
    cat("N/A")
  }
}
  
# Approximate String Matching (Fuzzy Matching)
#df <- dplyr::mutate(pii, full_name = tolower(paste(fs_name, ls_name, sep = ' ')))
#df3 <- df[c("child_id", "full_name")]
#qc3 <- lapply(list(df3$full_name), agrep, x = list(df3$full_name), value = TRUE)
#print(qc3)
```

#### Possible participant duplicates with sex discrepancy

```{r, results='asis'}
cat("**Rule:** possible participant duplicates detected based on their name and date of birth, but with a sex discrepancy. No specific action at the moment.")
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    day0_qc2 <- timci::detect_namedob_duplicates(locked_pii)
    day0_qc <- merge(day0_qc, day0_qc2, by = 'child_id')
    duplicates2 <- day0_qc[(day0_qc$ex_name2_fq > 1 & day0_qc$ex_name2_fq > day0_qc$ex_name_fq) | (day0_qc$sw_name2_fq > 1 & day0_qc$sw_name2_fq > day0_qc$sw_name_fq),]
    if (length(duplicates2) > 0 & nrow(duplicates2) > 0) { 
      duplicates2 %>% knitr::kable(row.names = FALSE)
    }
  }
}
```

```{r check-RCT-LS-ODK-facility-data-003-disp, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_pii) > 0) {
    if (length(duplicates2) > 0 & nrow(duplicates2) > 0) { 
      cat(paste0("", nrow(duplicates2), " possible participant duplicates detected based on their name and date of birth, but with sex discrepancy. No specific action was taken."))
    } else {
      cat("No possible participant duplicates detected based on their name and date of birth, but with sex discrepancy detected")
    }
  } else {
    cat("N/A")
  }
}
  
# Approximate String Matching (Fuzzy Matching)
#df <- dplyr::mutate(pii, full_name = tolower(paste(fs_name, ls_name, sep = ' ')))
#df3 <- df[c("child_id", "full_name")]
#qc3 <- lapply(list(df3$full_name), agrep, x = list(df3$full_name), value = TRUE)
#print(qc3)
```

```{r export-duplicates}
if (!is.null(day0_qc)) {
  fn <- timci::export_df2xlsx(day0_qc,
                              qc_dir,
                              "07_data_quality_checks")
}
```

### Withdrawal management

```{r, results='asis'}
cat("Rule: withdrawals with documented child IDs are kept in the locked Day 0 database, then removed in all the databases where entries are posterior to the date of withdrawal. If withdrawn IDs cannot be found in the locked Day 0 database, it is assumed that the caregiver withdrew during data collection. More information will be collected about this in the withdrawal form.")
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(raw_withdrawal_data)) {
      if (nrow(raw_withdrawal_data) > 0) { 
        raw_withdrawal_data$child_id <- ifelse(!is.na(raw_withdrawal_data$'page-a1_a_4'), raw_withdrawal_data$'page-a1_a_4', raw_withdrawal_data$'page-a1_a_4a')
        withdrawal_data2 <- raw_withdrawal_data[!is.na(raw_withdrawal_data$child_id), ]
        withdrawal_data2$child_id <- gsub("O", "0", withdrawal_data2$child_id)
        withdrawal_data2 %>%
          
          dplyr::select(c("child_id", "date")) %>%
          knitr::kable(col.names = c("Child ID", "Withdrawal date"))
      }
    }
  }
}
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(raw_withdrawal_data)) {
      if (nrow(raw_withdrawal_data) > 0) { 
        cat(paste0(nrow(raw_withdrawal_data), " withdrawal(s) reported (among which ", nrow(withdrawal_data2)," withdrawals with documented child IDs)."))
      } else {
        cat("No withdrawal reported.")
      }
    }
  } else {
    cat("N/A")
  }
}
```

```{r, results='asis'}
day0_data_id_withdrawal <- NULL
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(raw_withdrawal_data)) {
      if (nrow(raw_withdrawal_data) > 0) { 
        day0_data_id_withdrawal <- locked_day0_data[locked_day0_data$child_id %in% withdrawal_data2$child_id, ]
        day0_data_id_withdrawal <- day0_data_id_withdrawal %>%
          merge(withdrawal_data2, by = 'child_id', all.x = TRUE)
        if (nrow(day0_data_id_withdrawal) > 0) { 
          day0_data_id_withdrawal %>%
            dplyr::select(c("child_id", "date_visit", "date", "uuid")) %>%
            knitr::kable(col.names = c("Child ID", "Enrolment date", "Withdrawal date", "uuid"))
        }
      }
    }
  }
}
```

```{r, results='asis'}
if (!is.null(facility_data)) {
  if (nrow(locked_day0_data) > 0) {
    if (!is.null(day0_data_id_withdrawal)) {
      cat(paste0("**", nrow(day0_data_id_withdrawal), "** participant(s) who withdrew found in the locked Day 0 database."))
    }
  }
}
```

### Clinical presentation [Mandatory check]

**Description:** all participants should have complete information about their clinical presentation.

**Rule:** No action.

```{r}
qc_missing_cp <- timci::detect_missing_clinical_presentation(locked_day0_data)
```

```{r}
qc_missing_cp_is_not_null <- !is.null(qc_missing_cp)
qc_missing_cp_is_not_empty <- FALSE
if (qc_missing_cp_is_not_null) {
  qc_missing_cp_is_not_empty <- nrow(qc_missing_cp) > 0
}
```

```{r, results = 'asis', eval=qc_missing_cp_is_not_null}
timci::format_nrow("", qc_missing_cp, "record(s) with missing clinical presentation detected in the locked Day 0 database.")
```

```{r, results='asis', eval=qc_missing_cp_is_not_empty}
cols1 <- c("child_id", "fid", "date_visit", "uuid")
cols2 <- c("Child ID", "Enrolment date", "uuid")
qc_missing_cp %>%
  dplyr::select(cols1) %>%
  dplyr::arrange(fid) %>%
  knitr::kable(col.names = cols2,
               row.names = FALSE)
```

```{r, results='asis', eval=qc_missing_cp_is_not_empty}
qc_missing_cp_fn <- "DQC_01_03_missing_clinical_presentation"
fn <- timci::export_df2xlsx(qc_missing_cp,
                            qc_dir,
                            qc_missing_cp_fn)
cat(paste0("The table of participants for whom the clinical presentation is missing has been exported to **", qc_missing_cp_fn, "** (**", Sys.time(), "**)."))
```

### Diagnosis [Mandatory check]

**Description:** all participants should have complete information about their diagnosis for their Day 0 visit.

Check not implemented yet.

### Data cleaning summary

```{r, results = 'asis'}
timci::format_nrow("There are", locked_day0_data, "records in the locked Day 0 database.")
```

### Data export

```{r export-screening-data, results = 'asis'}
screening_export_name <- "01_timci_screening_data"
if (!is.null(facility_data)) { 
  fn <- timci::export_df2csvxlsx(screening_data,
                                 rctls_dir,
                                 screening_export_name)
}
cat(paste0("* Screening data are exported in ", screening_export_name, ".csv/xslx in the ", rctls_dir, " folder"))
```

```{r export-locked-screening-data, results = 'asis'}
if (!is.null(facility_data)) {
  fn <- timci::export_df2csvxlsx(locked_screening_data,
                                 locked_db_dir,
                                 screening_export_name)
}
cat(paste0("* Locked screening data are exported in ", screening_export_name, ".csv/xslx in the ", locked_db_dir, " folder"))
```

```{r export-facility-audit}
if (!is.null(facility_data_audit)) { 
  fn <- timci::export_df2csvxlsx(facility_data_audit,
                                 rctls_dir,
                                 "00_facility_audit_data")
}
```

```{r split-pii-from-research-data}
if (!is.null(facility_data)) {
  
  if (deidentification_on == 1) {
    deidentified_day0_data <- timci::deidentify_data(day0_data)
    fn <- timci::export_df2csvxlsx(deidentified_day0_data,
                                   rctls_dir,
                                   "02_timci_day0_data")
    
    locked_day0_data <- timci::deidentify_data(locked_day0_data)
    fn <- timci::export_df2csvxlsx(locked_day0_data,
                                   locked_db_dir,
                                   "02_timci_day0_data")
    
    if (!is.null(day0_data_id_duplicates)) {
      deidentified_day0_data_id_duplicates <- timci::deidentify_data(day0_data_id_duplicates)
      fn <- timci::export_df2csvxlsx(deidentified_day0_data_id_duplicates,
                                     qc_dir,
                                     "02a_timci_day0_data_id_duplicates")
    }
  } else {
    fn <- timci::export_df2csvxlsx(day0_data,
                                   rctls_dir,
                                   "02_timci_day0_data")
    
    fn <- timci::export_df2csvxlsx(locked_day0_data,
                                   locked_db_dir,
                                   "02_timci_day0_data")
    
    if (!is.null(day0_data_id_duplicates)) {
      fn <- timci::export_df2csvxlsx(day0_data_id_duplicates,
                                     qc_dir,
                                     "02a_timci_day0_data_id_duplicates")
    }
  }
  
  xlsx_fname <- timci::export_df2xlsx(pii, tempdir(),
                                      "timci_contact_data")
  pii_pwd <- Sys.getenv("TIMCI_PII_PW")
  zip(params$participant_zip, 
      files = xlsx_fname, 
      flags = paste("-r9Xj --password", pii_pwd))
}
```

```{r, results = 'asis'}
cat(paste0("* Raw Day 0 data are exported in ", "02_timci_day0_data", ".csv/xslx in the ", params$rctls_dir, " folder"))
```

```{r, results = 'asis'}
cat(paste0("* Locked Day 0 data are exported in ", "02_timci_day0_data", ".csv/xslx in the ", locked_db_dir, " folder"))
```

```{r export-visit-data, results = 'asis'}
facility_data_name <- "03_timci_facility_visits_data"
if (!is.null(facility_data)) {
  study_data <- timci::extract_all_visits(facility_data)
  
  if (deidentification_on == 1) {
    deidentified_facility_data <- timci::deidentify_data(study_data)
    fn <- timci::export_df2csvxlsx(deidentified_facility_data,
                                  params$rctls_dir,
                                  "03_timci_facility_visits_data")
  } else {
    fn <- timci::export_df2csvxlsx(study_data,
                                  params$rctls_dir,
                                  "03_timci_facility_visits_data")
  }
  #cat(paste0("* Raw facility visit data are exported in ", facility_data_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```
