```{r}
write("o Export drug re-entry data and run corresponding quality checks", stderr())
```

\newpage

## Drug free text re-entry data quality checks and cleaning

```{r}
db_name <- "Drug"
drug_is_not_null <- timci::is_not_empty(raw_drug_data)
n_raw_drug_records <- nrow(raw_drug_data)
```

There are **`r n_raw_drug_records`** record(s) in the raw `r db_name` database.

### Duplicated entries [Compliance check `r qc_duplicate_drug`]

```{r, results='asis', eval=drug_is_not_null}
qc_description <- "All participants should have a distinct ID. Duplicated IDs may generate errors for the conduct of follow-ups in the field and results in ambiguous outcomes for duplicated participants once the database is deidentified."
qc_rule <- "Remaining duplicated record IDs are deleted from the database."
qc_type <- "duplicates"
df <- raw_drug_data
col_id <- "uuid"
col_date <- "start"
cleaning <- "keep_latest"
qc_text <- "duplicated IDs"
qc_idx <- qc_duplicate_drug
qc_export_label <- "timci_drug_data_id_duplicates"
qc_export_description <- "the submission was done twice for the same record ID"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
n_dropped_duplicate_records <- n_detected
```

```{r, eval=!is.null(cleaned_df)}
drug_data <- cleaned_df
n_cleaned_drug_records <- nrow(drug_data)
```

### Amoxicillin entries [Expert knowledge checks `r qc_amox_consistency_drug`]

### Metronidazole entries [Expert knowledge checks `r qc_amox_consistency_drug`]

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r, fig.asp=1}
timci::create_drug_qc_flowchart(n_raw_drug_records,
                                n_dropped_duplicate_records,
                                n_cleaned_drug_records)
```

### Data overview

```{r}
write(" o Data overview", stderr())
```

```{r, results='asis'}
skimr::skim(drug_data)
```

### Data export

```{r}
write(" o Data export", stderr())
```

```{r, eval=drug_is_not_null, results = 'asis'}
timci::dataset_export(raw_drug_data,
                      "02z",
                      "timci_day0_drug_data",
                      rctls_dir,
                      "Raw Day 0 drug re-entry data")
```

```{r export-locked-drug-data, results = 'asis'}
timci::dataset_export(drug_data,
                      "02z",
                      "timci_day0_drug_data",
                      locked_db_dir,
                      "Cleaned Day 0 drug re-entry data")
```
