\newpage

## Day 28 data quality checks\n\n

```{r}
write("Export Day 28 data and run corresponding quality checks", stderr())
```

```{r}
db_name <- "Day 28 follow-up"
out <- timci::format_day28_data(raw_day28fu_data)
raw_allday28fu_data <- out[[3]]
n_raw_allday28fu_data_records <- nrow(raw_allday28fu_data)
raw_successday28fu_data <- out[[1]]

raw_day28_fu_is_not_empty <- timci::is_not_empty(raw_day28fu_data)
```

There are **`r n_raw_allday28fu_data_records`** records in the raw `r db_name` database.

### Non-consistent finalisation and submission dates [Context check `r qc_nontimely_submission_day28fu`]

```{r}
write(" o Inconsistent finalisation and submission", stderr())
```

```{r, eval=raw_allday28fu_is_not_empty, results='asis'}
qc_description <- "Transfer of a finalised submission to the ODK Central server not done on the day the submission was finalised (i.e. transfer time superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- raw_allday28fu_data
col_date1 <- "end"
col_date2 <- "submission_date"
cleaning <- "none"
qc_text <- "the submission was not transferred on the same day it was finalised"
qc_idx <- qc_nontimely_submission_day28fu
qc_export_label <- "nontimely_day28_submission"
qc_export_description <- "the submission was not transferred on the same day it was finalised"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
fig_caption <- "Submissions not transferred on the same day they were finalised"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>% 
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(end), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = ifelse(diff < 3,
                                    "Less than 3 days", ifelse(diff < 7,
                                                       "3-7 days",
                                                       "Above 7 days"))) %>%
  merge(research_facilities,
        by.x = 'fid',
        by.y = 'facility_id',
        all.x = TRUE)
cat(knitr::knit_child('database_export_sub_facet_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Non-timely completion [Context check `r qc_nontimely_completion_day7fu`]

```{r}
write(" o Non-timely completion", stderr())
```

```{r, eval=raw_allday28fu_is_not_empty, results='asis'}
qc_description <- "Finalisation of the submission not done on the same day the submission was started (i.e., duration from start to end strictly superior to 0 day)."
qc_rule <- action_alert_no_modification
qc_type <- "date_discrepancy"
df <- raw_allday28fu_data
col_date1 <- "start"
col_date2 <- "end"
cleaning <- "none"
qc_text <- "the submission was not finalised on the same day it was started"
qc_idx <- qc_nontimely_completion_day28fu
qc_export_label <- "nontimely_day28_completion"
qc_export_description <- "the submission was not finalised on the same day it was started"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r}
fig_caption <- "Number of submissions not finalised on the same day they were started"
facility_col <- "fid"
date_col <- "week"
date_lbl <- "Weeks"
date_format <- "%b%y"
comparison <- "area"
fill_col <- "Difference"
```

```{r, eval=timci::is_not_empty(qc_df), results='asis'}
fig_df <- qc_df %>%
  dplyr::mutate(week = as.Date(lubridate::floor_date(as.Date(start), "week", week_start = getOption("lubridate.week.start", 1)))) %>% 
  dplyr::mutate(Difference = ifelse(diff <= 1,
                                    "1 day", ifelse(diff < 3,
                                                       "2-3 days",
                                                       "Above 3 days"))) %>%
  merge(research_facilities,
        by.x = 'fid',
        by.y = 'facility_id',
        all.x = TRUE)
cat(knitr::knit_child('database_export_sub_facet_plot.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Follow-ups corresponding to participants enrolled outside the lock date range [context check `r qc_pids_out_lock_range_day28fu`]\n\n

```{r}
write(" o Follow-ups corresponding to participants enrolled outside the lock date range", stderr())
```

```{r, eval=!is.null(raw_allday28fu_data), results='asis'}
qc_description <- paste0("Day 28 follow-ups are relevant only if associated to participants enrolled between the start date ", start_date, " and the lock date on ", lock_date, ".")
qc_rule <- "Discard follow-up records of participants who are enrolled in the Day 0 database outside the date range considered for the lock."
qc_type <- "nonvalid_ids2"
df <- raw_allday28fu_data
idcol1 <- "child_id"
refdf <- facility_data_after_lock %>%
  filter( !is.na(child_id) )
idcol2 <- "child_id"
col_date <- "date_call"
qc_text <- "participant IDs outside the lock date range"
qc_idx <- qc_pids_out_lock_range_day28fu
qc_export_label <- "pids_outside_lock_range"
qc_export_description <- "the follow-up correspond to a child who has been enrolled outside the date range for the lock"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_afterlock_pids_day28fu_records <- n_detected
allday28fu_data <- cleaned_df
```

### Non-valid participant IDs [compliance check `r qc_nonvalid_day28fu`]\n\n

```{r}
write(" o Non-valid participant IDs", stderr())
```

```{r, eval=!is.null(allday28fu_data), results='asis'}
qc_description <- "Day 28 follow-ups are relevant only if they can be reconciled with a participant enrolled at Day 0. Reconciliation is based on the participant ID."
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_type <- "nonvalid_ids"
df <- allday28fu_data
idcol1 <- "child_id"
refdf <- day0_data
idcol2 <- "child_id"
qc_text <- "non-valid participant IDs"
qc_idx <- qc_nonvalid_day28fu
qc_export_label <- "nonvalid_pids_day28fu"
qc_export_description <- "the child ID does not correspond to any ID found the locked Day 0 database"
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

```{r, eval=!is.null(cleaned_df)}
n_nonvalid_pids_day28fu_records <- n_detected
allday28fu_data <- cleaned_df
```

### Non-consistent participant names [Context check `r qc_nonconsistent_name_day28fu`]

```{r}
write(" o Non-consistent participant names", stderr())
```

```{r, eval=is_tanzania}
raw_day0_with_names <- day0_data %>% 
  merge(raw_pii %>%
          dplyr::select(fs_name,
                        ms_name,
                        ls_name,
                        uuid),
        by = "uuid")
```

```{r, eval=!is_tanzania}
raw_day0_with_names <- day0_data %>%
  merge(raw_pii %>%
          dplyr::select(fs_name,
                        ls_name,
                        uuid),
        by = "uuid")
```

```{r, eval=!is.null(allday28fu_data), results='asis'}
qc_description <- "Day 28 follow-ups are relevant only if the name of the participant matches the name of the participant enrolled at Day 0. Some errors can be introduced when participant IDs have been duplicated or follow-ups have been entered manually."
qc_rule <- "Keep only IDs of children who can be found in the initial Day 0 database."
qc_type <- "inconsistent_names"
df <- allday28fu_data
refdf <- raw_day0_with_names
qc_text <- "non-consistent participant names"
qc_idx <- qc_nonconsistent_name_day28fu
qc_export_label <- "nonconsistent_names_day28fu"
qc_export_description <- paste0("the child name found in the ", db_name, " is not consistent with the name of the child with the same ID found in the locked Day 0 database")
cat(knitr::knit_child('database_export_sub_quality_check.Rmd',
                      envir = environment(),
                      quiet = TRUE))
```

### Data cleaning summary\n\n

```{r}
write(" o Data cleaning summary", stderr())
```

```{r}
n_cleaned_allday28fu_records <- nrow(allday28fu_data)
```

```{r}
timci::create_day28fu_qc_flowchart(n_raw_allday28fu_data_records,
                                   n_afterlock_pids_day28fu_records,
                                   n_nonvalid_pids_day28fu_records,
                                   n_cleaned_allday28fu_records)
```

### Data export\n\n

```{r}
write(" o Data export", stderr())
```

```{r, results = 'asis'}
timci::dataset_export(raw_allday28fu_data,
                      "06a",
                      "timci_followup_day28_data",
                      rctls_dir,
                      "Raw Day 28 follow-up data")
```

```{r, results = 'asis'}
timci::dataset_export(allday28fu_data,
                      "06a",
                      "timci_followup_day28_data",
                      locked_db_dir,
                      "Cleaned Day 28 follow-up data")
```
