```{r}
write("Export Day 7 data and run corresponding quality checks", stderr())
```

\newpage

## Day 7 data quality checks

```{r}
day7fu_data <- NULL
allday7fu_data <- NULL
```

```{r format-RCT-LS-ODK-fu-day7-data}
res <- timci::format_day7_data(raw_day7fu_data)
day7fu_data <- res[[1]]
allday7fu_data <- res[[3]]
```

```{r, results = 'asis'}
cat(paste0("There are **", nrow(allday7fu_data), "** records in the raw Day 7 follow-up database, among which **", nrow(day7fu_data), "** records documenting successful follow-ups."))
```

### Non-valid participant IDs [compliance check]

```{r}
write(" o Non-valid participant IDs [Day 7 data quality checks]", stderr())
```

**Rule:** keep only IDs of children who are enrolled in the locked Day 0 database (note: if data collection is still going-on, all participants enrolled after the lock will be considered as 'invalid' IDs).

```{r}
locked_day7fu_data <- NULL
locked_allday7fu_data <- NULL
if (!is.null(raw_day7fu_data)) {
  if (nrow(raw_day7fu_data) > 0) {
    # All follow-ups
    locked_allday7fu_data <- allday7fu_data[allday7fu_data$child_id %in% locked_day0_data$child_id, ]
    allday7fu_data_uids <- allday7fu_data[!allday7fu_data$child_id %in% locked_day0_data$child_id, ]
    # Successful follow-ups
    locked_day7fu_data <- day7fu_data[day7fu_data$child_id %in% locked_day0_data$child_id, ]
    day7fu_data_uids <- day7fu_data[!day7fu_data$child_id %in% locked_day0_data$child_id, ]
    locked_day7fu_data <- locked_day7fu_data %>%
      dplyr::mutate(window = ifelse(days >= 7 & days <= 10, 1, 0))
  }
}
```

```{r, results = 'asis'}
if (!is.null(allday7fu_data)) {
  if (nrow(allday7fu_data) > 0) {
    timci::format_nrow("", allday7fu_data_uids, "records with non-valid participant IDs were detected and removed in the locked Day 7 follow-up database.")
  }
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  if (nrow(day7fu_data) > 0) {
    timci::format_nrow("", day7fu_data_uids, "records with non-valid participant IDs were detected and removed in the locked successful Day 7 follow-up database.")
  }
}
```

```{r, results='asis', eval=!is.null(allday7fu_data_uids)}
allday7fu_data_uids_fn <- "DQC_07_01_nonvalid_ids_day7fu"
fn <- timci::export_df2xlsx(allday7fu_data_uids[c("child_id", "uuid")],
                            qc_dir,
                            allday7fu_data_uids_fn)
cat(paste0("The table of Day 7 follow-ups for which the child ID does not correspond to any ID found the locked Day 0 database is exported to **", allday7fu_data_uids_fn, "**"))
```

```{r}
# Replace Day 7 data by locked Day 7 data so that non-valid device IDs/facilities do not appear in the export
day7fu_data <- locked_day7fu_data
```

### Duplicate management

#### Successful follow-up duplicates

```{r}
write(" o Successful follow-up duplicates [Day 7 data quality checks]", stderr())
```

```{r, results='asis', eval=is_kenya}
cat("##### Initial check")
```

```{r check-RCT-LS-ODK-fu-day7-data, results='asis'}
if (!is.null(day7fu_data)) {
  day7fu_qc <- timci::detect_id_duplicates(locked_day7fu_data)
  day7fu_duplicates <- day7fu_qc[day7fu_qc$id_fq > 1,]
}

if (!is.null(day7fu_data)) {
  if (length(day7fu_duplicates) > 0) { 
    cat(paste0("**", nrow(day7fu_duplicates), "** duplicated successful follow-ups detected."))
  }
}

```

```{r}
if (!is.null(locked_day7fu_data)) {
  if (nrow(locked_day7fu_data) > 0) {
    id_duplicates <- timci::identify_dayfu_id_duplicates_with_dates(locked_day7fu_data)
  }
}
```

```{r, results='asis'}
if (!is.null(locked_day7fu_data)) {
  if (nrow(locked_day7fu_data) > 0) {
    if (nrow(id_duplicates) > 0) { 
      id_duplicates %>%
        knitr::kable(row.names = FALSE)
    }
  }
}
```

```{r, results='asis', eval=is_kenya}
cat("##### Child ID duplicate manual edits")
```

```{r, results='asis'}
out <- timci::correct_day7_duplicates(locked_day7fu_data)
locked_day7fu_data <- out[[1]]
duplicate_edits <- out[[2]]
if (!is.null(duplicate_edits)) {
  duplicate_edits %>%
    select(old_child_id, uuid, new_child_id) %>%
    knitr::kable()
}
```

```{r, results='asis', eval=is_kenya}
cat("##### Second check after manual edits")
```

```{r, results='asis'}
cat("Rule: only one successful follow-up is kept with the following priority rule: day 7 > day 8 > day 9 > day 10 > day 6 > day 11 and above")
```

```{r}
if (!is.null(day7fu_data)) {
  # Process duplicates separately
  day7fu_data_duplicates <- locked_day7fu_data[locked_day7fu_data$child_id %in% day7fu_duplicates$child_id, ]
  # Remove all duplicates from the dataframe
  locked_day7fu_data <- locked_day7fu_data[!locked_day7fu_data$child_id %in% day7fu_duplicates$child_id, ]
  # Process duplicates
  processed_day7fu_data_duplicates <- day7fu_data_duplicates %>%
    dplyr::group_by(child_id) %>%
    dplyr::slice_max(order_by = window) %>%
    dplyr::slice_min(order_by = days)
  # Concatenate with processed duplicates
  locked_day7fu_data <- rbind(locked_day7fu_data, processed_day7fu_data_duplicates)
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("**", nrow(day7fu_data_duplicates) - nrow(processed_day7fu_data_duplicates), "** records were removed in the locked successful Day 7 follow-up database. Note that records duplicated on the same day are kept - we need to define a rule for this."))
}
```

### Day 7 follow-up anterior to enrolment date [consistency check]

To be implemented

### Data cleaning summary

```{r}
write(" o Data cleaning summary", stderr())
```

```{r, results = 'asis'}
if (!is.null(allday7fu_data)) {
  if (nrow(allday7fu_data) > 0) {
    timci::format_nrow("There are", locked_allday7fu_data, "record(s) in the locked Day 7 follow-up database.")
  }
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  if (nrow(day7fu_data) > 0) {
    timci::format_nrow("There are", locked_day7fu_data, "record(s) in the locked successful Day 7 follow-up database.")
  }
}
```

```{r day7-lost-to-followup}
ltfu <- NULL
if (!is.null(day7fu_data)) {
  ltfu <- timci::generate_ltfu_log(df = day0_data,
                                   fudf = allday7fu_data,
                                   end_date = 12,
                                   raw = FALSE)
}
```

```{r locked-day7-lost-to-followup}
locked_ltfu <- NULL
if (!is.null(locked_day7fu_data)) {
  locked_ltfu <- timci::generate_ltfu_log(df = locked_day0_data,
                                          fudf = locked_allday7fu_data,
                                          end_date = 12,
                                          raw = FALSE)
}
```

### Data export

```{r}
write("Export Day 7 data", stderr())
```

```{r export-RCT-LS-ODK-fu-day7-data, results = 'asis'}
day7_export_name <- "04b_timci_followup_successful_day7_data"
if (!is.null(day7fu_data)) {
  
  fn <- timci::export_df2csvxlsx(day7fu_data,
                                 params$rctls_dir,
                                 day7_export_name)
  fn <- timci::export_df2csvxlsx(locked_day7fu_data,
                                 locked_db_dir,
                                 day7_export_name)
}
if (!is.null(allday7fu_data)) {
  
  fn <- timci::export_df2csvxlsx(allday7fu_data,
                                 params$rctls_dir,
                                 "04a_timci_followup_day7_data")
  fn <- timci::export_df2csvxlsx(locked_allday7fu_data,
                                 locked_db_dir,
                                 "04a_timci_followup_day7_data")
  fn <- timci::export_df2csvxlsx(allday7fu_data_uids,
                                 qc_dir,
                                 "04c_timci_followup_day7_data_unknown_ids")
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Raw Day 7 follow-up data are exported in ", "04a_timci_followup_day7_data", ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Locked Day 7 follow-up data are exported in ", "04a_timci_followup_day7_data", ".csv/xslx in the ", locked_db_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Raw successful Day 7 follow-up data are exported in ", day7_export_name, ".csv/xslx in the ", params$rctls_dir, " folder"))
}
```

```{r, results = 'asis'}
if (!is.null(day7fu_data)) {
  cat(paste0("* Locked successful Day 7 follow-up data are exported in ", day7_export_name, ".csv/xslx in the ", locked_db_dir, " folder"))
}
```

```{r}
if (!is.null(ltfu)) {
  fn <- timci::export_df2xlsx(ltfu,
                              params$rctls_dir,
                              "04c_day7_lost_to_followup")
}
```

```{r}
if (!is.null(locked_ltfu)) {
  fn <- timci::export_df2xlsx(locked_ltfu,
                              locked_db_dir,
                              "04c_day7_lost_to_followup")
}
```

```{r}
# if (!is.null(pii) & !is.null(raw_day7fu_data)) {
#   fu7all <- timci::generate_fu_log(pii,
#                                    raw_day7fu_data,
#                                    0,
#                                    12,
#                                    7,
#                                    10,
#                                    ext = TRUE,
#                                    deidentify = TRUE)
#   fn <- timci::export_df2xlsx(fu7all,
#                               params$rctls_dir,
#                               "04d_timci_deidentified_day7_fu_weekly_log_all")
# }
```
