---
title: "TIMCI Data Export Report"
author: "`r Sys.getenv('TIMCI_INSTITUTION')`"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
params:
  rctls_dir: "."
  participant_zip: "."
  spa_dir: "."
  qual1_dir: "."
output:
  html_document: default
  word_document:
    reference_docx: word_styles1.docx
---

```{r rmd-setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

ruODK setup

```{r ruODK-setup}
ruODK::ru_setup(
  svc = Sys.getenv("ODKC_SVC"),
  un = Sys.getenv("ODKC_UN"),
  pw = Sys.getenv("ODKC_PW"),
  tz = Sys.getenv("TZ"),
  verbose = FALSE # Can be switched to TRUE for demo or debugging
)
logs <- ruODK::audit_get()
print(logs)
```

TIMCI-specific RCT / LS setup

```{r}
crf_facility_fid <- Sys.getenv("TIMCI_CRF_FACILITY_FID")
crf_day7_fid <- Sys.getenv("TIMCI_CRF_DAY7_FID")
crf_hospit_fid <- Sys.getenv("TIMCI_CRF_HOSPIT_FID")
crf_day28_fid <- Sys.getenv("TIMCI_CRF_DAY28_FID")
wd_fid <- Sys.getenv("TIMCI_WD_FID")
main_study <- Sys.getenv("TIMCI_MAIN_STUDY")
```

Load TIMCI facility CRF data

```{r load-RCT-LS-ODK-facility-data}
raw_facility_data <- ruODK::odata_submission_get(fid = crf_facility_fid)
facility_data <- timci::process_facility_data(raw_facility_data)
start_date <- min(facility_data$date_visit)
end_date <- max(facility_data$date_visit)
```

This report covers the period from **`r start_date`** to **`r end_date`**.

# 1. `r if(Sys.getenv('TIMCI_IS_RCT') == 1){'Pragmatic cluster RCT'} else{'Longitudinal Observational Study'}`

## 1.1. Facility data

### Load data

```{r}
screening_data <- timci::extract_screening_data(facility_data)
timci::export_df2xlsx(screening_data, params$rctls_dir, "01_timci_screening_data")
```

```{r}
res <- timci::extract_enrolled_participants(facility_data)

day0_data <- res[[1]]
n_enrolled <- nrow(day0_data)
deidentified_day0_data <- timci::deidentify_data(day0_data)
timci::export_df2xlsx(deidentified_day0_data, params$rctls_dir, "02_timci_day0_data")

pii <- res[[2]]
xlsx_fname <- timci::export_df2xlsx(pii, tempdir(), "timci_contact_data")
pii_pwd <- Sys.getenv("TIMCI_PII_PW")
zip(params$participant_zip, 
    files = xlsx_fname, 
    flags = paste("-r9Xj --password", pii_pwd))

```

```{r}
study_data <- timci::extract_all_visits(facility_data)
deidentified_facility_data <- timci::deidentify_data(study_data)
tmp <- timci::export_df2xlsx(deidentified_facility_data, params$rctls_dir, "03_timci_facility_visits_data")
```

### Quality checks

#### Duplicates

```{r check-RCT-LS-ODK-facility-data-001, results='asis'}
duplicates <- timci::detect_id_duplicates(day0_data)
if (length(duplicates) > 0) { 
     knitr::kable(duplicates, caption = "ID duplicates")
} else {
  cat("No ID duplicates detected")
}
```

```{r check-RCT-LS-ODK-facility-data-002, results='asis'}
res <- timci::detect_name_duplicates(pii)
duplicates <- res[[1]]
if (nrow(duplicates) > 0) { 
     knitr::kable(duplicates, caption = "Exact name duplicates")
} else {
  cat("No exact name duplicates detected")
}
duplicates <- res[[2]]
if (nrow(duplicates) > 0) { 
     knitr::kable(duplicates, caption = "Switched first and last names")
} else {
  cat("No switched first and last names detected")
}
```

## 1.2. Day 7 follow-up

### Load data

```{r load-RCT-LS-ODK-fu-day7-data}
raw_day7fu_data <- ruODK::odata_submission_get(fid = crf_day7_fid)
res <- timci::format_day7_data(raw_day7fu_data)
day7fu_data <- res[[1]]
```

### Quality checks

```{r check-RCT-LS-ODK-fu-day7-data, results='asis'}
day7fu_duplicates <- timci::detect_id_duplicates(day7fu_data)
if (length(day7fu_duplicates) > 0) { 
     knitr::kable(day7fu_duplicates, caption = "ID duplicates")
} else {
  cat("No ID duplicates detected")
}
```

### Export data

```{r export-RCT-LS-ODK-fu-day7-data}
tmp <- timci::export_df2xlsx(day7fu_data, params$rctls_dir, "04_timci_followup_day7_data")
```

## 1.3. Hospitalisation follow-up

### Load data

```{r load-RCT-LS-ODK-fu-hospit-data}
raw_hospit_data <- ruODK::odata_submission_get(fid = crf_hospit_fid)
hospit_data <- process_hospital_data(raw_hospit_data)
```

### Quality checks

```{r check-RCT-LS-ODK-fu-hospit-data, results='asis'}
hospit_data_duplicates <- detect_id_duplicates(hospit_data)
if (length(hospit_data_duplicates) > 0) { 
     knitr::kable(hospit_data_duplicates, caption = "ID duplicates")
} else {
  cat("No ID duplicates detected")
}
```

### Export data

```{r export-RCT-LS-ODK-fu-hospit-data}
tmp <- timci::export_df2xlsx(hospit_data, params$rctls_dir, "05_timci_followup_hospit_data")
```

## 1.3. Day 28 follow-up

```{r load-RCT-LS-ODK-fu-day28-data}
raw_day28fu_data <- ruODK::odata_submission_get(fid = crf_day28_fid)
day28fu_data <- format_odk_metadata(raw_day28fu_data)
tmp <- timci::export_df2xlsx(day28fu_data, params$rctls_dir, "06_timci_followup_day28_data")
```

## 1.4. Withdrawal data

```{r load-RCT-LS-ODK-withdrawal}
raw_withdrawal_data <- ruODK::odata_submission_get(fid = wd_fid)
withdrawal_data <- format_odk_metadata(raw_withdrawal_data)
```

# 2. Service Provision Assessment (SPA)

```{r spa-setup}
spa_pid <- Sys.getenv("TIMCI_SPA_PID")
cgei_fid <- Sys.getenv("TIMCI_SPA_CGEI_FID")
fa_fid <- Sys.getenv("TIMCI_SPA_FA_FID")
sco_fid <- Sys.getenv("TIMCI_SPA_SCO_FID")
hcpi_fid <- Sys.getenv("TIMCI_SPA_HCPI_FID")
```

## 2.1. Caregiver exit interview

```{r cg-exit-interview-export}
raw_spa_cgei_data <- ruODK::odata_submission_get(pid = spa_pid, fid = cgei_fid)
spa_cgei_data <- format_odk_metadata(raw_spa_cgei_data)
timci::export_df2xlsx(spa_cgei_data, params$spa_dir, "03_timci_spa_exit_interview_data")
```

## 2.2. Facility assessment

```{r facility-assessment-export}
raw_spa_fa_data <- ruODK::odata_submission_get(pid = spa_pid, fid = fa_fid)
spa_fa_data <- format_odk_metadata(raw_spa_fa_data)
timci::export_df2xlsx(spa_fa_data, params$spa_dir, "01_timci_spa_facility_assessment_data")
```

## 2.3. Healthcare provider interview

```{r hcp-interview-export}
raw_spa_hcpi_data <- ruODK::odata_submission_get(pid = spa_pid, fid = hcpi_fid)
spa_hcpi_data <- format_odk_metadata(raw_spa_hcpi_data)
timci::export_df2xlsx(spa_hcpi_data, params$spa_dir, "02_timci_spa_provider_interview_data")
```

## 2.4. Sick child observation protocol

```{r sick-child-observation-export}
raw_spa_sco_data <- ruODK::odata_submission_get(pid = spa_pid, fid = sco_fid)
spa_sco_data <- format_odk_metadata(raw_spa_sco_data)
timci::export_df2xlsx(spa_sco_data, params$spa_dir, "04_timci_spa_consultation_obs_data")
```

# 3. Qualitative studies

```{r qual-setup}
cpid <- Sys.getenv("TIMCI_QUAL_PID")
cgidi1_fid <- Sys.getenv("TIMCI_QUAL_CGIDI1_FID")
cgidi2_fid <- Sys.getenv("TIMCI_QUAL_CGIDI2_FID")
cgidi3_fid <- Sys.getenv("TIMCI_QUAL_CGIDI3_FID")
```

## 3.1. Caregiver in-depth interview

```{r cg-idi-invitation-export}
raw_cgidi_invitation_data <- ruODK::odata_submission_get(pid = cpid,
                                                         fid = cgidi1_fid)
cgidi_invitation_data <- format_odk_metadata(raw_cgidi_invitation_data)
tmp <- timci::export_df2xlsx(cgidi_invitation_data, params$qual1_dir, "01_timci_cg_invitation_data")
```

```{r cg-idi-encryption-export}
raw_cgidi_encryption_data <- ruODK::odata_submission_get(pid = cpid,
                                                         fid = cgidi2_fid)
cgidi_encryption_data <- format_odk_metadata(raw_cgidi_encryption_data)
tmp <- timci::export_df2xlsx(cgidi_encryption_data, params$qual1_dir, "02_timci_cg_encryption_data")
```

```{r cg-idi-interview-export}
raw_cgidi_interview_zip <- ruODK::submission_export(pid = cpid,
                                                    fid = cgidi3_fid)
cgidi_interview_data <- timci::extract_data_from_odk_zip(raw_cgidi_interview_zip, paste0(cgidi3_fid,".csv"))
tmp <- timci::export_df2xlsx(cgidi_interview_data, params$qual1_dir, "03_timci_cg_interview_data")
```

```{r}
sl <- ruODK::submission_list(pid = cpid,
                             fid = cgidi3_fid)

# Loop on all rows
for (i in 1:nrow(sl)) {
  crow <- cgidi_interview_data[i,]
  uuid <- crow$'meta-instanceID'
  cpath <- file.path(params$qual1_dir, crow$'identification-idiidm')
  print(paste0("Participant: ", crow$'identification-idiidm'))
  dir.create(cpath, showWarnings = FALSE)
  # Create a new dataframe using the transpose of crow
  tcrow <- as.data.frame(t(as.matrix(crow)))
  names(tcrow)[names(tcrow) == "V1"] <- "values"
  fname <- file.path(cpath, paste("data", "_", Sys.Date(), ".xlsx", sep = ""))
  openxlsx::write.xlsx(tcrow, fname, row.names = TRUE)
  
  # Download attachments
  al <- ruODK::get_one_submission_attachment_list(pid = cpid,
                                                  fid = cgidi3_fid,
                                                  uuid)
  for (j in 1:nrow(al)) {
    aid <- al$name[[j]]
    print(paste0("Attachment: ", aid))
    ruODK::attachment_get(pid = cpid,
                          fid = cgidi3_fid,
                          uuid, 
                          aid,
                          local_dir = cpath)
  }
}
```
