---
title: "TIMCI `r if(params$fu_fid == Sys.getenv('TIMCI_CRF_DAY7_FID')){'Day 7'} else if(params$fu_fid == Sys.getenv('TIMCI_CRF_DAY28_FID')){'Day 28'}` follow-up - Daily log"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King George s Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
params:
  output_dir: !r tempdir()
  rct_ls_form_list: NULL
  facility_data: NULL
  rctls_pid: NULL
  fu_fid: !r Sys.getenv('TIMCI_CRF_DAY7_FID')
  raw_fu_data: NULL
  raw_oth_fu_data: NULL
  raw_withdrawal_data: NULL
  fu_start: 6
  fu_end: 12
  physicalday7fu_end: 35
  fu_vstart: 7
  fu_vend: 10
output:
  html_document: default
  word_document:
    reference_docx: word_styles1.docx
---

```{r setup-rmd, include=FALSE}
library(qrcode)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r setup-variables}
fu_start <- params$fu_start
fu_end <- params$fu_end
physicalday7fu_end <- params$physicalday7fu_end
fu_vstart <- params$fu_vstart
fu_vend <- params$fu_vend
rctls_pid <- params$rctls_pid
fu_fid <- params$fu_fid
output_dir <- params$output_dir

# Create `odk_external_files` folder if it does not exist
dir.create(file.path(output_dir, "odk_external_files"), showWarnings = FALSE)

if (!is.null(params$facility_data)) {
  
  facility_data <- params$facility_data
  res <- timci::extract_enrolled_participants(facility_data)
  day0_data <- res[[1]]
  pii <- res[[2]]
  raw_fu_data <- params$raw_fu_data
  raw_oth_fu_data <- params$raw_oth_fu_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  rct_ls_form_list <- params$rct_ls_form_list
  
}
```

```{r}
fu <- timci::generate_fu_log_csv(pii,
                                 raw_fu_data,
                                 fu_start,
                                 fu_end,
                                 fu_vstart,
                                 fu_vend)
```

```{r, eval=(Sys.getenv('TIMCI_COUNTRY') == 'Tanzania')&(fu_fid == Sys.getenv('TIMCI_CRF_DAY7_FID'))}
physicalday7fu <- timci::generate_physical_fu_log_csv(pii,
                                                      raw_fu_data,
                                                      fu_start,
                                                      physicalday7fu_end,
                                                      fu_vstart,
                                                      fu_vend)
```

```{r, eval=(fu_fid == Sys.getenv('TIMCI_CRF_DAY28_FID'))}
if (!is.null(raw_oth_fu_data)) {
  if (nrow(raw_oth_fu_data) > 0) {
    # Remove duplicate child ID entries in raw_oth_fu_data based while keeping the most recent date
    raw_oth_fu_data <- raw_oth_fu_data %>% rename(child_id = 'a1-pid')
    raw_oth_fu_data <- aggregate(date ~ child_id, raw_oth_fu_data, max)
    raw_oth_fu_data <- raw_oth_fu_data %>% rename('a1-pid' = 'child_id')
    # Add date of the day 7 follow-up in the day 28 log, if available
    fu <- merge(fu,
                raw_oth_fu_data[, c('a1-pid', 'date')],
                by.x = 'name',
                by.y = 'a1-pid',
                all.x = TRUE) %>%
          dplyr::rename(day7fu = date)
  }
}
```

```{r}
if (!is.null(raw_fu_data)) {
  if (nrow(raw_fu_data) > 0) {
    failed_fu_data <- timci::format_day7_data(raw_fu_data)[[2]]
    if (fu_fid == Sys.getenv('TIMCI_CRF_DAY7_FID')) {
      tmp <- timci::export_df2xlsx(failed_fu_data, output_dir, "day7_unsuccessful_calls")
    } else if (params$fu_fid == Sys.getenv('TIMCI_CRF_DAY28_FID')) {
      tmp <- timci::export_df2xlsx(failed_fu_data, output_dir, "day28_unsuccessful_calls")
    }
  }
}
```

```{r}
ltfu <- timci::generate_ltfu_log(day0_data,
                                 raw_fu_data,
                                 fu_end)
if (fu_fid == Sys.getenv('TIMCI_CRF_DAY7_FID')) {
  tmp <- timci::export_df2xlsx(ltfu, output_dir, "day7_lost_to_followup")
} else if (params$fu_fid == Sys.getenv('TIMCI_CRF_DAY28_FID')) {
  tmp <- timci::export_df2xlsx(ltfu, output_dir, "day28_lost_to_followup")
}
```

```{r}
pii_cols <- c("child_id",
              "fs_name",
              "ls_name",
              "cg_fs_name",
              "cg_ls_name",
              "mother_fs_name",
              "mother_ls_name",
              "phone_nb",
              "phone_owner",
              "phone_nb2",
              "cmty_contact")
ext_ltfu <- merge(ltfu, pii[, pii_cols], by = c("child_id"))
if (fu_fid == Sys.getenv('TIMCI_CRF_DAY7_FID')) {
  tmp <- timci::export_df2xlsx(ext_ltfu, output_dir, "day7_lost_to_followup_incl_pii")
} else if (params$fu_fid == Sys.getenv('TIMCI_CRF_DAY28_FID')) {
  tmp <- timci::export_df2xlsx(ext_ltfu, output_dir, "day28_lost_to_followup_incl_pii")
}
```

```{r}
if (fu_fid == Sys.getenv('TIMCI_CRF_DAY7_FID')) {
  csv_filename <- file.path(output_dir, "odk_external_files", "day7fu.csv")
  write.csv(fu, csv_filename, row.names = FALSE, quote = FALSE, fileEncoding = "UTF-8")
  if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {
    csv_filename2 <- file.path(output_dir, "odk_external_files", "day7physicalfu.csv")
    write.csv(physicalday7fu, csv_filename2, row.names = FALSE, quote = FALSE, fileEncoding = "UTF-8")
  }
} else if (params$fu_fid == Sys.getenv('TIMCI_CRF_DAY28_FID')) {
  csv_filename <- file.path(output_dir, "odk_external_files", "day28fu.csv")
  write.csv(fu, csv_filename, row.names = FALSE, quote = FALSE, fileEncoding = "UTF-8")
}
```

# Upload list of participants on the ODK Central server

```{r}
current_version <- "N/A"
if (fu_fid %in% rct_ls_form_list) {
  # Get form details
  cform <- ruODK::form_detail(
    pid = rctls_pid,
    fid = fu_fid,
    url = ruODK::get_default_url(),
    un = ruODK::get_default_un(),
    pw = ruODK::get_default_pw(),
  )
  version_no_bracket <- strsplit(cform$version, "[[]")[[1]][1]
  encryption_version <- strsplit(cform$version, "[[]")[[1]][2]
  current_version <- as.numeric(version_no_bracket)
}
```

```{r}
form_url <- "N/A"
draft_response <- NULL
csv_upload_response <- NULL
new_version <- "N/A"
publication_response <- NULL

if (fu_fid %in% rct_ls_form_list) {
  form_url <- paste0(ruODK::get_default_url(), "/v1/projects/", rctls_pid, "/forms/", fu_fid)
  # Create a new draft of the form
  draft_response  <- timci::create_odkc_draft_form(ruODK::get_default_un(), ruODK::get_default_pw(), form_url)
  # Upload the new CSV created as a form attachment
  csv_upload_response <- timci::upload_odkc_csv_attachment(ruODK::get_default_un(), ruODK::get_default_pw(), form_url, csv_filename)
  # Publish a draft form
  new_version <- as.character(current_version + 0.000000001)
  # Reintegrate the encryption number if necessary
  if (!is.na(encryption_version)) {
    new_version <- paste0(new_version, "[", encryption_version)
  }
  
  publication_response <- timci::publish_odkc_draft_form(ruODK::get_default_un(), ruODK::get_default_pw(), form_url, new_version)
}
```

**`r form_url`**

* Initial version of the form: **`r current_version`**

* Create a new draft of the form: **`r draft_response$success`**

* Upload the CSV containing the current follow-up log as an attachment to the draft: **`r csv_upload_response$success`**

* Publish the updated form with version number **`r new_version`**: **`r publication_response$success`**
