---
title: "TIMCI hospitalisation follow-up log"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King George s Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
params:
  output_dir: !r tempdir()
  rct_ls_form_list: NULL
  pii: NULL
  day0_data: NULL
  rctls_pid: NULL
  raw_day7fu_data: NULL
  raw_hospit_data: NULL
  raw_withdrawal_data: NULL
  fu_end: 12
output:
  html_document: default
  word_document:
    reference_docx: word_styles2.docx
---

```{r setup-rmd, include=FALSE}
library(qrcode)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r load-hospit-environment-variables}
output_dir <- params$output_dir

# Create `odk_external_files` folder if it does not exist
dir.create(file.path(output_dir, "odk_external_files"), showWarnings = FALSE)

crf_hospit_fid <- Sys.getenv("TIMCI_CRF_HOSPIT_FID")

if (!is.null(params$raw_day7fu_data)) {
  
  pii <- params$pii
  day0_data <- params$day0_data
  rctls_pid <- params$rctls_pid
  rct_ls_form_list <- params$rct_ls_form_list
  raw_day7fu_data <- params$raw_day7fu_data
  raw_hospit_data <- params$raw_hospit_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  
} else {

  print("Please load data first")
  
}
```

```{r}
hospit_fu <- timci::generate_hospital_log(pii = pii,
                                          fu7df = raw_day7fu_data,
                                          day0df = day0_data,
                                          hospitdf = raw_hospit_data,
                                          deidentify = FALSE)
```

```{r}
dir.create(file.path(output_dir, "odk_external_files"), showWarnings = FALSE)
csvh_fname <- file.path(output_dir, "odk_external_files", "higher_level_visits.csv")
write.csv(hospit_fu, csvh_fname, row.names = FALSE, quote = FALSE, fileEncoding = "UTF-8")
if (!is.null(hospit_fu)) {
  if (nrow(hospit_fu) > 0) {
    tmp <- timci::export_df2xlsx(hospit_fu, output_dir, "timci_hospit_fu_log_all")
  }
}
```

```{r}
if (!is.null(hospit_fu)) {
  if (nrow(hospit_fu) > 0) {
    for (i in 1:nrow(hospit_fu)) {
      pid <- toString(hospit_fu[i,'name'])
      png_file <- file.path(tempdir(), paste0(pid,".png"))
      png(png_file)
      qrcode::qrcode_gen(pid)
      dev.off()
      }
    
    df <- hospit_fu %>%
      dplyr::mutate(
        code = paste0('![](', file.path(tempdir(), paste0(hospit_fu$name,".png")), ')', '{width=0.75in}')
        ) %>%
      dplyr::select('code', dplyr::everything()) %>%
      dplyr::rename('id' = 'name',
                    'child' = 'label',
                    'enrolment date' = 'enroldate',
                    'day 7 call date' = 'day7fudate')
    
    drops <- c("sex", "device_id", "rhf_loc_id")
    df <- df[ , !(names(df) %in% drops)]
    
    df %>% knitr::kable()
  }
}
```

# Upload list of participants on the ODK Central server

```{r}
current_version <- "N/A"
if (crf_hospit_fid %in% rct_ls_form_list) {
  # Get form details
  cform <- ruODK::form_detail(
    pid = rctls_pid,
    fid = crf_hospit_fid,
    url = ruODK::get_default_url(),
    un = ruODK::get_default_un(),
    pw = ruODK::get_default_pw(),
  )
  version_no_bracket <- strsplit(cform$version, "[[]")[[1]][1]
  encryption_version <- strsplit(cform$version, "[[]")[[1]][2]
  current_version <- as.numeric(version_no_bracket)
}
```

```{r}
form_url <- "N/A"
draft_response <- NULL
csv_upload_response <- NULL
new_version <- "N/A"
publication_response <- NULL
if (crf_hospit_fid %in% rct_ls_form_list) {
  form_url <- paste0(ruODK::get_default_url(), "/v1/projects/", rctls_pid, "/forms/", crf_hospit_fid)
  # Create a draft form
  draft_response <- timci::create_odkc_draft_form(ruODK::get_default_un(), ruODK::get_default_pw(), form_url)
  # Upload the new CSV created as a form attachment
  csv_upload_response <- timci::upload_odkc_csv_attachment(ruODK::get_default_un(), ruODK::get_default_pw(), form_url, csvh_fname)
  # Publish a draft form
  new_version <- as.character(current_version + 0.000000001)
  publication_response <- timci::publish_odkc_draft_form(ruODK::get_default_un(), ruODK::get_default_pw(), form_url, new_version)
}
```

**`r form_url`**

* Initial version of the form: **`r current_version`**

* Create a new draft of the form: **`r draft_response$success`**

* Upload the CSV containing the current follow-up log as an attachment to the draft: **`r csv_upload_response$success`**

* Publish the updated form with version number **`r new_version`**: **`r publication_response$success`**
