---
title: "TIMCI hospitalisation follow-up log"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King George s Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
params:
  output_dir: !r tempdir()
  rct_ls_form_list: NULL
  pii: NULL
  rctls_pid: NULL
  raw_day7fu_data: NULL
  raw_hospit_data: NULL
  raw_withdrawal_data: NULL
  fu_end: 12
output:
  html_document: default
  word_document:
    reference_docx: word_styles2.docx
---

```{r setup-rmd, include=FALSE}
library(qrcode)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)
```

```{r load-hospit-environment-variables}
output_dir <- params$output_dir

# Create `odk_external_files` folder if it does not exist
dir.create(file.path(output_dir, "odk_external_files"), showWarnings = FALSE)

crf_hospit_fid <- Sys.getenv("TIMCI_CRF_HOSPIT_FID")

if (!is.null(params$raw_day7fu_data)) {
  
  pii <- params$pii
  rctls_pid <- params$rctls_pid
  rct_ls_form_list <- params$rct_ls_form_list
  raw_day7fu_data <- params$raw_day7fu_data
  raw_hospit_data <- params$raw_hospit_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  
} else {

  ################
  # Set up ruODK #
  ################

  ruODK::ru_setup(
    svc = Sys.getenv("ODKC_SVC"),
    un = Sys.getenv("ODKC_UN"),
    pw = Sys.getenv("ODKC_PW"),
    tz = Sys.getenv("TZ"),
    verbose = TRUE # Can be switched to TRUE for demo or debugging
  )

  # List of projects visible with the credentials `ODKC_UN` and `ODKC_PW`
  odkc_project_list <- ruODK::project_list()$id
  wd_fid <- Sys.getenv("TIMCI_WD_FID")

  # RCT / LS environment variables
  crf_facility_fid <- Sys.getenv("TIMCI_CRF_FACILITY_FID")
  crf_day7_fid <- Sys.getenv("TIMCI_CRF_DAY7_FID")
  
  rctls_pid <- Sys.getenv("TIMCI_PILOT_RCTLS_PID")
  rctls_pp <- Sys.getenv("TIMCI_PILOT_RCTLS_PP")

  #######################
  # Load TIMCI ODK data #
  #######################

  # List of forms visible in the RCT / LS project
  rct_ls_form_list <- ruODK::form_list(pid = rctls_pid)$fid

  # Load facility data
  print("Load facility data")

  raw_facility_zip <- ruODK::submission_export(local_dir = tempdir(),
                                               pid = rctls_pid,
                                               fid = crf_facility_fid,
                                               pp = rctls_pp)
  raw_facility_data <- timci::extract_data_from_odk_zip(raw_facility_zip,
                                                        paste0(crf_facility_fid,".csv"),
                                                        start_date = as.Date("2021-07-05"),
                                                        end_date = NULL)
  facility_data <- timci::process_facility_data(raw_facility_data)
  pii <- timci::extract_enrolled_participants(facility_data)[[2]]

  # Load day 7 follow-up data
  print("Load day 7 follow-up data")
  raw_day7fu_data <- NULL
  if (crf_day7_fid %in% rct_ls_form_list) {
    raw_day7fu_zip <- ruODK::submission_export(local_dir = tempdir(),
                                               pid = rctls_pid,
                                               fid = crf_day7_fid,
                                               pp = rctls_pp,
                                               media = FALSE)
    raw_day7fu_data <- timci::extract_data_from_odk_zip(raw_day7fu_zip,
                                                        paste0(crf_day7_fid,".csv"),
                                                        start_date = as.Date("2021-07-05"),
                                                        end_date = NULL)
    ltfu <- timci::generate_fu_log(pii, raw_day7fu_data, fu_end + 1, 100000, fu_end + 1, 100000)
  }
  
  # Load hospital visit follow-up data
  print("Load hospital visit data")
  raw_hospit_data <- NULL
  if (crf_hospit_fid %in% rct_ls_form_list) {
    raw_hospit_zip <- ruODK::submission_export(local_dir = tempdir(),
                                               pid = rctls_pid,
                                               fid = crf_hospit_fid,
                                               pp = rctls_pp,
                                               media = FALSE)
    raw_hospit_data <- timci::extract_data_from_odk_zip(raw_hospit_zip,
                                                        paste0(crf_hospit_fid,".csv"),
                                                        start_date = as.Date("2021-07-05"),
                                                        end_date = NULL)
  }

  # Load widthdrawal data
  print("Load withdrawal data")
  raw_withdrawal_data <- NULL
  if (wd_fid %in% rct_ls_form_list) {
    raw_withdrawal_zip <- ruODK::submission_export(local_dir = tempdir(),
                                                   pid = rctls_pid,
                                                   fid = wd_fid,
                                                   pp = rctls_pp,
                                                   media = FALSE)
    raw_withdrawal_data <- timci::extract_data_from_odk_zip(raw_withdrawal_zip,
                                                            paste0(wd_fid,".csv"),
                                                            start_date = as.Date("2021-07-05"),
                                                            end_date = NULL)
  }
  
}
```

```{r}
hospit_fu <- timci::generate_hospital_log(pii, raw_day7fu_data)
```

```{r}
day7fu <- NULL
if (!is.null(raw_hospit_data)) {
  if (nrow(raw_hospit_data) > 0) {
    day7fu <- timci::generate_fu_log(params$pii, raw_hospit_data, 7, 9)
    day7lost <- timci::generate_fu_log(params$pii, raw_hospit_data, 10, 2000)
    tmp <- timci::export_df2xlsx(day7lost, params$output_dir, "hospit_lost_to_followup")
  }
}
```

```{r}
dir.create(file.path(output_dir, "odk_external_files"), showWarnings = FALSE)
csvh_fname <- file.path(output_dir, "odk_external_files", "higher_level_visits.csv")
write.csv(hospit_fu, csvh_fname, row.names = FALSE, quote = FALSE)
if (!is.null(hospit_fu)) {
  if (nrow(hospit_fu) > 0) {
    tmp <- timci::export_df2xlsx(hospit_fu, output_dir, "timci_hospit_fu_log_all")
  }
}
```

```{r}
if (!is.null(hospit_fu)) {
  for (i in 1:nrow(hospit_fu)) {
    pid <- toString(hospit_fu[i,'name'])
    png_file <- file.path(tempdir(), paste0(pid,".png"))
    png(png_file)
    qrcode::qrcode_gen(pid)
    dev.off()
    }
  
  df <- hospit_fu %>%
    dplyr::mutate(
      code = paste0('![](', file.path(tempdir(), paste0(hospit_fu$name,".png")), ')', '{width=0.75in}')
      ) %>%
    dplyr::select('code', dplyr::everything()) %>%
    dplyr::rename('id' = 'name',
                  'child' = 'label',
                  'enrolment date' = 'enroldate',
                  'day 7 call date' = 'day7fudate')
  
  drops <- c("sex", "device_id", "rhf_loc_id")
  df <- df[ , !(names(df) %in% drops)]
  
  df %>% knitr::kable()
}
```

# Upload list of participants on the ODK Central server

```{r}
current_version <- "N/A"
if (crf_hospit_fid %in% rct_ls_form_list) {
  # Get form details
  cform <- ruODK::form_detail(
    pid = rctls_pid,
    fid = crf_hospit_fid,
    url = ruODK::get_default_url(),
    un = ruODK::get_default_un(),
    pw = ruODK::get_default_pw(),
  )
  version_no_bracket <- strsplit(cform$version, "[[]")[[1]][1]
  encryption_version <- strsplit(cform$version, "[[]")[[1]][2]
  current_version <- as.numeric(version_no_bracket)
}
```

```{r}
form_url <- "N/A"
draft_response <- NULL
csv_upload_response <- NULL
new_version <- "N/A"
publication_response <- NULL
if (crf_hospit_fid %in% rct_ls_form_list) {
  form_url <- paste0(ruODK::get_default_url(), "/v1/projects/", rctls_pid, "/forms/", crf_hospit_fid)
  # Create a draft form
  draft_response <- timci::create_odkc_draft_form(ruODK::get_default_un(), ruODK::get_default_pw(), form_url)
  # Upload the new CSV created as a form attachment
  csv_upload_response <- timci::upload_odkc_csv_attachment(ruODK::get_default_un(), ruODK::get_default_pw(), form_url, csvh_fname)
  # Publish a draft form
  new_version <- as.character(current_version + 0.000000001)
  publication_response <- timci::publish_odkc_draft_form(ruODK::get_default_un(), ruODK::get_default_pw(), form_url, new_version)
}
```

**`r form_url`**

* Initial version of the form: **`r current_version`**

* Create a new draft of the form: **`r draft_response$success`**

* Upload the CSV containing the current follow-up log as an attachment to the draft: **`r csv_upload_response$success`**

* Publish the updated form with version number **`r new_version`**: **`r publication_response$success`**
