---
title: "TIMCI `r if (Sys.getenv('TIMCI_COUNTRY') != 'Senegal') {'Process Mapping & Time-flow - Monitoring Report'} else {'Cartographie des processus & flux temporel - Rapport de suivi'}`"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King Georges Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M GMT%z')`"
params:
  research_facilities: !r data.frame(deviceid = character(0), district = character(0), facility = character(0))
  facility_data: NULL
  tf_data: NULL
  pm_data: NULL
  raw_withdrawal_data: NULL
output:
  pdf_document:
    number_sections: true
    extra_dependencies:
      float: null
      flafter: null
      bm: null
      tocbibind: ["nottoc"]
      babel: ["french","english"]
      graphicx: null
      fancyhdr: null
      lastpage: null
classoption: table
---

```{r setup-rmd, include=FALSE}
library(magrittr)
library(readxl)
library(ggplot2)
library(lubridate)
library(gridExtra)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.pos='!H')
options(qwraps2_markup = 'markdown')

# Qwraps2 parameters
prec <- 1

#kableExtra table parameters
table_fs <- 7
figsize <- 3
total_row_ft <- "gray"
total_row_ft2 <- "white"
striped_row_bg <- "gray!10"
total_row_bg2 <- "gray"
```

\fancypagestyle{plain}{\pagestyle{fancy}}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{32pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[C]{\includegraphics[width=10cm]{banner.png}}
\fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}
\fancyfoot[L]{TIMCI PM \& T-F Operational Report v1.0}

```{r translations-subsection, child = 'translations.Rmd'}
```

\setcounter{tocdepth}{2}
\tableofcontents

\newpage

`r notice_str`

`r intro_str`

```{r setup-variables}
if (!is.null(params$facility_data)) {
  
  facility_data <- params$facility_data
  tf_data <- params$tf_data
  pm_data <- params$pm_data
  raw_withdrawal_data <- params$raw_withdrawal_data
  
}

# Extract personally identifiable data
pii <- timci::extract_enrolled_participants(facility_data)[[2]]

# Merge facility generic info with facility data
facility_data <- merge(facility_data, params$research_facilities[, c("deviceid", "facility_name")], by.x = 'device_id', by.y = 'deviceid', all.x = TRUE)
```

```{r process-facility-data, results='asis'}
start_date <- NULL
end_date <- NULL
if (nrow(tf_data) > 0) {
  start_date <- min(tf_data$date)
  end_date <- max(tf_data$date)
  week_nb <- ceiling(difftime(as.Date(end_date), as.Date(start_date) - 1,units = "weeks"))
  days_nb <- sum(!lubridate::wday(seq(as.Date(start_date), as.Date(end_date), "days")) %in% c("7", "1"))
  if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {
    cat(paste0("Ce rapport couvre la période du **", start_date, "** (début de l'étude) au **", end_date, "** pour le **Sénégal**."))
  } else {
    cat(paste0("This report covers the period from **", start_date, "** (study start) to **", end_date, "** for **", Sys.getenv('TIMCI_COUNTRY'), "**."))
  }
}
```

```{r context-subsection, child = 'context.Rmd'}
```

```{r}
pm_is_not_null <- !is.null(pm_data)
if (pm_is_not_null) {
  pm_is_not_null <- length(pm_data) > 0
}
```

```{r pm-subsection, child = if (pm_is_not_null) 'pmtf_monitoring_report_sub_pm.Rmd'}
```

```{r}
tf_is_not_null <- !is.null(tf_data)
if (tf_is_not_null) {
  tf_is_not_null <- length(tf_data) > 0
}
```

```{r tf-subsection, child = if (tf_is_not_null) 'pmtf_monitoring_report_sub_tf.Rmd'}
```

\newpage
\listoftables

\newpage
\listoffigures

```{r technical-info-subsection, child = 'technical_info.Rmd'}
```
