---
title: "TIMCI caregiver random selection"
author: "H. LANGET"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(readxl)
cdate <- "2022-03-16"#Sys.Date()
myxlsx <- paste0("C:/Users/langhe/Documents/India/timci_exports/export_", cdate, "/01_India_pilot/03_India_qualitative/01_India_caregiver_idis/01_cg_idi_participants.xlsx")
set.seed(2021)
```

## Loading data
```{r, echo=TRUE, message=FALSE}
df <- readxl::read_excel(myxlsx)
df <- df %>%
  mutate(month_category = ifelse(age_mo < 2, 1, ifelse(age_mo < 12, 2, ifelse(age_mo < 24, 3, 4))))
print(nrow(df))
```

## Filter data

### Eligible data collection period
Last week of data collection => most recent date from which referrals are selected (2022-01-22)

```{r, echo=TRUE, message=FALSE}
df1 <- df %>% dplyr::filter(date_visit >= "2022-01-22")
print(nrow(df1))
```

### Atariya (F2101), Majhagawa (F0274), Kamplapur (F0287) and Purwa (F3116)

```{r, echo=TRUE, message=FALSE}
df1 <- df1 %>% dplyr::filter(fid %in% c("F2101","F0274","F0287","F3116"))
print(nrow(df1))
```
### Referred children

```{r, echo=TRUE, message=FALSE}
referred_df <- df1 %>% dplyr::filter(referral_cg == 1 | referral_hf == 1)
print(referred_df)
```

### Non-referred children

```{r, echo=TRUE, message=FALSE}
nonreferred_df <- df1 %>% dplyr::filter(referral_cg == 0 & referral_hf == 0)
print(nrow(nonreferred_df))
```
#### Split by regions

```{r, echo=TRUE, message=FALSE}
referred_sitapur_df <- referred_df %>% dplyr::filter(district_ra == "Sitapur")
print(nrow(referred_sitapur_df))

referred_unnao_df <- referred_df %>% dplyr::filter(district_ra == "Unnao")
print(nrow(referred_unnao_df))

referred_deoria_df <- referred_df %>% dplyr::filter(district_ra == "Deoria")
print(nrow(referred_deoria_df))
```

```{r, echo=TRUE, message=FALSE}
nonreferred_sitapur_df <- nonreferred_df %>% dplyr::filter(district_ra == "Sitapur")
print(nrow(nonreferred_sitapur_df))

nonreferred_unnao_df <- nonreferred_df %>% dplyr::filter(district_ra == "Unnao")
print(nrow(nonreferred_unnao_df))

nonreferred_deoria_df <- nonreferred_df %>% dplyr::filter(district_ra == "Deoria")
print(nrow(nonreferred_deoria_df))
```
## Random selection for referred children
```{r, echo=TRUE, message=FALSE}
random_selection_sitapur <- referred_sitapur_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_unnao <- referred_unnao_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_deoria <- referred_deoria_df %>%
  group_by(month_category) %>%
  sample_n(1)
#nonreferred_sitapur_df <- nonreferred_sitapur_df[!nonreferred_sitapur_df$child_id %in% random_selection_sitapur$child_id, ]
print(random_selection_sitapur)
print(random_selection_unnao)
print(random_selection_deoria)

referred_random_selection <- rbind(random_selection_sitapur, random_selection_unnao, random_selection_deoria)
print(referred_random_selection)
```

## Random selection for non-referred children
```{r, echo=TRUE, message=FALSE}
random_selection_sitapur <- nonreferred_sitapur_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_unnao <- nonreferred_unnao_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_deoria <- nonreferred_deoria_df %>%
  group_by(month_category) %>%
  sample_n(1)
#nonreferred_sitapur_df <- nonreferred_sitapur_df[!nonreferred_sitapur_df$child_id %in% random_selection_sitapur$child_id, ]
print(random_selection_sitapur)
print(random_selection_unnao)
print(random_selection_deoria)

random_selection <- rbind(random_selection_sitapur, random_selection_unnao, random_selection_deoria)
print(random_selection)
```

```{r, echo=TRUE, message=FALSE}
openxlsx::write.xlsx(random_selection, "india_qual_selection_nonreferred.xlsx", row.names = FALSE, overwrite = TRUE)
```
## Random selection for non-referred children (backup)
```{r, echo=TRUE, message=FALSE}
nonreferred_sitapur_df <- nonreferred_sitapur_df[!nonreferred_sitapur_df$child_id %in% random_selection_sitapur$child_id, ]
nonreferred_deoria_df <- nonreferred_deoria_df[!nonreferred_deoria_df$child_id %in% random_selection_deoria$child_id, ]
nonreferred_unnao_df <- nonreferred_unnao_df[!nonreferred_unnao_df$child_id %in% random_selection_unnao$child_id, ]

random_selection_sitapur_bkp <- nonreferred_sitapur_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_unnao_bkp <- nonreferred_unnao_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_deoria_bkp <- nonreferred_deoria_df %>%
  group_by(month_category) %>%
  sample_n(1)

print(random_selection_sitapur_bkp)
print(random_selection_unnao_bkp)
print(random_selection_deoria_bkp)

random_selection_bkp <- rbind(random_selection_sitapur_bkp, random_selection_unnao_bkp, random_selection_deoria_bkp)
print(random_selection_bkp)
```

```{r, echo=TRUE, message=FALSE}
openxlsx::write.xlsx(random_selection_bkp, "india_qual_selection_nonreferred_bkp.xlsx", row.names = FALSE, overwrite = TRUE)
```
## Random selection for non-referred children (backup 2)
```{r, echo=TRUE, message=FALSE}
nonreferred_sitapur_df <- nonreferred_sitapur_df[!nonreferred_sitapur_df$child_id %in% random_selection_sitapur_bkp$child_id, ]
nonreferred_deoria_df <- nonreferred_deoria_df[!nonreferred_deoria_df$child_id %in% random_selection_deoria_bkp$child_id, ]
nonreferred_unnao_df <- nonreferred_unnao_df[!nonreferred_unnao_df$child_id %in% random_selection_unnao_bkp$child_id, ]

random_selection_sitapur_bkp2 <- nonreferred_sitapur_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_unnao_bkp2 <- nonreferred_unnao_df %>%
  group_by(month_category) %>%
  sample_n(1)
random_selection_deoria_bkp2 <- nonreferred_deoria_df %>%
  group_by(month_category) %>%
  sample_n(1)

print(random_selection_sitapur_bkp2)
print(random_selection_unnao_bkp2)
print(random_selection_deoria_bkp2)

random_selection_bkp2 <- rbind(random_selection_sitapur_bkp2, random_selection_unnao_bkp2, random_selection_deoria_bkp2)
print(random_selection_bkp2)
```
```{r, echo=TRUE, message=FALSE}
openxlsx::write.xlsx(random_selection_bkp2, "india_qual_selection_nonreferred_bkp2.xlsx", row.names = FALSE, overwrite = TRUE)
```
