---
title: "TIMCI `r Sys.getenv('TIMCI_MAIN_STUDY')` Monitoring Report"
author: "`r Sys.getenv('TIMCI_INSTITUTION')`"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  html_document: default
  word_document:
    reference_docx: word_styles1.docx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Introduction

```{r ruODK-setup, echo=FALSE}
ruODK::ru_setup(
  svc = Sys.getenv("ODKC_SVC"),
  un = Sys.getenv("ODKC_UN"),
  pw = Sys.getenv("ODKC_PW"),
  tz = Sys.getenv("TZ"),
  verbose = FALSE # Can be switched to TRUE for demo or debugging
)
```

```{r, echo=FALSE}
crf_facility_fid <- Sys.getenv("TIMCI_CRF_FACILITY_FID")
crf_day7_fid <- Sys.getenv("TIMCI_CRF_DAY7_FID")
crf_hospit_fid <- Sys.getenv("TIMCI_CRF_HOSPIT_FID")
crf_day28_fid <- Sys.getenv("TIMCI_CRF_DAY28_FID")
wd_fid <- Sys.getenv("TIMCI_WD_FID")
```

```{r, echo=FALSE}
raw_facility_data <- ruODK::odata_submission_get(fid = crf_facility_fid)
raw_day7fu_data <- ruODK::odata_submission_get(fid = crf_day7_fid)
raw_hospit_data <- ruODK::odata_submission_get(fid = crf_hospit_fid)
raw_day28fu_data <- ruODK::odata_submission_get(fid = crf_day28_fid)
raw_withdrawal_data <- ruODK::odata_submission_get(fid = wd_fid)
```

```{r, echo=FALSE}
facility_data <- timci::process_facility_data(raw_facility_data)
```

```{r, echo=FALSE}
start_date <- min(facility_data$date_visit)
end_date <- max(facility_data$date_visit)
```

This report covers the period from **`r start_date`** to **`r end_date`**.

# 2. Submissions

## Number of submissions per day
```{r, echo=FALSE}
w <- 14
facility_submission_bar_plot <- timci::generate_day_bar_plot(facility_data$date_visit, as.Date(end_date) - w, as.Date(end_date))
plot(facility_submission_bar_plot)
```

## Number of submissions per form
```{r, echo=FALSE, results = "asis"}
n_screened <- nrow(facility_data)
screening_data <- timci::extract_screening_data(facility_data)

res <- timci::extract_enrolled_participants(facility_data)
demog_data <- res[[1]]
pii <- res[[2]]
n_enrolled <- nrow(demog_data)

study_data <- extract_all_visits(facility_data)
baseline_data <- extract_baseline_visits(study_data)
repeat_data <- extract_repeat_visits(study_data)
n_repeat <- nrow(repeat_data)

n_day7fu <- nrow(raw_day7fu_data)
n_day28fu <- nrow(raw_day28fu_data)
n_hospit <- nrow(raw_hospit_data)

n_withdrawal <- nrow(raw_withdrawal_data)

n_all <- n_screened + n_day7fu + n_day28fu + n_hospit + n_withdrawal
visit_names <- c("Screening",
                 "Baseline visit",
                 "Repeat visit",
                 "Day 7 phone call",
                 "Day 28 phone call",
                 "Hospital visit",
                 "Withdrawal",
                 "All")
submissions <- c(n_screened, n_enrolled, n_repeat, n_day7fu, n_day28fu, n_hospit, n_withdrawal, n_all)
visits <- data.frame(visit_names, submissions) 
knitr::kable(visits, col.names = c("Visit", "N"))
```

# 3. Participants
```{r, echo=FALSE, results = "asis"}
options(qwraps2_markup = 'markdown')

all <- data.frame(facility_data)
all$sickness[is.na(all$sickness)] <- 0
all$inpatient[is.na(all$inpatient)] <- 0
all$consult_reason[is.na(all$consult_reason)] <- 0
all$prev_enrl[is.na(all$prev_enrl)] <- 0
all$repeat_consult[is.na(all$repeat_consult)] <- 0
all$consent[is.na(all$consent)] <- 0
all$yg_infant <- ifelse(all$yg_infant == 0, "2-59m", "0-2m")

summary_statistics <- list(
  "Age eligibility" = list(
    "0 - 59 months" = ~qwraps2::n_perc(age_incl == 1, 2),
    "First day of life" = ~qwraps2::n_perc(age_excl == 1, 2)
    ),
  "Visit eligibility" = list(
    "Sick child" = ~qwraps2::n_perc(sickness == 1, 2),
    "Inpatient admission" = ~qwraps2::n_perc(inpatient == 1, 2),
    "Trauma" = ~qwraps2::n_perc(consult_reason == 2, 2),
    "Immunisation" = ~qwraps2::n_perc(consult_reason == 3, 2),
    "Monitoring" = ~qwraps2::n_perc(consult_reason == 4, 2)
    ),
  "Multiple enrolments" = list(
    "Previous enrolment" = ~qwraps2::n_perc(prev_enrl == 1 | prev_enrl == 2, 2),
    "Last enrolment < 28 days" = ~qwraps2::n_perc(repeat_consult == 1, 2)
    ),
  "Consenting process outcome" = list(
    "Enrolled" = ~qwraps2::n_perc(consent == 1, 2)
    )
)
st <- qwraps2::summary_table(all, summary_statistics)
st1 <- qwraps2::summary_table(dplyr::group_by(all, yg_infant), summary_statistics)
print(cbind(st, st1))
```

```{r, echo=FALSE}
deidentified_facility_data <- timci::deidentify_data(study_data)
```

### Enrolment versus global target
```{r, echo=FALSE}
#enrolment_hist <- timci::generate_enrolment_hist(deidentified_facility_data)
#plot(enrolment_hist)
```
### Enrolment versus weekly target
### Enrolment rate
```{r, echo=FALSE}
enrolment_pie_chart <- timci::generate_pie_chart(data.frame(group = c("Enrolled", "Not enrolled"), value = c(n_enrolled, n_screened - n_enrolled)))
plot(enrolment_pie_chart)
```

### Non-enrolment causes
```{r, echo=FALSE}
non_enrolment_causes <- timci::count_screening(facility_data)
nec_pie_chart <- timci::generate_pie_chart(non_enrolment_causes)
plot(nec_pie_chart)
```

# 4. Baseline visit

## Medical history

## Hypoxaemia

## Lab tests

## Diagnosis and care management 

### Referrals

```{r, echo=FALSE, results = "asis"}
options(qwraps2_markup = 'markdown')

all <- data.frame(study_data)
all$yg_infant <- ifelse(all$yg_infant == 0, "2-59m", "0-2m")

summary_statistics <- list(
  "Referral" = list(
    "Reported (caregiver)" = ~qwraps2::n_perc(referral_cg == 1 | referral_cg == 2, 2),
    "Declined (caregiver)" = ~qwraps2::n_perc(referral_cg == 97, 2),
    "Reported (registry)" = ~qwraps2::n_perc(referral_hf == 1 | referral_hf == 2 | referral_hf == 3, 2),
    "Inpatient admission (registry)" = ~qwraps2::n_perc(referral_hf == 4, 2)
    )
)
referral_summary <- qwraps2::summary_table(all, summary_statistics)
referral_summary1 <- qwraps2::summary_table(dplyr::group_by(all, yg_infant), summary_statistics)
print(cbind(referral_summary, referral_summary1))
```

```{r, echo=FALSE}
referral_data <- timci::extract_referrals(deidentified_facility_data)
n_referrals <- nrow(referral_data)
referral_pie_chart <- timci::generate_pie_chart(data.frame(group = c("Referred at Day 0", "Not referred at Day 0"), value = c(n_referrals, n_enrolled - n_referrals)))
plot(referral_pie_chart)
```

# 5. Day 7 follow-up

Lost to follow-up  
Child cured?  
Child alive?  
Visit to hospital between baseline and D7  
If yes, reason for admission, hospital name and location  
Was child hospitalized? If yes, details  

```{r, echo=FALSE, results = "asis"}
options(qwraps2_markup = 'markdown')

all <- data.frame(raw_day7fu_data)
all$a1_contact_a4_d_1b[is.na(all$a1_contact_a4_d_1b)] <- 0
all$o1_o1_1a[is.na(all$o1_o1_1a)] <- 0
all$o1_o1_1[is.na(all$o1_o1_1)] <- 0
all$n1_o3_1[is.na(all$n1_o3_1)] <- 0

day7_call_ss <- list(
  "Call outcome" = list(
    "Participant reached" = ~qwraps2::n_perc(a1_contact_a4_d_1b == 1, 2),
    "Valid time window" = ~qwraps2::n_perc(a1_contact_a4_d_1b == 1, 2),
    "Lost to follow-up" = ~qwraps2::n_perc(a1_contact_a4_d_1b == 1, 2)
    )
)
print(qwraps2::summary_table(all, day7_call_ss))

day7_outcome_ss <- list(
  "Cure" = list(
    "Known" = ~qwraps2::n_perc(o1_o1_1 == 1 | o1_o1_1 == 2 | o1_o1_1 == 3 | o1_o1_1 == 4, 2)
    ),
  "Hospitalisation" = list(
    "Reported" = ~qwraps2::n_perc(o1_o1_1a == 2 | n1_o3_1 == 1, 2)
    )
)
print(qwraps2::summary_table(all, day7_outcome_ss))
```
# 6. Hospital follow-up

# 7. Day 28 follow-up
```{r, echo=FALSE, results = "asis"}
options(qwraps2_markup = 'markdown')

all <- data.frame(raw_day28fu_data)
all$a1_contact_a4_d_1b[is.na(all$a1_contact_a4_d_1b)] <- 0
all$o1_o1_1a[is.na(all$o1_o1_1a)] <- 0
all$o1_o1_1[is.na(all$o1_o1_1)] <- 0
all$n1_o3_1[is.na(all$n1_o3_1)] <- 0

day28_call_ss <- list(
  "Call outcome" = list(
    "Participant reached" = ~qwraps2::n_perc(a1_contact_a4_d_1b == 1, 2),
    "Valid time window" = ~qwraps2::n_perc(a1_contact_a4_d_1b == 1, 2),
    "Lost to follow-up" = ~qwraps2::n_perc(a1_contact_a4_d_1b == 0, 2)
    )
)
print(qwraps2::summary_table(all, day28_call_ss))
```
