\clearpage

```{r spa-sco-message}
write(formats2h2("Generate the sick child observation subsection"), stderr())
```

`r h1_spa_sco`

The objective of the sick child observation protocol is:
\begin{itemize}
  \item to understand the impact of intervention(s) on healthcare provider's adherence to practice and quality of care
  \begin{itemize}
    \item critical components of IMCI assessment, diagnosis, management
    \item inform understanding of correctness of severity classification
    \item patient-centeredness of care (respectful care)
  \end{itemize}
  \item to evaluate the implementation of interventions
  \begin{itemize}
    \item functionality, use of and communication about pulse oximetry, including correctness of use
    \item functionality, use of and communication about CDSA, including correctness of use
  \end{itemize}
\end{itemize}

```{r spa-sco-condition}
n <- nrow(spa_sco_data)
cond <- n > 0
spa_sco_heatmap_cap <- paste("Sick child observation", heatmap_cap, sep=' - ')
```

**`r n`** submissions

```{r, eval=cond, results='asis', fig.cap=spa_sco_heatmap_cap}
timci::generate_calendar_heatmap2(spa_sco_data,
                                  date,
                                  legendtitle = "Number of submissions")
```

```{r, eval=cond}
names(spa_sco_data) <- gsub("-", "_", names(spa_sco_data), fixed = TRUE)
```

```{r, eval=cond, results="asis"}
all <- spa_sco_data %>% 
  rename(young_infant = "child_identification_young_infant",
         facility_name = "facility_identification_fname",
         district = "facility_identification_district",
         child_id = "child_identification_pid",
         hcp_id = "hcp_identification_hcpid")
```

```{r, eval=is_senegal}
all <- all %>% 
  dplyr::mutate(quarter = dplyr::case_when(
    as.Date(date) <= as.Date(Sys.getenv("TIMCI_SPA_Q1_END_DATE")) ~ "Q1",
    as.Date(date) > as.Date(Sys.getenv("TIMCI_SPA_Q1_END_DATE")) ~ "Q2")
  )
```

```{r, eval=is_kenya}
all <- all %>% 
  dplyr::mutate(quarter = dplyr::case_when(
    as.Date(date) <= as.Date(Sys.getenv("TIMCI_SPA_Q1_END_DATE")) ~ "Q1",
    as.Date(date) > as.Date(Sys.getenv("TIMCI_SPA_Q1_END_DATE")) & as.Date(date) <= as.Date(Sys.getenv("TIMCI_SPA_Q2_END_DATE")) ~ "Q2",
    as.Date(date) <= as.Date(Sys.getenv("TIMCI_SPA_Q2_END_DATE")) ~ "Q3")
  )
```

```{r, eval=is_rct}
all <- all %>% 
  dplyr::mutate(quarter = dplyr::case_when(
    as.Date(date) <= as.Date(Sys.getenv("TIMCI_SPA_Q2_END_DATE")) ~ "Q2",
    as.Date(date) > as.Date(Sys.getenv("TIMCI_SPA_Q2_END_DATE")) ~ "Q3")
  )
```

```{r, eval=cond, results="asis"}
obs_count <- all %>%                       
  dplyr::group_by(facility_name) %>%
  dplyr::summarise("Observed children" = n_distinct(child_id),
                   "Observed providers" = n_distinct(hcp_id)) %>%
  bind_rows(dplyr::summarise(.,
                             across(where(is.numeric), sum),
                             across(where(is.character), ~"Total"))) %>%
  rowwise() %>% 
  dplyr::mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE))

obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  align = c("c", "c", "c"),
                  caption = "Number of observed participants (children and providers)") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::row_spec(1:(nrow(obs_count)/2) * 2, background = striped_row_bg)
```

The number of consultation observations to be done depends on the numbers of providers seeing children under 5 at the facility:
\begin{itemize}
  \item 1 provider: 14-18 observations
  \item 2 providers: 10-12 observations per provider
  \item 3 providers: 8-10 observations per provider
  \item 4 providers: 6-8 observations per provider
  \item 5 providers: 5-7 observations per provider
  \item 6 providers: 5-6 observations per provider
\end{itemize}

```{r, results="asis", eval=cond & is_ls}
q1_count <- all %>%
  dplyr::filter(quarter == "Q1") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q1)" = n_distinct(child_id))

q2_count <- all %>%
  dplyr::filter(quarter == "Q2") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q2)" = n_distinct(child_id))

obs_count <- merge(x = q1_count,
                   y = q2_count,
                   by = c("facility_name", "hcp_id"),
                   all = TRUE)
```

```{r, results="asis", eval=cond & is_senegal}
obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  longtable = TRUE,
                  linesep = "",
                  align = c("c", "c", "c"),
                  caption = "Number of consultation observations by providers in Q1 and Q2") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top") 
```

```{r, results="asis", eval=cond & is_kenya}
q3_count <- all %>%
  dplyr::filter(quarter == "Q3") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q3)" = n_distinct(child_id))

obs_count <- merge(x = obs_count,
                   y = q3_count,
                   by = c("facility_name", "hcp_id"),
                   all = TRUE)

obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  longtable = TRUE,
                  linesep = "",
                  align = c("c", "c", "c", "c"),
                  caption = "Number of consultation observations by providers in Q1, Q2 and Q3") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top") 
```

```{r, results="asis", eval=cond & is_india}
obs_count <- all %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("Observed children" = n_distinct(child_id))

obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  longtable = TRUE,
                  linesep = "",
                  align = c("c", "c", "c"),
                  caption = "Number of consultation observations by providers") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top") 
```

```{r, results="asis", eval=cond & is_tanzania}
d1 <- "Kaliua"

q2_count <- all %>%
  dplyr::filter(district == d1) %>%
  dplyr::filter(quarter == "Q2") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q2)" = n_distinct(child_id))

q3_count <- all %>%
  dplyr::filter(district == d1) %>%
  dplyr::filter(quarter == "Q3") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q3)" = n_distinct(child_id))

obs_count <- merge(x = q2_count,
                   y = q3_count,
                   by = c("facility_name", "hcp_id"),
                   all = TRUE)

obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  longtable = TRUE,
                  linesep = "",
                  align = c("c", "c", "c"),
                  caption = paste0("Number of consultation observations by providers in ", d1)) %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top") 
```

```{r, results = "asis", eval=cond & is_tanzania}
d2 <- "Sengerema"

q2_count <- all %>%
  dplyr::filter(district == d2) %>%
  dplyr::filter(quarter == "Q2") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q2)" = n_distinct(child_id))

q3_count <- all %>%
  dplyr::filter(district == d2) %>%
  dplyr::filter(quarter == "Q3") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q3)" = n_distinct(child_id))

obs_count <- merge(x = q2_count,
                   y = q3_count,
                   by = c("facility_name", "hcp_id"),
                   all = TRUE)

obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  align = c("c", "c", "c"),
                  caption = paste0("Number of consultation observations by providers in ", d2)) %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top")
```

```{r, results="asis", eval=cond & is_tanzania}
d3 <- "Tanga"

q2_count <- all %>%
  dplyr::filter(district == d3) %>%
  dplyr::filter(quarter == "Q2") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q2)" = n_distinct(child_id))

q3_count <- all %>%
  dplyr::filter(district == d3) %>%
  dplyr::filter(quarter == "Q3") %>%
  dplyr::group_by(facility_name, hcp_id) %>%
  dplyr::summarise("N obs. children (Q3)" = n_distinct(child_id))

obs_count <- merge(x = q2_count,
                   y = q3_count,
                   by = c("facility_name", "hcp_id"),
                   all = TRUE)

obs_count %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  align = c("c", "c", "c"),
                  caption = paste0("Number of consultation observations by providers in ", d3)) %>%  
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::collapse_rows(columns = 1, valign = "top")
```

```{r, eval=cond & (Sys.getenv('TIMCI_COUNTRY') != 'Senegal'), results='asis'}
all <- all %>% 
  rename(back_from_lab = "child_identification_back_from_lab")

summary <- list(
  "Summary" = list(
    "Initial consultation" = ~qwraps2::n_perc(back_from_lab == 0, prec),
    "Back from lab" = ~qwraps2::n_perc(back_from_lab == 1, prec)
    )
)

out <- format_summary_table(all,
                            summary,
                            facility_name)

all <- all %>%
  dplyr::filter(back_from_lab == 0)

out %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  align = c("c", "c"),
                  caption = "Type of observation") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::row_spec(1, color = total_row_ft2, background = total_row_bg2, bold = TRUE) %>%
  kableExtra::row_spec(1:(nrow(out)/2) * 2, background = striped_row_bg)
```

## Observation times

```{r, eval=cond & is_india, results='asis', fig.cap=heatmap2_cap, fig.height=figsize}
timci::heatmap_wday_hourofday(all, 'start')
```

```{r, results="asis", eval=cond & is_tanzania, fig.cap=heatmap2_cap, fig.height=figsize}
all_q2 <- all %>%
  dplyr::filter(quarter == "Q2")
if (!is.null(all_q2)) {
  timci::heatmap_wday_hourofday(all_q2, 'start')
}
```

```{r, results="asis", eval=cond & is_tanzania, fig.height=figsize}
all_q3 <- all %>%
  dplyr::filter(quarter == "Q3")
if (!is.null(all_q3)) {
  if (nrow(all_q3)>0) {
    timci::heatmap_wday_hourofday(all_q3, 'start')
  }
}
```

```{r, results="asis", eval=cond & is_ls, fig.height=figsize}
all_q1 <- all %>% dplyr::filter(quarter == "Q1")
if (!is.null(all_q1)) {
  timci::heatmap_wday_hourofday(all_q1, 'start')
}
```

```{r, results="asis", eval=cond & is_ls, fig.height=figsize}
all_q2 <- all %>% dplyr::filter(quarter == "Q2")
if (!is.null(all_q2)) {
  if (nrow(all_q2)>0) {
    timci::heatmap_wday_hourofday(all_q2, 'start')
  }
}
```

```{r, results="asis", eval=cond & is_ls, fig.height=figsize}
all_q3 <- all %>% dplyr::filter(quarter == "Q3")
if (!is.null(all_q3)) {
  if (nrow(all_q3)>0) {
    timci::heatmap_wday_hourofday(all_q3, 'start')
  }
}
```

## Young infants

```{r, eval=cond, results="asis"}
summary <- list(
  "Summary" = list(
    "0-59 days" = ~qwraps2::n_perc(young_infant == 1, prec),
    "2-59 months" = ~qwraps2::n_perc(young_infant == 0, prec)
    )
)

out <- format_summary_table(all,
                            summary,
                            facility_name)
out %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  align = c("c", "c"),
                  caption = tcap_age_category) %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::row_spec(1, color = total_row_ft2, background = total_row_bg2, bold = TRUE) %>%
  kableExtra::row_spec(1:(nrow(out)/2) * 2, background = striped_row_bg)
```

## Clinical presentation

```{r, eval=cond, results="asis"}
all$symptoms_lethargic[is.na(all$symptoms_lethargic)] <- 0
all$symptoms_convulsing[is.na(all$symptoms_convulsing)] <- 0

summary <- list(
  "Summary" = list(
    "Unconscious" = ~qwraps2::n_perc(symptoms_unconscious == 1, prec),
    "Lethargic" = ~qwraps2::n_perc(symptoms_lethargic == 1, prec),
    "Convulsing" = ~qwraps2::n_perc(symptoms_convulsing == 1, prec)
    )
)

out <- format_summary_table(all,
                            summary,
                            facility_name)
out %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  longtable = TRUE,
                  align = c("c", "c", "c"),
                  caption = tcap_observed_danger_signs) %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::row_spec(1, color = total_row_ft2, background = total_row_bg2, bold = TRUE) %>%
  kableExtra::row_spec(1:(nrow(out)/2) * 2, background = striped_row_bg)
```

```{r, eval=cond, results="asis"}
all$symptoms_conv_hist_asked[is.na(all$symptoms_conv_hist_asked)] <- 0
all$symptoms_conv_hist_present[is.na(all$symptoms_conv_hist_present)] <- 0

summary <- list(
  "Summary" = list(
    "Asked" = ~qwraps2::n_perc(symptoms_conv_hist_asked == 1, prec),
    "Present" = ~qwraps2::n_perc(symptoms_conv_hist_present == 1, prec)
    )
)

out <- format_summary_table(all,
                            summary,
                            facility_name)
out %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  longtable = TRUE,
                  align = c("c", "c"),
                  caption = "History of convulsions") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::row_spec(1, color = total_row_ft2, background = total_row_bg2, bold = TRUE) %>%
  kableExtra::row_spec(1:(nrow(out)/2) * 2, background = striped_row_bg)
```

```{r, eval=cond, results="asis"}
all$symptoms_resp_asked[is.na(all$symptoms_resp_asked)] <- 0
all$symptoms_resp_present[is.na(all$symptoms_resp_present)] <- 0
all$symptoms_resp_onset_asked[is.na(all$symptoms_resp_onset_asked)] <- 0

summary <- list(
  "Summary" = list(
    "Asked" = ~qwraps2::n_perc(symptoms_resp_asked == 1, prec),
    "Present" = ~qwraps2::n_perc(symptoms_resp_present == 1, prec),
    "Onset asked" = ~qwraps2::n_perc(symptoms_resp_onset_asked == 1, prec)
    )
)

out <- format_summary_table(all,
                            summary,
                            facility_name)
out %>% 
  kableExtra::kbl(booktabs = TRUE,
                  linesep = "",
                  longtable = TRUE,
                  align = c("c", "c", "c"),
                  caption = "Cough/Difficulty breathing") %>% 
  kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
  kableExtra::row_spec(0, bold = TRUE) %>%
  kableExtra::row_spec(1, color = total_row_ft2, background = total_row_bg2, bold = TRUE) %>%
  kableExtra::row_spec(1:(nrow(out)/2) * 2, background = striped_row_bg)
```
