---
title: "TIMCI `r if (Sys.getenv('TIMCI_COUNTRY') != 'Senegal') {'Service Provision Assessment (SPA) - Operational Report'} else {'Evaluation de la prestation de service (EPS) - Rapport opérationnel'}`"
author: "`r if (Sys.getenv('TIMCI_COUNTRY') == 'Tanzania') {'Ifakara Health Institute (IHI)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'India') {'King Georges Medical University (KGMU)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {'Université Cheikh Anta Diop de Dakar (UCAD)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Kenya') {'University of Nairobi (UoN)'} else if (Sys.getenv('TIMCI_COUNTRY') == 'Myanmar') {'Burnet Institute (BI)'} else {'Swiss Tropical and Public Health Institute (Swiss TPH)'}`"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M GMT%z')`"
params:
  research_facilities: !r data.frame(deviceid = character(0), district = character(0), facility = character(0))
  facility_data: NULL
  spa_sco_data: NULL
  spa_cgei_data: NULL
  spa_fa_data: NULL
  spa_hcpi_data: NULL
  raw_withdrawal_data: NULL
output:
  pdf_document:
    number_sections: true
    extra_dependencies:
      float: null
      flafter: null
      bm: null
      tocbibind: ["nottoc"]
      babel: ["french","english"]
      graphicx: null
      fancyhdr: null
      lastpage: null
classoption: table
---

```{r setup-rmd, include=FALSE}
library(magrittr)
library(readxl)
library(ggplot2)
library(lubridate)
library(gridExtra)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.pos='!H')
options(qwraps2_markup = 'markdown')

# Qwraps2 parameters
prec <- 1

#kableExtra table parameters
table_fs <- 7
figsize <- 3
total_row_ft <- "gray"
total_row_ft2 <- "white"
striped_row_bg <- "gray!10"
total_row_bg2 <- "gray"
```

\fancypagestyle{plain}{\pagestyle{fancy}}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{32pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[C]{\includegraphics[width=10cm]{banner.png}}
\fancyfoot[R]{Page \thepage\ of \pageref{LastPage}}
\fancyfoot[L]{TIMCI SPA Operational Report v1.0}

```{r translations-subsection, child = 'translations.Rmd'}
```

\setcounter{tocdepth}{2}
\tableofcontents

\newpage

`r notice_str`

`r intro_str`

```{r}
is_india <- Sys.getenv('TIMCI_COUNTRY') == 'India'
is_tanzania <- Sys.getenv('TIMCI_COUNTRY') == 'Tanzania'
is_kenya <- Sys.getenv('TIMCI_COUNTRY') == 'Kenya'
is_senegal <- Sys.getenv('TIMCI_COUNTRY') == 'Senegal'
is_rct <- is_tanzania | is_india
is_ls <- is_kenya | is_senegal
```

```{r setup-variables}
spa_sco_data <- params$spa_sco_data
spa_cgei_data <- params$spa_cgei_data
spa_fa_data <- params$spa_fa_data
spa_hcpi_data <- params$spa_hcpi_data
```

```{r conditions}
spa_sco_is_not_null <- !is.null(spa_sco_data)
if(spa_sco_is_not_null) {
  spa_sco_is_not_null <- (nrow(spa_sco_data) > 0) & (length(spa_sco_data) > 0)
}
spa_cgei_is_not_null <- !is.null(spa_cgei_data)
if(spa_cgei_is_not_null) {
  spa_cgei_is_not_null <- (nrow(spa_cgei_data) > 0) & (length(spa_cgei_data) > 0)
}
spa_fa_is_not_null <- !is.null(spa_fa_data)
if(spa_fa_is_not_null) {
  spa_fa_is_not_null <- (nrow(spa_fa_data) > 0) & (length(spa_fa_data) > 0)
}
spa_hcpi_is_not_null <- !is.null(spa_hcpi_data)
if(spa_hcpi_is_not_null) {
  spa_hcpi_is_not_null <- (nrow(spa_hcpi_data) > 0) & (length(spa_hcpi_data) > 0)
}
spa_is_not_null <- spa_sco_is_not_null | spa_cgei_is_not_null | spa_fa_is_not_null | spa_hcpi_is_not_null
```

```{r}
start_date <- NULL
end_date <- NULL
```

```{r dates, results='asis', eval=spa_is_not_null}
sco_start_date <- NULL
sco_end_date <- NULL
if (spa_sco_is_not_null) {
  sco_start_date <- min(spa_sco_data$date)
  sco_end_date <- max(spa_sco_data$date)
}

cgei_start_date <- NULL
cgei_end_date <- NULL
if (spa_cgei_is_not_null) {
  if (nrow(spa_cgei_data) > 0) {
    cgei_start_date <- min(spa_cgei_data$date)
    cgei_end_date <- max(spa_cgei_data$date)
  }
}

fa_start_date <- NULL
fa_end_date <- NULL
if (spa_fa_is_not_null) {
  if (nrow(spa_fa_data) > 0) {
    fa_start_date <- min(spa_fa_data$date)
    fa_end_date <- max(spa_fa_data$date)
  }
}

hcpi_start_date <- NULL
hcpi_end_date <- NULL
if (spa_hcpi_is_not_null) {
  if (nrow(spa_hcpi_data) > 0) {
    hcpi_start_date <- min(spa_hcpi_data$date)
    hcpi_end_date <- max(spa_hcpi_data$date)
  }
}

start_date <- min(sco_start_date, cgei_start_date, fa_start_date, hcpi_start_date)
end_date <- max(sco_end_date, cgei_end_date, fa_end_date, hcpi_end_date)
```

```{r start-end-dates, results='asis'}
if (Sys.getenv('TIMCI_COUNTRY') == 'Senegal') {
  cat(paste0("Ce rapport couvre la période du **", start_date, "** (début de l'étude) au **", end_date, "** pour le **Sénégal**."))
} else {
  cat(paste0("This report covers the period from **", start_date, "** (study start) to **", end_date, "** for **", Sys.getenv('TIMCI_COUNTRY'), "**."))
}
```

```{r, eval = spa_is_not_null, results = "asis"}
# obs_count <- all %>%                       
#   dplyr::group_by(facility_name) %>%
#   dplyr::summarise("Observed children" = n_distinct(child_id),
#                    "Observed providers" = n_distinct(hcp_id)) %>%
#   bind_rows(dplyr::summarise(.,
#                              across(where(is.numeric), sum),
#                              across(where(is.character), ~"Total"))) %>%
#   rowwise() %>% 
#   dplyr::mutate(Total = sum(c_across(where(is.numeric)), na.rm = TRUE))
# 
# obs_count %>% 
#   kableExtra::kbl(booktabs = TRUE,
#                   linesep = "",
#                   align = c("c", "c", "c"),
#                   caption = "Number of consultation observations") %>% 
#   kableExtra::kable_styling(latex_options = c("HOLD_position", "repeat_header"), font_size = table_fs) %>%
#   kableExtra::row_spec(0, bold = TRUE) %>%
#   kableExtra::row_spec(1:(nrow(obs_count)/2) * 2, background = striped_row_bg)
```

```{r context-subsection, child = 'context.Rmd'}
```

```{r spa-cleaning, child = if (spa_is_not_null) 'data_cleaning_spa.Rmd'}
```

```{r sco-subsection, child = if (spa_sco_is_not_null) 'spa_monitoring_report_sub_sco.Rmd'}
```

```{r cgei-subsection, child =  if (spa_cgei_is_not_null) 'spa_monitoring_report_sub_cgei.Rmd'}
```

```{r fa-subsection, child =  if (spa_fa_is_not_null) 'spa_monitoring_report_sub_fa.Rmd'}
```

```{r hcpi-subsection, child =  if (spa_hcpi_is_not_null) 'spa_monitoring_report_sub_hcpi.Rmd'}
```

\newpage
\listoftables

\newpage
\listoffigures

```{r technical-info-subsection, child = 'technical_info.Rmd'}
```
